### 2019-08-24 Opsætningexam/DraftExam.tex
hella

\documentclass[12pt,a4paper]{article}
\usepackage{amsmath}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\onehalfspacing
\usepackage[danish]{babel}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{pst-tree}
\usepackage{tikz}
\usetikzlibrary{trees}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage[top=2.5cm, bottom=2.5cm, left=2.5cm, right=2.5cm]{geometry}
\usepackage{enumerate} 
\usepackage{amssymb}
\usepackage{csquotes}
\usepackage{fancyhdr}
\usepackage{times}
\usepackage{gauss}
\usepackage{fancyhdr}
\usepackage[bottom]{footmisc}
\pagestyle{fancy}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{lscape}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
\node[shape=circle,draw,inner sep=2pt] (char) {#1};}}
\DeclareMathSizes{12}{12}{10}{10}
\interfootnotelinepenalty=10000
\usepackage{dsfont}
\usepackage{mathtools}
\usepackage{graphics}
\usepackage[danish]{babel} 
\usepackage{graphicx}
\usepackage{multirow, booktabs}
\usepackage[final]{pdfpages}
\usepackage{hyperref}

\lhead{}
\rhead{}
\chead{}

\begin{document}
\includepdf[pages=-]{forside.pdf}
\newpage
\onehalfspacing

\tableofcontents
\newpage
\section{Introduction}
This project predicts the valuation price of the danish housing market. By scraping \href{https://www.boliga.dk}{boliga.dk} we obtain a broad range of variables of potential interest, on all listed housing by august $22^{th}$, 2019. The AVI, \href{https://www.hvorlangterder.dk}{hvorlangterder.dk}, constructs measurements of distances from an address to conveniences and necessities such as hospitals, schools and shopping. Obtaining these distances for all of the listed housing and merging the two datasets, gives more opportunity for geographical-control. The data from hvorlangterder.dk will allow more micro-oriented differences within a given municipality. Which otherwise would not have been captured.  
\newline \underline{Måske en anden formulering ovenfor?} 
By applying supervised machine learning on our combined dataset.  
\section{Data description}
\subsection{Data construction}
Crime-rates. Traffic offences are not considered as a "serious" offence and are therefore neglected. 
\subsection{Exclusion of outliers}
A few of the listed housing, have been for sale for over a decade. These are considered outliers, which are overly priced considering their characteristics. The outliers are excluded, because they would otherwise only contribute to a bias of overestimation. Number of excluded housing.  
\newline
\begin{tabular}{ c | c | c | c | c | c | c | c} 
  \toprule
   & \multicolumn{2}{c|}{Dreng} & \multicolumn{2}{c}{Pige} \\ \hline
   & Hovedstaden & Sjælland & Syddanmark & Midtjylland & Nordjylland \\
   \midrule 
   Villa & 513,36 & 459,67 & 503,62 & 461,96 \\ \hline
   Rækkehus & 470,67 & 404,95 & 460,93 & 407,24 \\ \hline
   Ejerlejlighhed & 482,30 & 463,94 & 455,87 & 449,54 \\ \hline
   Fritidsbolig & 513,36 & 459,67 & 503,62 & 461,96 \\ \hline
   Kolonihave & 470,67 & 404,95 & 460,93 & 407,24 \\ \hline
   Andelsbolig & 482,30 & 463,94 & 455,87 & 449,54 \\ \hline
   Landejendom & 513,36 & 459,67 & 503,62 & 461,96 \\ \hline
   Helårsgrund & 470,67 & 404,95 & 460,93 & 407,24 \\ \hline
   Fritidsgrund & 482,30 & 463,94 & 455,87 & 449,54 \\ \hline
   Villalejlighed & 513,36 & 459,67 & 503,62 & 461,96 \\ \hline
   Lystejendom & 470,67 & 404,95 & 460,93 & 407,24 \\ 
    \bottomrule
\end{tabular}
\newline

\section{Methods}
\subsection{Supervised Machine Learning}
The objective by applying Machine Learning to these kinds of data, is to train a model that can predict pricing of housing listed in near future.
Two types of predictive models will be used for the sake of returning different outputs: Regression-model to return the pricing as a continuous output. As well as a classification-model for predicting the interval which the price is included in.

\subsection{Regularization}
The use of a sizeable amount of regressors leads to a significant risk of over-fitting the prediction model. 
For the purpose of dealing with over-fitting, a form of regularization needs to be carried out. The Lasso-feature posses the attributes to do so. Regularization by Lasso, will penalize complexity of the model by adjustment of parameter estimates. This penalty will make the model less complex and more appropriate for prediction. \footnote{Big Data in Social Sciences, Forster et al. p. 173}\, \footnote{Python Machine Learning, Sebastian Raschka et al. p. 332}
\newline The regularization parameter $\lambda$ is determined by: $$Evt-optimeringsproblem$$

\subsection{Cross-Validation}
Selecting $\lambda$

\subsection{Variable selction}
Another convenient feature of Lasso, is the

\section{Analysis}

\section{Results}

\section{Discussion}
\subsection{Data critique}
Another interesting prediction which could have been obtained using the same methods, could have been to estimate expected selling prices. This could have been done simply by scraping data on sold housing instead. This could be of more value for private agents, whose main interest should be the selling price of their housing. 
\newline 
In a prediction-model like this it is near impossible to evade some form of omitted variable bias. A significant amount of potential important factors can not be acquired. For an example the view from the listed housing will for sure have great impact of the valuation price. Another factor of interest could have been a evaluation of the condition of the housing, unfortunately the "statement of property" red. (tilstandrapport) are not publicly accessible.

\newpage
\section{Litterature}
Big Data in Social Sciences, Forster et al. 2017
\newline Python Machine Learning, Sebastian Raschka et al. 2017, $2^{nd}$editon
\end{document}

### 2019-08-25 Opsætningexam/DraftExam.tex
hej

@@
 This project predicts the valuation price of the danish housing market.
-By scraping \href{https://www.boliga.dk}{boliga.dk} we obtain a broad range of variables of potential interest, on all listed housing by august $22^{th}$, 2019.
+By scraping \href{https://www.boliga.dk}{boliga.dk} we obtain a broad range of variables of potential interest, on all listed housing by august $23^{th}$, 2019.
 The AVI, \href{https://www.hvorlangterder.dk}{hvorlangterder.dk}, constructs measurements of distances from an address to conveniences and necessities such as hospitals, schools and shopping.
@@
 \newline \underline{Måske en anden formulering ovenfor?}
+Also scraping from  \href{https://statistik.politi.dk/QvAJAXZfc/opendoc.htm?document=QlikApplication%2F2999_Public\%2FPublic_IndsatsResultater.qvw}{statistik.politi.dk} and 
+\href{https://www.dst.dk/da/Statistik/emner/befolkning-og-valg}{Danmarks Statistik}. 
 By applying supervised machine learning on our combined dataset.  
@@
 \newline
-\begin{tabular}{ c | c | c | c | c | c | c | c} 
+\begin{tabular}{| c | c | c | c | c | c |} 
   \toprule
-   & \multicolumn{2}{c|}{Dreng} & \multicolumn{2}{c}{Pige} \\ \hline
-   & Hovedstaden & Sjælland & Syddanmark & Midtjylland & Nordjylland \\
+  \multicolumn{6}{|c|}{Danmark} \\ \hline
+   & \multicolumn{2}{c|}{Sjælland} & \multicolumn{3}{c|}{Ikke Sjælland} \\ \hline
+  Type/Region & Hovedstaden & Sjælland & Syddanmark & Midtjylland & Nordjylland \\
    \midrule 
@@
 \subsection{Supervised Machine Learning}
-The objective by applying Machine Learning to these kinds of data, is to train a model that can predict pricing of housing listed in near future.
+The objective by applying Machine Learning is to train a model that can predict pricing of housing listed in near future.
 Two types of predictive models will be used for the sake of returning different outputs: Regression-model to return the pricing as a continuous output.
@@
 
-\subsection{Regularization}
+\subsection{Regularization / Lasso og derved variable selection}
 The use of a sizeable amount of regressors leads to a significant risk of over-fitting the prediction model. 
@@
 \newline The regularization parameter $\lambda$ is determined by: $$Evt-optimeringsproblem$$
+Another convenient attribute of the Lasso-feature is that it produces regressions where some of the variables are set equal to zero \footnote{Hal R.
+Varian.
+Big data: New tricks for econometrics.
+p.19}.
+Lasso thereby perform the variable selection.
+
+\subsection{Lars}
 
@@
 Selecting $\lambda$
-
-\subsection{Variable selction}
-Another convenient feature of Lasso, is the
 
@@
 \section{Litterature}
+
 Big Data in Social Sciences, Forster et al. 2017
 \newline Python Machine Learning, Sebastian Raschka et al. 2017, $2^{nd}$editon
+\newline Hal R. Varian. Big data: New tricks for econometrics. Journal of Economic Perspectives, 28(2):3–28, 2014.
+
 \end{document}

### 2019-08-25 Opsætningexam/ProjectDescription.tex
d

--- 2019-08-24 Opsætningexam/DraftExam.tex
@@
 \usepackage{hyperref}
+\pagenumbering{gobble}
 
@@
 
+\usepackage{graphicx}
+
 \begin{document}
-\includepdf[pages=-]{forside.pdf}
-\newpage
-\onehalfspacing
 
-\tableofcontents
-\newpage
-\section{Introduction}
-This project predicts the valuation price of the danish housing market.
-By scraping \href{https://www.boliga.dk}{boliga.dk} we obtain a broad range of variables of potential interest, on all listed housing by august $22^{th}$, 2019.
-The AVI, \href{https://www.hvorlangterder.dk}{hvorlangterder.dk}, constructs measurements of distances from an address to conveniences and necessities such as hospitals, schools and shopping.
-Obtaining these distances for all of the listed housing and merging the two datasets, gives more opportunity for geographical-control.
-The data from hvorlangterder.dk will allow more micro-oriented differences within a given municipality.
-Which otherwise would not have been captured.
-\newline \underline{Måske en anden formulering ovenfor?} 
-By applying supervised machine learning on our combined dataset.  
-\section{Data description}
-\subsection{Data construction}
-Crime-rates. Traffic offences are not considered as a "serious" offence and are therefore neglected. 
-\subsection{Exclusion of outliers}
-A few of the listed housing, have been for sale for over a decade.
-These are considered outliers, which are overly priced considering their characteristics.
-The outliers are excluded, because they would otherwise only contribute to a bias of overestimation.
-Number of excluded housing.
-\newline
-\begin{tabular}{ c | c | c | c | c | c | c | c} 
-  \toprule
-   & \multicolumn{2}{c|}{Dreng} & \multicolumn{2}{c}{Pige} \\ \hline
-   & Hovedstaden & Sjælland & Syddanmark & Midtjylland & Nordjylland \\
-   \midrule 
-   Villa & 513,36 & 459,67 & 503,62 & 461,96 \\ \hline
-   Rækkehus & 470,67 & 404,95 & 460,93 & 407,24 \\ \hline
-   Ejerlejlighhed & 482,30 & 463,94 & 455,87 & 449,54 \\ \hline
-   Fritidsbolig & 513,36 & 459,67 & 503,62 & 461,96 \\ \hline
-   Kolonihave & 470,67 & 404,95 & 460,93 & 407,24 \\ \hline
-   Andelsbolig & 482,30 & 463,94 & 455,87 & 449,54 \\ \hline
-   Landejendom & 513,36 & 459,67 & 503,62 & 461,96 \\ \hline
-   Helårsgrund & 470,67 & 404,95 & 460,93 & 407,24 \\ \hline
-   Fritidsgrund & 482,30 & 463,94 & 455,87 & 449,54 \\ \hline
-   Villalejlighed & 513,36 & 459,67 & 503,62 & 461,96 \\ \hline
-   Lystejendom & 470,67 & 404,95 & 460,93 & 407,24 \\ 
-    \bottomrule
-\end{tabular}
-\newline
+\title{Predicting Evaluation Prices of Danish Real Estate Property} 
+\author{Exam-numbers 115, 144, 146, 204}
+\maketitle
+\section*{}
+The intention of this project is to predict which features are most relevant for evaluation of real estate properties in Denmark.
+Two prediction models will be used, one with a classification output by price-intervals.
+The second model with a continuous output.
+Data will be scraped from \href{https://www.boliga.dk}{boliga.dk}, \href{https://www.hvorlangterder.dk}{hvorlangterder.dk}, \href{https://statistik.politi.dk/QvAJAXZfc/opendoc.htm?document=QlikApplication%2F2999_Public\%2FPublic_IndsatsResultater.qvw}{statistik.politi.dk},
+ \href{https://www.dst.dk/da/Statistik/emner/befolkning-og-valg}{Danmarks Statistik}.
+The data from \href{https://www.boliga.dk}{boliga.dk} and \href{https://www.hvorlangterder.dk}{hvorlangterder.dk} are undoubtedly essential to the model.
+Whereas the data scraped from \href{https://statistik.politi.dk/QvAJAXZfc/opendoc.htm?document=QlikApplication%2F2999_Public\%2FPublic_IndsatsResultater.qvw}{statistik.politi.dk}
+and \href{https://statistikbanken.dk/statbank5a/default.asp?w=1280}{Statistikbanken} contributes with potential to include socio-economic factors.\newline
+The model will take variation in pricing caused by geographical matters, as well as differences in types of housing into account.
+Machine learning will be applied, for the purpose of prediction of prices.
+Because of the large amount of terms and corresponding interaction-terms in the prediction-model, regularization by the Lasso-feature will be used.
 
-\section{Methods}
-\subsection{Supervised Machine Learning}
-The objective by applying Machine Learning to these kinds of data, is to train a model that can predict pricing of housing listed in near future.
-Two types of predictive models will be used for the sake of returning different outputs: Regression-model to return the pricing as a continuous output.
-As well as a classification-model for predicting the interval which the price is included in.
-
-\subsection{Regularization}
-The use of a sizeable amount of regressors leads to a significant risk of over-fitting the prediction model. 
-For the purpose of dealing with over-fitting, a form of regularization needs to be carried out.
-The Lasso-feature posses the attributes to do so.
-Regularization by Lasso, will penalize complexity of the model by adjustment of parameter estimates.
-This penalty will make the model less complex and more appropriate for prediction.
-\footnote{Big Data in Social Sciences, Forster et al.
-p.
-173}\, \footnote{Python Machine Learning, Sebastian Raschka et al.
-p.
-332}
-\newline The regularization parameter $\lambda$ is determined by: $$Evt-optimeringsproblem$$
-
-\subsection{Cross-Validation}
-Selecting $\lambda$
-
-\subsection{Variable selction}
-Another convenient feature of Lasso, is the
-
-\section{Analysis}
-
-\section{Results}
-
-\section{Discussion}
-\subsection{Data critique}
-Another interesting prediction which could have been obtained using the same methods, could have been to estimate expected selling prices.
-This could have been done simply by scraping data on sold housing instead.
-This could be of more value for private agents, whose main interest should be the selling price of their housing.
-\newline 
-In a prediction-model like this it is near impossible to evade some form of omitted variable bias.
-A significant amount of potential important factors can not be acquired.
-For an example the view from the listed housing will for sure have great impact of the valuation price.
-Another factor of interest could have been a evaluation of the condition of the housing, unfortunately the "statement of property" red.
-(tilstandrapport) are not publicly accessible.
-
-\newpage
-\section{Litterature}
-Big Data in Social Sciences, Forster et al. 2017
-\newline Python Machine Learning, Sebastian Raschka et al. 2017, $2^{nd}$editon
 \end{document}

### 2019-08-25 Opsætningexam/DraftExam.tex
m

@@
 This project predicts the valuation price of the danish housing market.
-By scraping \href{https://www.boliga.dk}{boliga.dk} we obtain a broad range of variables of potential interest, on all listed housing by august $23^{th}$, 2019.
+By scraping \href{https://www.boliga.dk}{boliga.dk} we obtain a broad range of features of interest, on all listed housing by august $23^{th}$, 2019.
 The AVI, \href{https://www.hvorlangterder.dk}{hvorlangterder.dk}, constructs measurements of distances from an address to conveniences and necessities such as hospitals, schools and shopping.
@@
    \midrule 
-   Villa & 513,36 & 459,67 & 503,62 & 461,96 \\ \hline
-   Rækkehus & 470,67 & 404,95 & 460,93 & 407,24 \\ \hline
-   Ejerlejlighhed & 482,30 & 463,94 & 455,87 & 449,54 \\ \hline
-   Fritidsbolig & 513,36 & 459,67 & 503,62 & 461,96 \\ \hline
-   Kolonihave & 470,67 & 404,95 & 460,93 & 407,24 \\ \hline
-   Andelsbolig & 482,30 & 463,94 & 455,87 & 449,54 \\ \hline
-   Landejendom & 513,36 & 459,67 & 503,62 & 461,96 \\ \hline
-   Helårsgrund & 470,67 & 404,95 & 460,93 & 407,24 \\ \hline
-   Fritidsgrund & 482,30 & 463,94 & 455,87 & 449,54 \\ \hline
-   Villalejlighed & 513,36 & 459,67 & 503,62 & 461,96 \\ \hline
-   Lystejendom & 470,67 & 404,95 & 460,93 & 407,24 \\ 
+   Villa & 513,36 & 459,67 & 503,62 & 461,96 & \\ \hline
+   Rækkehus & 470,67 & 404,95 & 460,93 & 407,24 & \\ \hline
+   Ejerlejlighhed & 482,30 & 463,94 & 455,87 & 449,54 & \\ \hline
+   Fritidsbolig & 513,36 & 459,67 & 503,62 & 461,96 & \\ \hline
+   Kolonihave & 470,67 & 404,95 & 460,93 & 407,24 & \\ \hline
+   Andelsbolig & 482,30 & 463,94 & 455,87 & 449,54 & \\ \hline
+   Landejendom & 513,36 & 459,67 & 503,62 & 461,96 & \\ \hline
+   Helårsgrund & 470,67 & 404,95 & 460,93 & 407,24 & \\ \hline
+   Fritidsgrund & 482,30 & 463,94 & 455,87 & 449,54 & \\ \hline
+   Villalejlighed & 513,36 & 459,67 & 503,62 & 461,96 & \\ \hline
+   Lystejendom & 470,67 & 404,95 & 460,93 & 407,24 & \\ 
     \bottomrule
@@
 332}
-\newline The regularization parameter $\lambda$ is determined by: $$Evt-optimeringsproblem$$
-Another convenient attribute of the Lasso-feature is that it produces regressions where some of the variables are set equal to zero \footnote{Hal R.
+\newline Lasso solves the optimizationproblem: $$Evt-optimeringsproblem$$
+Another convenient attribute of the Lasso-feature is that it produces regressions where some of the features are set equal to zero \footnote{Hal R.
 Varian.
@@
 p.19}.
-Lasso thereby perform the variable selection.
+Lasso thereby perform feature selection.
 
@@
 
-\subsection{Cross-Validation}
+\subsection{Cross-Validation by K-fold method}
 Selecting $\lambda$

### 2019-08-25 hvorlang_scrape.py
Sidste dataset = 'Final_Boligdata.csv'

@@ -1,0 +1,46 @@
+import numpy as np
+import pandas as pd
+import requests
+import scraping_class
+import time
+import random
+import json
+import tqdm
+
+logfile = 'Hvorlangterder_full2_log.csv'
+connector = scraping_class.Connector(logfile)
+
+df = pd.read_csv('Boliga - Behandling 2 - Befolkningstal.csv')
+
+def create_url_and_scrape(lat_long):
+    url = 'https://hvorlangterder.poi.viamap.net/v1/nearestpoi/?poitypes='
+    poitypes = ["lake", "forest", "doctor", "supermarket", "school", "daycare", "hospital", "metro",
+                "train", "stop", "strain", "junction", "pharmacy", "library", "coast", "airport"]
+    coor = lat_long.split(' ')
+    coordinates = '&fromcoord=' + ''.join(coor)
+    auth = '&mot=foot&token=eyJkcGZ4IjogImh2b3JsYW5ndGVyZGVyIiwgInByaXZzIjogInIxWjByMEYwazZCdFdxUWNPVXlrQi95NlNVcEp2MlFiZ3lYZXRxNEhZNFhPLzNZclcwK0s5dz09In0.fP4JWis69HmaSg5jVHiK8nemiCu6VaMULSGGJyK4D4PkWq4iA1+nSHWMaHxepKwJ83sEiy9nMNZhv7BcktRNrA'
+    tempurl = url + ','.join(poitypes) + coordinates + auth
+    #time.sleep(0.3)
+    print(1)
+    response = requests.get(tempurl)
+    js = response.json()
+    data = dict()
+    data['lake'] = js['lake']['routedmeters'] 
+    data['forest'] = js['forest']['routedmeters'] 
+    data['doctor'] = js['doctor']['routedmeters']
+    data['supermarket'] = js['supermarket']['routedmeters']
+    data['school'] = js['school']['routedmeters']
+    data['daycare'] = js['daycare']['routedmeters']
+    data['hospital'] = js['hospital']['routedmeters']
+    data['metro'] = js['metro']['routedmeters']
+    data['train'] = js['train']['routedmeters']
+    data['strain'] =js['strain']['routedmeters']
+    data['junction'] = js['junction']['routedmeters']
+    data['pharmacy'] = js['pharmacy']['routedmeters']
+    data['library'] = js['library']['routedmeters']
+    data['coast'] = js['coast']['routedmeters']
[…]

### 2019-08-26 Opsætningexam/DraftExam.tex
l

@@
 \section{Introduction}
-This project predicts the valuation price of the danish housing market.
-By scraping \href{https://www.boliga.dk}{boliga.dk} we obtain a broad range of features of interest, on all listed housing by august $23^{th}$, 2019.
-The AVI, \href{https://www.hvorlangterder.dk}{hvorlangterder.dk}, constructs measurements of distances from an address to conveniences and necessities such as hospitals, schools and shopping.
-Obtaining these distances for all of the listed housing and merging the two datasets, gives more opportunity for geographical-control.
-The data from hvorlangterder.dk will allow more micro-oriented differences within a given municipality.
+
+\section{Data description}
+
+\subsection{Data sources}
+Scraping from \textbf{\href{https://www.boliga.dk}{boliga.dk}} provides key characteristic such as price, squaremeters, location etc.   \newline
+The API \href{https://www.hvorlangterder.dk}{hvorlangterder.dk} returns measurements of distances from an address to conveniences such as hospitals, schools and shopping.
+Obtaining these distances for all of the listed housing and merging the two datasets, gives additional arguments to geographical-control.
+The data from hvorlangterder.dk can allow more micro-oriented differences within a given municipality.
 Which otherwise would not have been captured.
-\newline \underline{Måske en anden formulering ovenfor?}
-Also scraping from  \href{https://statistik.politi.dk/QvAJAXZfc/opendoc.htm?document=QlikApplication%2F2999_Public\%2FPublic_IndsatsResultater.qvw}{statistik.politi.dk} and 
-\href{https://www.dst.dk/da/Statistik/emner/befolkning-og-valg}{Danmarks Statistik}. 
-By applying supervised machine learning on our combined dataset.  
-\section{Data description}
+\newline 
+Social and economic factors on municipality level is collected from \href{https://statistik.politi.dk/QvAJAXZfc/opendoc.htm?document=QlikApplication%2F2999_Public\%2FPublic_IndsatsResultater.qvw}{statistik.politi.dk}   \newline
+\href{https://www.dst.dk/da/Statistik/emner/befolkning-og-valg}{Danmarks Statistik} respectively. These factors includes reported crime, income and level of completed education.
+
 \subsection{Data construction}
-Crime-rates. Traffic offences are not considered as a "serious" offence and are therefore neglected. 
+Traffic offences are not considered as a "serious" offence and are therefore excluded in the crime statistics. 
+Socio-economic data is converted to ratios.
+
 \subsection{Exclusion of outliers}
@@
 The outliers are excluded, because they would otherwise only contribute to a bias of overestimation.
-Number of excluded housing.
+The total number of excluded housing are approximately 4000.
 \newline
@@
 \subsection{Regularization / Lasso og derved variable selection}
-The use of a sizeable amount of regressors leads to a significant risk of over-fitting the prediction model. 
+The use of a sizeable amount of features leads to a significant risk of over-fitting the prediction model. 
 For the purpose of dealing with over-fitting, a form of regularization needs to be carried out.
@@
 332}
-\newline Lasso solves the optimizationproblem: $$Evt-optimeringsproblem$$
-Another convenient attribute of the Lasso-feature is that it produces regressions where some of the features are set equal to zero \footnote{Hal R.
+\newline Lasso solves the optimization problem: $$\hat{\beta}(\lambda)=\underset{\beta}{arg\min} \left(\frac{1}{N} \sum_{i=1}^{N} (Y_i-\hat{Y_i}(\beta)^2)+\lambda\sum_{j=1}^{p}|\beta_j|\right) \qquad s.t \quad \lambda \geq 0 $$
+Another convenient attribute of the Lasso penalty is that some estimates are set equal to zero \footnote{Hal R.
 Varian.
@@
 p.19}.
-Lasso thereby perform feature selection.
+Lasso thereby performs the feature selection automatic.
 
@@
 
-\subsection{Cross-Validation by K-fold method}
-Selecting $\lambda$
+\subsection{K-fold Cross-Validation}
+To get the optimal tuning parameter: $\lambda$ a k-fold cross-validation is performed. The 10-fold CV, divides the data into 10 subsets
 
@@
 \section{Discussion}
+
 \subsection{Data critique}
-Another interesting prediction which could have been obtained using the same methods, could have been to estimate expected selling prices.
+Another interesting prediction which could have been obtained using the same methods, would have been to estimate expected selling prices.
 This could have been done simply by scraping data on sold housing instead.
@@
 (tilstandrapport) are not publicly accessible.
+\newline
+The prediction of the cooperative housing valuation %\footnote{http://housingpeople.dk/en/housing-guide/housing-types/cooperative-andelsbolig/},
+are subject to significant bias, since the cooperative housing that enters the marked through a realtor often would be those with critical amount of undesirable characteristics. 
+\section{Conclusion}
 

### 2019-08-27 Opsætningexam/Tentative ethics/Ethics(litrev).tex
Foreløbig etik afsnit

\documentclass[10pt,a4paper]{report}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}

\begin{document}
\paragraph{An Ethical Overview \newline}
The ethical principles of social research are anchored in the fundamental human rights, which are broadly formulated in the UN Declaration of Human Rights. Additional policies and declarations that codify principles of research ethics and the ethical treatment of research participants include the Nuremberg Code, the Helsinki Declaration, the Belmont Report, and the Menlo Report (Salganik 2017; European Commission 2018). These codes and addendums originate mostly in the biomedical field, though they encompass the central principles applied to all human research, which have led some academics to call for a Hippocratic oath for data scientists to safeguard against powerful new technologies under development in laboratories and tech firms (Rotblat 1999; Sample 2019). This discussion is nothing new however, as a tentative reformulation of the Hippocratic oath was introduced by Karl Popper (1969), wherein he stressed the importance of professional responsibility, a critical mind, and an overriding loyalty towards the betterment of mankind.\newline
Matthew Salgani (2017) offer four principles deduced from the Belmont and Menlo Report that should guide the ethical deliberations of the researcher: 1) the respect for persons, that is individuals should be treated as autonomous and if circumstances require it individuals should be entitled to additional protections. 2) Beneficence stresses the importance of doing no harm and to maximize the possible benefits and minimizing any potential harms. 3) The principle of justice touches upon the importance of the distribution of burdens and benefits of the social scientist's research. This principle stress that is should not be a single stratum of society that bears the costs of the research while another stratum benefits. 4) The fourth and final principle is the respect for law and public interest, according to Salganik, the principle consists of two distinct elements, that is compliance to relevant laws and legal contracts and transparency-based accountability. It is worth noting that Popper’s tentative Hippocratic oath mirrors the first three principles put forth by Salganik, stressing the importance of the ethical conduct of the researcher.\newline
The need for rigid ethical standards within computational social science was made apparent by the Cambridge Analytica Scandal that broke on the 17th of March 2018. Where Steve Bannon could reveal that between 2013 and 2015 Cambridge Analytica had exploited a loophole in Facebook’s API which allowed the company to harvest profile data from 87 million Facebook users, without the user’s permission and use the harvested data to construct a massive targeted marketing database based on the user’s likes and interests (Vox.com 2018). Other examples of misuse of data acquired from Facebook include the Harvard-run experiment, where students' data was used to create new knowledge about how social networks form and how these networks and their actors' behavior co-evolve, and the emotional contagion experiment from 2012, where approximately 700,000 users were involved in a research experiment to examine the extent to which a person's emotions are affected by the emotions of the people they interact with (Salgani 2017).\newline
From this it should be evident that clear ethical guidelines are required in order to protect the user's privacy from tech-savvy companies. To this end, the European Parliament introduced the General Data Protection Regulation (GDPR). With its seven overarching principles the GDPR seeks to formalize the procedures involved in the data processing and storing of sensitive and private information (CRDC 2018). These principles include and expand upon the principles found in the Belmont and Menlo Report. The most important consideration, however, must be that even a dataset comprising tens of thousands of observations involve human beings who must be protected from adverse side-effects of the social research. There is considerable evidence that point to the fact that even in anonymized data sets it can be possible to backtrack an individual's identity. A researcher must therefore be mindful of the mosaic effect if the dataset combines large amount of data from various sources (European Commission 2018).
\end{document}

Consumer Data Research Center, UK  [CDRC] (2018) The General Data Protection Regulation & Social Science Research [Online] https://ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020_ethics-soc-science-humanities_en.pdf [Accessed on 25/08/2019]

European Commission (2018). Ethics in Social Sciences and the Humanities [Online] https://ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020_ethics-soc-science-humanities_en.pdf [Accessed on 25/08/2019]

Popper, Karl (1969) The Moral Responsibility of the Scientist. Encounter, March 1969, pp. 52-56 [Online] http://www.unz.com/print/Encounter-1969mar-00052 [Accessed on 25/08/2019]

Rotblat, Joseph (1999) A Hippocratic Oath for Scientists. Science, November 1999: Vol. 286, Issue 5444, pp. 1475 [Online] https://science.sciencemag.org/content/286/5444/1475.full [Accessed on 25/08/2019] DOI: 10.1126/science.286.5444.1475 
Salgani, Matthew J. (2017) Bit by Bit Bit - Social research in the digital age. Princeton, NJ: Princeton University Press. Open review edition.

Salganik, Matthew J. (2019) Bit by Bit Bit - Social research in the digital age. Princeton, NJ: Princeton University Press.

Sample, Ian (2019, Fri 16 Aug 2019)  and tech specialists need Hippocratic oath, says academic. The Guardian [Online] https://www.theguardian.com/science/2019/aug/16/mathematicians-need-doctor-style-hippocratic-oath-says-academic-hannah-fry [Accessed on 25/08/2019]

Vox.com (2018) The Cambridge Analytica Facebook scandal [Online] https://www.vox.com/2018/4/10/17207394/cambridge-analytica-facebook-zuckerberg-trump-privacy-scandal [Accessed on 26/08/2019]

### 2019-08-27 Opsætningexam/DraftExam.tex

@@
 \usepackage{amsmath}
-\usepackage{lmodern}
 \usepackage[T1]{fontenc}
@@
 
-\section{Data description}
+\section{Data description \& Ethics}
 
+\paragraph{Ethical considerations in the current research project\newline}
+In the current paper the appropriate care and consideration has been given to the ethical concerns regarding the scraping, processing, and the presentation of the data.
+Drawing upon the European Comissions\footnote{European Commission (2018).
+\textit{Ethics in Social Sciences and the Humanities}} ethical guidelines and principles for ethical conduct in social data science, the potential harm to users of Boliga's web-page were carefully considered.
+As a step to prevent the mosaic effect and in an effort to anonymize the scraped data only aggregated data will be presented in this paper, so that no single observation can be identified from the analysed data.\newline
+No informed consent has been obtained from the users of the site, prompting us to consider the consequences of the lack thereof, as informed consent is paramount to the proper, ethical conduct in social science.
+However, sometimes, as in this instance, informed consent can be logistically impossible to collect from all participants in the study.
+Salganik mentions that informed consent for everything is an ideal, but in practice impossible to obtain and researchers should instead strive to follow an alternative rule, that he describes as: "some form of consent for most things." \footnote{Salganik, Matthew J.
+(2019) \textit{Bit by Bit Bit - Social research in the digital age.} p.281} Adhering to this, more complex  understanding of the practicality of informed consent, we chose to contact Boliga to inform them of our intent to scrape their website and use the data in an educational context.
+Boliga responded positively to our inquiry, which we took as informed consent from a third party on behalf of the participating users in our study.\newline
+In considering the legal ramifications of our research and to make sure we adhere to the seven principles of GDPR, and other appropriate legislation and legal contracts, we consulted the general guidelines introduced by the Consumer Data Research Center.
+In particular we noted that we are justified to collect and use the data on the lawful basis of legitimate interests.
+Furthermore, we consulted with Boliga's Terms and Conditions to avoid any legal ramifications and the appropriate contractual terms of interest can be seen in \href{https://www.boliga.dk/vilkaar-og-betingelser}{§10 Terms and Conditions}.
+In order to comply with these terms we refrained from burdening their website's performance by implementing a time.sleep function, which causes each scraping iteration to pause for 0.5 seconds before commencing on scraping the next page (see appendix XX).
+Furthermore, Boliga prohibits the use of automated scrapers and bots, which we did not do, as our scraping was done in a specified time-frame and we did not automate the procedure to be done on multiple occasions.
 \subsection{Data sources}
@@
 
-\subsection{Regularization / Lasso og derved variable selection}
+\subsection{Regularization}
 The use of a sizeable amount of features leads to a significant risk of over-fitting the prediction model. 
-For the purpose of dealing with over-fitting, a form of regularization needs to be carried out.
-The Lasso-feature posses the attributes to do so.
+For the purpose of dealing with over-fitting, regularization needs to be carried out.
+Regularization can be done with different approaches, in this project three types are applied; Lasso, Ridge and Elastic-net.
+\subsubsection{Lasso}
 Regularization by Lasso, will penalize complexity of the model by adjustment of parameter estimates.
 This penalty will make the model less complex and more appropriate for prediction.
-\footnote{Big Data in Social Sciences, Forster et al.
-p.
-173}\, \footnote{Python Machine Learning, Sebastian Raschka et al.
-p.
+\footnote{Foster, Ian; Rayid Ghani Ron S.
+Jarmin, Frauke Kreuter, Julia Lane; \textit{Big Data in Social Sciences, A Practical Guide to Methods and Tools} p.
+173}\, \footnote{Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow} p.
 332}
-\newline Lasso solves the optimization problem: $$\hat{\beta}(\lambda)=\underset{\beta}{arg\min} \left(\frac{1}{N} \sum_{i=1}^{N} (Y_i-\hat{Y_i}(\beta)^2)+\lambda\sum_{j=1}^{p}|\beta_j|\right) \qquad s.t \quad \lambda \geq 0 $$
-Another convenient attribute of the Lasso penalty is that some estimates are set equal to zero \footnote{Hal R.
+\newline Lasso minimize: $$L_{Lasso}(\hat{\beta}) = \left(\sum_{i=1}^{n} (y_i-\hat{y_i}(\beta)^2)+\lambda\sum_{j=1}^{p}|\hat{\beta_j}|\right) \qquad s.t \quad \lambda \geq 0 $$
+Another convenient attribute of the Lasso penalty is that some estimates are set equal to zero and thereby produce sparse models\footnote{Hal R.
 Varian.
-Big data: New tricks for econometrics.
+\textit{Big data: New tricks for econometrics.
+Journal of Economic Perspectives}.
 p.19}.
 Lasso thereby performs the feature selection automatic.
+\subsubsection{Ridge}
+The ridge model add squared terms of the coefficient as penalty
+$$L_{Ridge}(\hat{\beta}) = \left(\sum_{i=1}^{n} (y_i-\hat{y_i}(\beta)^2)+\lambda\sum_{j=1}^{p}\hat{\beta_j}^2\right) \qquad s.t \quad \lambda \geq 0 $$ 
+Like Lasso, the Ridge model add bias in exchange for a decrease in variance. Resulting in a better prediction model.
 
-\subsection{Lars}
-
+\subsubsection{Elastic-net}
+The Elastic net is a combination of Lasso and Ridge. Elastic net minimizes the function: 
+$$L_{enet}(\hat{\beta}) = \frac{\sum_{i=1}^{n}\left(y_i-\hat{y_i}\right)^2}{2n} + \lambda\left(\frac{1-\alpha}{2}\sum_{j=1}^{P}\hat{\beta_j}^2+\alpha\sum_{j=1}^{P}|\hat{\beta_j}|\right) Note: Anderledes i Rashka!$$
+$$0 \leq \alpha \leq 1 \quad \wedge \quad \lambda \geq 0$$
+Where $\alpha$ denotes the relative mixing between Lasso and Ridge. 
 \subsection{K-fold Cross-Validation}
@@
 
+\section{Appendix}
+\paragraph{An Ethical Overview \newline}
+The ethical principles of social research are anchored in the fundamental human rights, which are broadly formulated in the UN Declaration of Human Rights.
+Additional policies and declarations that codify principles of research ethics and the ethical treatment of research participants include the Nuremberg Code, the Helsinki Declaration, the Belmont Report, and the Menlo Report\footnote{Salganik, Matthew J.
+(2019) \textit{Bit by Bit Bit - Social research in the digital age.}}\, \footnote{European Commission (2018).
+\textit{Ethics in Social Sciences and the Humanities}}.
+These codes and addendums originate mostly in the biomedical field, though they encompass the central principles applied to all human research, which have led some academics to call for a Hippocratic oath for data scientists to safeguard against powerful new technologies under development in laboratories and tech firms\footnote{Rotblat, Joseph (1999) \textit{A Hippocratic Oath for Scientists}}\, \footnote{Sample, Ian (2019, Fri 16 Aug 2019) \textit{and tech specialists need Hippocratic oath, says academic.}}.
+This discussion is nothing new however, as a tentative reformulation of the Hippocratic oath was introduced by Karl Popper\footnote{Popper, Karl (1969) \textit{The Moral Responsibility of the Scientist}}, wherein he stressed the importance of professional responsibility, a critical mind, and an overriding loyalty towards the betterment of mankind.\newline
+Matthew Salganik offer four principles deduced from the Belmont and Menlo Report that should guide the ethical deliberations of the researcher: 1) the respect for persons, that is individuals should be treated as autonomous and if circumstances require it individuals should be entitled to additional protections.
+2) Beneficence stresses the importance of doing no harm and to maximize the possible benefits and minimizing any potential harms.
+3) The principle of justice touches upon the importance of the distribution of burdens and benefits of the social scientist's research.
+This principle stress that is should not be a single stratum of society that bears the costs of the research while another stratum benefits.
+4) The fourth and final principle is the respect for law and public interest, according to Salganik, the principle consists of two distinct elements, that is compliance to relevant laws and legal contracts and transparency-based accountability.
+It is worth noting that Popper’s tentative Hippocratic oath mirrors the first three principles put forth by Salganik, stressing the importance of the ethical conduct of the researcher.\newline
+The need for rigid ethical standards within computational social science was made apparent by the Cambridge Analytica Scandal that broke on the 17th of March 2018.
+Where Steve Bannon could reveal that between 2013 and 2015 Cambridge Analytica had exploited a loophole in Facebook’s API which allowed the company to harvest profile data from 87 million Facebook users, without the user’s permission and use the harvested data to construct a massive targeted marketing database based on the user’s likes and interests\footnote{Vox.com (2018) \textit{The Cambridge Analytica Facebook scandal} [Online]}.
+Other examples of misuse of data acquired from Facebook include the Harvard-run experiment, where students' data was used to create new knowledge about how social networks form and how these networks and their actors' behavior co-evolve, and the emotional contagion experiment from 2012, where approximately 700,000 users were involved in a research experiment to examine the extent to which a person's emotions are affected by the emotions of the people they interact with (Salganik.
+2019).\newline
+From this it should be evident that clear ethical guidelines are required in order to protect the user's privacy from tech-savvy companies.
+To this end, the European Parliament introduced the General Data Protection Regulation (GDPR).
+With its seven overarching principles the GDPR seeks to formalize the procedures involved in the data processing and storing of sensitive and private information (CDRC\footnote{Consumer Data Research Center, UK  [CDRC] (2018) \textit{The General Data Protection Regulation \& Social Science Research} [Online]:}).
+These principles include and expand upon the principles found in the Belmont and Menlo Report.
+The most important consideration, however, must be that even a dataset comprising tens of thousands of observations involve human beings who must be protected from adverse side-effects of the social research.
+There is considerable evidence that point to the fact that even in anonymized data sets it can be possible to backtrack an individual's identity.
+A researcher must therefore be mindful of the mosaic effect if the dataset combines large amount of data from various sources (European Commission 2018).
+
 \newpage
@@
 
-Big Data in Social Sciences, Forster et al. 2017
-\newline Python Machine Learning, Sebastian Raschka et al. 2017, $2^{nd}$editon
-\newline Hal R. Varian. Big data: New tricks for econometrics. Journal of Economic Perspectives, 28(2):3–28, 2014.
+\ Foster, Ian; Rayid Ghani Ron S. Jarmin, Frauke Kreuter, Julia Lane; \textit{Big Data in Social Sciences, A Practical Guide to Methods and Tools}, CRS Press 2017
+
+Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow}, $2^{nd}$editon, Packt Publishing 2017.
+
+Hal R. Varian. \textit{Big data: New tricks for econometrics. Journal of Economic Perspectives}, 28(2):3–28, 2014.
+
+Consumer Data Research Center, UK  [CDRC] (2018) \textit{The General Data Protection Regulation \& Social Science Research} [Online]: \href{https://ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020_ethics-soc-science-humanities_en.pdf}{ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020\_ethics-soc-science-humanities\_en.pdf} [Accessed on 25/08/2019]
+
+European Commission (2018).
+\textit{Ethics in Social Sciences and the Humanities} [Online]: \href{https://ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020_ethics-soc-science-humanities_en.pdf}{https://ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020\_ethics-soc-science-humanities\_en.pdf} [Accessed on 25/08/2019]
+
+Popper, Karl (1969) \textit{The Moral Responsibility of the Scientist}.
+Encounter, March 1969, pp.
+52-56 [Online]: \href{http://www.unz.com/print/Encounter-1969mar-00052}{http://www.unz.com/print/Encounter-1969mar-00052} [Accessed on 25/08/2019]
+
+Rotblat, Joseph (1999) \textit{A Hippocratic Oath for Scientists}.
+Science, November 1999: Vol.
+286, Issue 5444, pp.
+1475 [Online]: \href{https://science.sciencemag.org/content/286/5444/1475.full}{https://science.sciencemag.org/content/286/5444/1475.full} [Accessed on 25/08/2019] DOI: 10.1126/science.286.5444.1475
+
+Salganik, Matthew J. (2019) \textit{Bit by Bit Bit - Social research in the digital age.} Princeton, NJ: Princeton University Press.
+
+Sample, Ian (2019, Fri 16 Aug 2019) \textit{and tech specialists need Hippocratic oath, says academic.} The Guardian [Online]: \href{https://www.theguardian.com/science/2019/aug/16/mathematicians-need-doctor-style-hippocratic-oath-says-academic-hannah-fry} [Accessed on 25/08/2019]
+
+Vox.com (2018) \textit{The Cambridge Analytica Facebook scandal} [Online]: \href{https://www.vox.com/2018/4/10/17207394/cambridge-analytica-facebook-zuckerberg-trump-privacy-scandal} [Accessed on 26/08/2019]
 

### 2019-08-27 Opsætningexam/DraftExam.tex
Latex update

@@
 \usepackage{hyperref}
+\usepackage{xcolor}
 
@@
 Furthermore, Boliga prohibits the use of automated scrapers and bots, which we did not do, as our scraping was done in a specified time-frame and we did not automate the procedure to be done on multiple occasions.
-\subsection{Data sources}
-Scraping from \textbf{\href{https://www.boliga.dk}{boliga.dk}} provides key characteristic such as price, squaremeters, location etc.   \newline
-The API \href{https://www.hvorlangterder.dk}{hvorlangterder.dk} returns measurements of distances from an address to conveniences such as hospitals, schools and shopping.
-Obtaining these distances for all of the listed housing and merging the two datasets, gives additional arguments to geographical-control.
-The data from hvorlangterder.dk can allow more micro-oriented differences within a given municipality.
-Which otherwise would not have been captured.
+\subsection{Data Scraping Process}
+In the following paragraphs our scraping efforts will be described. The scrapers can be examined in the attached Jupyter Notebooks labelled \textcolor{red}{XX and XX.} 
+\paragraph{\href{https://www.boliga.dk}{Boliga}\newline}
+Our data comes from \href{https://www.boliga.dk}{Boliga.dk}, the largest independent online web-portal for real-estate sales in Denmark and has access to unique features such as "liggetid", price-development and access to BBR - the Danish Building and Housing Register \footnote{\href{https://www.boligagruppen.dk}{www.boligagruppen.dk}}.
+Giving us unique insights into the pricing of real-estate in all 98 municipalities of Denmark.
+At the time of scraping 65,950 properties were for sale.\newline
+The scraping process was conducted on Friday the 23rd of August 2019.
+We had advised Boliga of our intent to collect data from their website via our scraper in an effort to identify ourselves and our intent\footnote{Shiab, Nael (2015) \textit{On the Ethics of Web Scraping and Data Journalism.
+Global Investigative Journalism Network.}} (Shiab 2015).
+In order to scrape the data of interest we familiarized ourselves with the HTML-structure of Boliga.
+On the basis of these insights we constructed a code, which were able to scrape every page, containing information pertaining the currently listed real-estates on Boliga.
+The scraper requested all information available from each individual page, which surmounted to 65,950 URL requests.
 \newline
-Social and economic factors on municipality level is collected from \href{https://statistik.politi.dk/QvAJAXZfc/opendoc.htm?document=QlikApplication%2F2999_Public\%2FPublic_IndsatsResultater.qvw}{statistik.politi.dk}   \newline
-\href{https://www.dst.dk/da/Statistik/emner/befolkning-og-valg}{Danmarks Statistik} respectively. These factors includes reported crime, income and level of completed education.
+For each URL, 34 features and the target variable (price) was collected.
+Table \textcolor{red}{XX} provides an overview of the features with a short description, and whether the feature has been dropped or saved for later usage.
+There are three reasons for a feature to be dropped:\newline
+1. The feature does not act with independent characteristics according to the our research,\newline
+2. The feature contains insufficient data,\newline
+3. The feature is poorly formatted and cannot efficiently be recreated.
+\paragraph{\href{https://www.hvorlangterder.dk}{Hvorlangterder.dk}\newline}
+The scraping of \href{https://www.hvorlangterder.dk}{hvorlangterder.dk} was achieved by writing a function that took in the GPS-coordinates gathered from Boliga and a list of points of interest.
+It then constructed an URL, which was then scraped and the json response was then returned as a dictionary of distances to the points of interest.
+The values from each key in the dictionary was then extracted as a new column in a Pandas DataFrame.\newline
+As Jupyter is bad for running long asynchronous tasks and an estimated running time of 18 hours this procedure was run in Visual Studio.
 
-\subsection{Data construction}
-Traffic offences are not considered as a "serious" offence and are therefore excluded in the crime statistics. 
-Socio-economic data is converted to ratios.
+\paragraph{Social and economic factors\newline}
+Social and economic factors on municipality level is collected from \href{https://statistik.politi.dk/QvAJAXZfc/opendoc.htm?document=QlikApplication%2F2999_Public\%2FPublic_IndsatsResultater.qvw}{statistik.politi.dk} and
+\href{https://www.dst.dk/da/Statistik/emner/befolkning-og-valg}{Danmarks Statistik} respectively.
+These factors includes income, reported crime and level of completed education etc.
+These are transformed to into ratios, by taking the total population in a given municipality into account.
 
@@
 \subsubsection{Ridge}
-The ridge model add squared terms of the coefficient as penalty
+The ridge model add squared terms of the coefficient as penalty. In opposed to Lasso, Ridge do not force features to be omitted. Ridge minimizes:
 $$L_{Ridge}(\hat{\beta}) = \left(\sum_{i=1}^{n} (y_i-\hat{y_i}(\beta)^2)+\lambda\sum_{j=1}^{p}\hat{\beta_j}^2\right) \qquad s.t \quad \lambda \geq 0 $$ 
-Like Lasso, the Ridge model add bias in exchange for a decrease in variance. Resulting in a better prediction model.
+Like Lasso, the Ridge model add bias in exchange for a decrease in variance, resulting in a better prediction model.
 
@@
 The Elastic net is a combination of Lasso and Ridge. Elastic net minimizes the function: 
-$$L_{enet}(\hat{\beta}) = \frac{\sum_{i=1}^{n}\left(y_i-\hat{y_i}\right)^2}{2n} + \lambda\left(\frac{1-\alpha}{2}\sum_{j=1}^{P}\hat{\beta_j}^2+\alpha\sum_{j=1}^{P}|\hat{\beta_j}|\right) Note: Anderledes i Rashka!$$
+$$L_{elasticnet}(\hat{\beta}) = \frac{\sum_{i=1}^{n}\left(y_i-\hat{y_i}\right)^2}{2n} + \lambda\left(\frac{1-\alpha}{2}\sum_{j=1}^{p}\hat{\beta_j}^2+\alpha\sum_{j=1}^{p}|\hat{\beta_j}|\right) Note: Anderledes i Rashka!$$
 $$0 \leq \alpha \leq 1 \quad \wedge \quad \lambda \geq 0$$
 Where $\alpha$ denotes the relative mixing between Lasso and Ridge. 
-\subsection{K-fold Cross-Validation}
-To get the optimal tuning parameter: $\lambda$ a k-fold cross-validation is performed. The 10-fold CV, divides the data into 10 subsets
+\subsection{Optimizing the Hyperparameter}
+To minimize the mean squared errors of our Lasso and Ridge regression we performed k-fold cross validation to optimize the hyperparameter $\lambda$. 
+We split the data into a test set and a development set, consisting of respectively 20\% and 80\% of the total observations.
+Subsequently, we use k-fold cross-validation to randomly split the development set into k folds, where k-1 folds are used to train the model.
+The remaining fold is used to validate the model’s generalizability by calculating the mean squared errors of the trained model’s prediction of the left-out fold\footnote{Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow}.
+p.191}.
+This process is repeated k times and each time a new fold is left out for validation.
+Since we are working with a relatively large dataset we chose to split our data into 5 folds, and computed the average MSE for the 5 iterations.
+By using the k-fold cross-validation method we relieve ourselves of the concern that the estimation of our model’s performance is simply due to a lucky or unlucky split of the data.
+\newline
+We performed this procedure for 12 different values of $\lambda$ spanning between \textcolor{red}{$10^(-4) and 10^4$}.
+We chose the value of $\lambda$ which yields the smallest average MSE over the 5 folds.
+We both calculated the optimal hyperparameters for a Ridge regression model, a Lasso regression model and an Elastic Net regression model.
+\textcolor{red}{The following table} shows the performance of the different models, when trained with their optimal hyperparameter and predicting the test data.
 
@@
 
-\section{Appendix}
-\paragraph{An Ethical Overview \newline}
+\section{An Ethical Overview}
+
 The ethical principles of social research are anchored in the fundamental human rights, which are broadly formulated in the UN Declaration of Human Rights.
@@
 
+Boligagruppen.dk (2019) \textit{Om boliga gruppen} [Online]: \href{https://www.boligagruppen.dk}{www.boligagruppen.dk}: [Accessed on 27/08/2019]
+
+Shiab, Nael (2015) \textit{On the Ethics of Web Scraping and Data Journalism.
+Global Investigative Journalism Network.} [Online]: \href{https://gijn.org/2015/08/12/on-the-ethics-of-web-scraping-and-data-journalism/}{gijn.org/2015/08/12/on-the-ethics-of-web-scraping-and-data-journalism/}: [Accessed on 27/08/2019]
 \end{document}

### 2019-08-27 Opsætningexam/DraftExam.tex
Updatelatex

@@
 
-\section{Data description \& Ethics}
+\section{Data Description \& Ethics}
 
-\paragraph{Ethical considerations in the current research project\newline}
+\subsection{Ethical Considerations in the Current Research Project}
 In the current paper the appropriate care and consideration has been given to the ethical concerns regarding the scraping, processing, and the presentation of the data.
@@
 These are transformed to into ratios, by taking the total population in a given municipality into account.
+\subsection{Merging Data}
 
-\subsection{Exclusion of outliers}
+\subsection{Data Cleaning}
 A few of the listed housing, have been for sale for over a decade.
@@
 The total number of excluded housing are approximately 4000.
-\newline
+
+\subsection{Describtive Statistics}
+\subsubsection{The Dataset}
+\subsubsection{Selecting Features}
+
 \begin{tabular}{| c | c | c | c | c | c |} 

### 2019-08-27 Opsætningexam/DraftExam.tex
d
push

@@
 \section{Introduction}
+
+\section{Literature Review}
 
@@
 As well as a classification-model for predicting the interval which the price is included in.
+\subsection{Fitting the model}
+The potential problems of underfitting and overfitting should be assessed when fitting a model.
+A model is underfitted if it hardly captures the variation of the sample data.
+It is then said that the model has \textit{high bias}.
+A model is overfitted, when it is overly sensitive to the idiosyncrasy of the sample data and captures the variation in too great detail.
+This problem often comes with the introduction of a sizeable number of features.
+Overfit models are said to have \textit{high variance}\footnote{Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow}.
+p.73}.
+In both cases, the model will generalize poorly.
+A key step in defining a decent model in machine learning is to find an optimal bias-variance-balance, by tuning the complexity of one’s model.
+This is done through \textit{regularization}.
 
-\subsection{Regularization}
+\subsubsection{Regularization}
+
 The use of a sizeable amount of features leads to a significant risk of over-fitting the prediction model. 
 For the purpose of dealing with over-fitting, regularization needs to be carried out.
-Regularization can be done with different approaches, in this project three types are applied; Lasso, Ridge and Elastic-net.
+Regularization can be done with different approaches, in this project three types are applied; Lasso, Ridge and Elastic net.
 \subsubsection{Lasso}
@@
 332}
-\newline Lasso minimize: $$L_{Lasso}(\hat{\beta}) = \left(\sum_{i=1}^{n} (y_i-\hat{y_i}(\beta)^2)+\lambda\sum_{j=1}^{p}|\hat{\beta_j}|\right) \qquad s.t \quad \lambda \geq 0 $$
+\newline Lasso minimize: $$L_{Lasso}(\hat{\beta}) = \left(\sum_{i=1}^{n} (y_i-\hat{y_i}(\beta))^2+\lambda\sum_{j=1}^{p}|\hat{\beta_j}|\right) \qquad s.t \quad \lambda \geq 0 $$
 Another convenient attribute of the Lasso penalty is that some estimates are set equal to zero and thereby produce sparse models\footnote{Hal R.
@@
 The ridge model add squared terms of the coefficient as penalty. In opposed to Lasso, Ridge do not force features to be omitted. Ridge minimizes:
-$$L_{Ridge}(\hat{\beta}) = \left(\sum_{i=1}^{n} (y_i-\hat{y_i}(\beta)^2)+\lambda\sum_{j=1}^{p}\hat{\beta_j}^2\right) \qquad s.t \quad \lambda \geq 0 $$ 
+$$L_{Ridge}(\hat{\beta}) = \left(\sum_{i=1}^{n} (y_i-\hat{y_i}(\beta))^2+\lambda\sum_{j=1}^{p}\hat{\beta_j}^2\right) \qquad s.t \quad \lambda \geq 0 $$ 
 Like Lasso, the Ridge model add bias in exchange for a decrease in variance, resulting in a better prediction model.
@@
 The Elastic net is a combination of Lasso and Ridge. Elastic net minimizes the function: 
-$$L_{elasticnet}(\hat{\beta}) = \frac{\sum_{i=1}^{n}\left(y_i-\hat{y_i}\right)^2}{2n} + \lambda\left(\frac{1-\alpha}{2}\sum_{j=1}^{p}\hat{\beta_j}^2+\alpha\sum_{j=1}^{p}|\hat{\beta_j}|\right) Note: Anderledes i Rashka!$$
+$$L_{elasticnet}(\hat{\beta}) = \frac{\sum_{i=1}^{n}\left(y_i-\hat{y_i}(\beta)\right)^2}{2n} + \lambda\left(\frac{1-\alpha}{2}\sum_{j=1}^{p}\hat{\beta_j}^2+\alpha\sum_{j=1}^{p}|\hat{\beta_j}|\right) Note: Anderledes i Rashka!$$
 $$0 \leq \alpha \leq 1 \quad \wedge \quad \lambda \geq 0$$
@@
 \section{Litterature}
-
 \ Foster, Ian; Rayid Ghani Ron S. Jarmin, Frauke Kreuter, Julia Lane; \textit{Big Data in Social Sciences, A Practical Guide to Methods and Tools}, CRS Press 2017

### 2019-08-27 Opsætningexam/DraftExam.tex
n

@@
 \usepackage{graphics}
-\usepackage[danish]{babel} 
 \usepackage{graphicx}
@@
 We had advised Boliga of our intent to collect data from their website via our scraper in an effort to identify ourselves and our intent\footnote{Shiab, Nael (2015) \textit{On the Ethics of Web Scraping and Data Journalism.
-Global Investigative Journalism Network.}} (Shiab 2015).
+Global Investigative Journalism Network.}}.
 In order to scrape the data of interest we familiarized ourselves with the HTML-structure of Boliga.
 On the basis of these insights we constructed a code, which were able to scrape every page, containing information pertaining the currently listed real-estates on Boliga.
-The scraper requested all information available from each individual page, which surmounted to 65,950 URL requests.
+The scraper requested all information available from each individual page, which surmounted to 1,319 URL requests.
 \newline
@@
 There are three reasons for a feature to be dropped:\newline
-1. The feature does not act with independent characteristics according to the our research,\newline
+1. The feature does not act with independent characteristics according to the research,\newline
 2. The feature contains insufficient data,\newline
@@
 \paragraph{\href{https://www.hvorlangterder.dk}{Hvorlangterder.dk}\newline}
+\href{https://www.hvorlangterder.dk}{hvorlangterder.dk} returns distances from a given address, to conveniences such as supermarkets, hospitals and schools.   
 The scraping of \href{https://www.hvorlangterder.dk}{hvorlangterder.dk} was achieved by writing a function that took in the GPS-coordinates gathered from Boliga and a list of points of interest.
-It then constructed an URL, which was then scraped and the json response was then returned as a dictionary of distances to the points of interest.
+It constructed a URL (65,950 URL request), which was scraped and the json response was returned as a dictionary of distances to the points of interest.
 The values from each key in the dictionary was then extracted as a new column in a Pandas DataFrame.\newline
-As Jupyter is bad for running long asynchronous tasks and an estimated running time of 18 hours this procedure was run in Visual Studio.
+As Jupyter performs poorly at running long asynchronous tasks and estimated a running time of 18 hours this procedure was run in Visual Studio.
 
@@
 \href{https://www.dst.dk/da/Statistik/emner/befolkning-og-valg}{Danmarks Statistik} respectively.
-These factors includes income, reported crime and level of completed education etc.
+These factors includes income, reported crime and level of highest completed education etc.
 These are transformed to into ratios, by taking the total population in a given municipality into account.
@@
 \subsection{Data Cleaning}
-A few of the listed housing, have been for sale for over a decade.
+
+A few of the listed housing, have been listed for over a decade.
 These are considered outliers, which are overly priced considering their characteristics.
-The outliers are excluded, because they would otherwise only contribute to a bias of overestimation.
+The outliers are excluded, because they would otherwise only contribute to further bias of overestimation.
 The total number of excluded housing are approximately 4000.
 
-\subsection{Describtive Statistics}
+\subsection{Descriptive Statistics}
 \subsubsection{The Dataset}
@@
 This is done through \textit{regularization}.
+In this project three different types of regularization are applied; Lasso, Ridge and Elastic net.
 
-\subsubsection{Regularization}
-
-The use of a sizeable amount of features leads to a significant risk of over-fitting the prediction model. 
-For the purpose of dealing with over-fitting, regularization needs to be carried out.
-Regularization can be done with different approaches, in this project three types are applied; Lasso, Ridge and Elastic net.
 \subsubsection{Lasso}
-Regularization by Lasso, will penalize complexity of the model by adjustment of parameter estimates.
+Regularization by Lasso, will penalize complexity of the model by the sum of the absolute value of the coefficients.
 This penalty will make the model less complex and more appropriate for prediction.
@@
 332}
-\newline Lasso minimize: $$L_{Lasso}(\hat{\beta}) = \left(\sum_{i=1}^{n} (y_i-\hat{y_i}(\beta))^2+\lambda\sum_{j=1}^{p}|\hat{\beta_j}|\right) \qquad s.t \quad \lambda \geq 0 $$
+\newline Lasso minimizes: $$L_{Lasso}(\hat{\beta}) = \left(\sum_{i=1}^{n} (y_i-\hat{y_i}(\beta))^2+\lambda\sum_{j=1}^{p}|\hat{\beta_j}|\right) \qquad s.t \quad \lambda \geq 0 $$
 Another convenient attribute of the Lasso penalty is that some estimates are set equal to zero and thereby produce sparse models\footnote{Hal R.
@@
 \subsubsection{Ridge}
-The ridge model add squared terms of the coefficient as penalty. In opposed to Lasso, Ridge do not force features to be omitted. Ridge minimizes:
+The ridge model penalizes with the sum of squared coefficients. Opposed to Lasso, Ridge do not force features to be omitted. Ridge minimizes:
 $$L_{Ridge}(\hat{\beta}) = \left(\sum_{i=1}^{n} (y_i-\hat{y_i}(\beta))^2+\lambda\sum_{j=1}^{p}\hat{\beta_j}^2\right) \qquad s.t \quad \lambda \geq 0 $$ 
-Like Lasso, the Ridge model add bias in exchange for a decrease in variance, resulting in a better prediction model.
+The Ridge model add bias in exchange for a decrease in variance, resulting in a better prediction model.
 

### 2019-08-27 Opsætningexam/Data sources/Data sources.tex
data sources

\documentclass[10pt,a4paper]{report}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\begin{document}
\paragraph{Data sources \newline}
In this section the data used in this report will be introduced. 
\subparagraph{Boliga\newline}
Data was collected from Boliga.dk which is one of the largest, independent web-portal for real-estate sales in Denmark. It has 1.1 million active views each month (boligagruppen.dk). The data scraped from Boliga provides unique insight into each real-estate posted on their website, such as pricing, m$^2$, municipality, coordinates, and access to the BBR - the Danish Building and Housing Register, which contains information about all Danish properties. 
\subparagraph{Additional features\newline}
As we want to predict the pricing of real-estates in the current market, we want to add additional features, which potentially could increase the predicting power of our model. \newline
\textbf{hvorlangterder.dk} is a find-closest demo developed by Viamap, a digital map provider. This API contains information about distances to distances from an address to conveniences such as hospitals, schools and shopping. Obtaining these distances for all of the listed housing
and merging the two datasets, gives additional arguments to geographical-control. The data
from hvorlangterder.dk can allow more micro-oriented differences within a given municipality. Which otherwise would not have been captured.\newline
Socioeconomic data on municipality level is collected from \textbf{statistikbanken.dk} \& \textbf{statistik.politi.dk}. 
These factors include measures for reported crime, socioeconomic index, mean income and level of completed education, etc. These measures are thought to influence the pricing of real estate in a given municipality.

\end{document}

### 2019-08-27 Opsætningexam/DraftExam.tex
u

@@
 \subsection{Descriptive Statistics}
+\begin{center}
+\begin{tabular}{| c | c | c | c | c | c |} 
+\hline
+   & Price & Rooms & $m^2$ & Average Municipal income \\ \hline
+   Mean & 2,312,798.00 & 4.21 & 127.82 & 312,957.03 \\ \hline
+   Std & 2,351,127.00 & 2.12 & 75.67 & 46,095.34 \\ \hline
+   Min & 15,000.00 & 0 & 0,0 & 257,776 \\ \hline
+   25\% & 985,000.00 & 3 & 82 & 290,973 \\ \hline
+   50\% & 1,695,000.00 & 4 & 123 & 302,153 \\ \hline
+   75\% & 2,895,000.00 & 5 & 167 & 318,745 \\ \hline
+   Max & 85,000,000.00 & 50 & 2,390 & 583,331 \\ \hline
+\end{tabular}
+\end{center}
+
 \subsubsection{The Dataset}
+The merged dataset contains 61.618 observations and 37 features.  
 \subsubsection{Selecting Features}
-
-\begin{tabular}{| c | c | c | c | c | c |} 
-  \toprule
-  \multicolumn{6}{|c|}{Danmark} \\ \hline
-   & \multicolumn{2}{c|}{Sjælland} & \multicolumn{3}{c|}{Ikke Sjælland} \\ \hline
-  Type/Region & Hovedstaden & Sjælland & Syddanmark & Midtjylland & Nordjylland \\
-   \midrule 
-   Villa & 513,36 & 459,67 & 503,62 & 461,96 & \\ \hline
-   Rækkehus & 470,67 & 404,95 & 460,93 & 407,24 & \\ \hline
-   Ejerlejlighhed & 482,30 & 463,94 & 455,87 & 449,54 & \\ \hline
-   Fritidsbolig & 513,36 & 459,67 & 503,62 & 461,96 & \\ \hline
-   Kolonihave & 470,67 & 404,95 & 460,93 & 407,24 & \\ \hline
-   Andelsbolig & 482,30 & 463,94 & 455,87 & 449,54 & \\ \hline
-   Landejendom & 513,36 & 459,67 & 503,62 & 461,96 & \\ \hline
-   Helårsgrund & 470,67 & 404,95 & 460,93 & 407,24 & \\ \hline
-   Fritidsgrund & 482,30 & 463,94 & 455,87 & 449,54 & \\ \hline
-   Villalejlighed & 513,36 & 459,67 & 503,62 & 461,96 & \\ \hline
-   Lystejendom & 470,67 & 404,95 & 460,93 & 407,24 & \\ 
-    \bottomrule
-\end{tabular}
-\newline
 
@@
 The Elastic net is a combination of Lasso and Ridge. Elastic net minimizes the function: 
-$$L_{elasticnet}(\hat{\beta}) = \frac{\sum_{i=1}^{n}\left(y_i-\hat{y_i}(\beta)\right)^2}{2n} + \lambda\left(\frac{1-\alpha}{2}\sum_{j=1}^{p}\hat{\beta_j}^2+\alpha\sum_{j=1}^{p}|\hat{\beta_j}|\right) Note: Anderledes i Rashka!$$
+$$L_{elasticnet}(\hat{\beta}) = \frac{\sum_{i=1}^{n}\left(y_i-\hat{y_i}(\beta)\right)^2}{2n} + \lambda\left(\frac{1-\alpha}{2}\sum_{j=1}^{p}\hat{\beta_j}^2+\alpha\sum_{j=1}^{p}|\hat{\beta_j}|\right)$$
 $$0 \leq \alpha \leq 1 \quad \wedge \quad \lambda \geq 0$$

### 2019-08-27 Opsætningexam/DraftExam.tex
up

@@
 \onehalfspacing
-\usepackage[danish]{babel}
 \usepackage{graphicx}
@@
 \usepackage{times}
-\usepackage{gauss}
 \usepackage{fancyhdr}
@@
 \usepackage{xcolor}
-
+\usepackage{booktabs,siunitx}
+\usepackage{float}
 \lhead{}
@@
 \subsection{Descriptive Statistics}
+\begin{table}[h!]
 \begin{center}
+\caption{Key Statistics\label{time}}
 \begin{tabular}{| c | c | c | c | c | c |} 
 \hline
-   & Price & Rooms & $m^2$ & Average Municipal income \\ \hline
-   Mean & 2,312,798.00 & 4.21 & 127.82 & 312,957.03 \\ \hline
+   & Price & \, Rooms \ & \ $m^2$ \ & Average Municipal Income \\ \hline
+   Mean & 2,312,798.00 & \ 4.21 \  & \ 127.82 \ & 312,957.03 \\ \hline
    Std & 2,351,127.00 & 2.12 & 75.67 & 46,095.34 \\ \hline
-   Min & 15,000.00 & 0 & 0,0 & 257,776 \\ \hline
+   Min & 15,000.00 & 0 & 0 & 257,776 \\ \hline
    25\% & 985,000.00 & 3 & 82 & 290,973 \\ \hline
@@
 \end{center}
+\end{table} 
+\begin{figure}[H]
+  \centering
+   \caption{}
+   \includegraphics[width=\linewidth]{Barplot_Estate2.png} 
+  \label{fig:}
+\end{figure}
 
 \subsubsection{The Dataset}
-The merged dataset contains 61.618 observations and 37 features.  
+The merged dataset contains 61.618 observations and 37 features.   The features are of both categorical and continuous measures.
+
 \subsubsection{Selecting Features}
@@
 \textcolor{red}{The following table} shows the performance of the different models, when trained with their optimal hyperparameter and predicting the test data.
+\section{Analysis}
 
-\section{Analysis}
+\begin{table}[h!]
+\begin{center}
+\caption{Key Statistics\label{time}}
+\begin{tabular}{| c | c | c | c | c | c |} 
+\hline
+   & Price & \, Rooms \ & \ $m^2$ \ & Average Municipal Income \\ \hline
+   Mean & 2,312,798.00 & \ 4.21 \  & \ 127.82 \ & 312,957.03 \\ \hline
+   Std & 2,351,127.00 & 2.12 & 75.67 & 46,095.34 \\ \hline
+   Min & 15,000.00 & 0 & 0 & 257,776 \\ \hline
+   25\% & 985,000.00 & 3 & 82 & 290,973 \\ \hline
+   50\% & 1,695,000.00 & 4 & 123 & 302,153 \\ \hline
+   75\% & 2,895,000.00 & 5 & 167 & 318,745 \\ \hline
+   Max & 85,000,000.00 & 50 & 2,390 & 583,331 \\ \hline
+\end{tabular}
+\end{center}
+\end{table}
 

### 2019-08-27 hvorlang_scrape.py
sdf

@@ -7,7 +7,7 @@ import random
 import json
 import tqdm
 
-logfile = 'Hvorlangterder_full2_log.csv'
+logfile = 'Hvorlangterder_total_log.csv'
 connector = scraping_class.Connector(logfile)
 
 df = pd.read_csv('Boliga - Behandling 2 - Befolkningstal.csv')
@@ -22,11 +22,11 @@ def create_url_and_scrape(lat_long):
     tempurl = url + ','.join(poitypes) + coordinates + auth
     #time.sleep(0.3)
     print(1)
-    response = requests.get(tempurl)
+    response, call_id = connector.get(tempurl,'Coordinates_datascience')
     js = response.json()
     data = dict()
-    data['lake'] = js['lake']['routedmeters'] 
-    data['forest'] = js['forest']['routedmeters'] 
+    data['lake'] = js['lake']['routedmeters']
+    data['forest'] = js['forest']['routedmeters']
     data['doctor'] = js['doctor']['routedmeters']
     data['supermarket'] = js['supermarket']['routedmeters']
     data['school'] = js['school']['routedmeters']
@@ -43,4 +43,4 @@ def create_url_and_scrape(lat_long):
     return data
 df['hvorlangt_total'] = df['coordinate'].apply(create_url_and_scrape)
 
-df.to_csv('howlongdf.csv')
+df.to_csv('howlongdf2.csv')

### 2019-08-27 Opsætningexam/DraftExam.tex
up

@@
 \section{Introduction}
+This report depicts a research performed regarding active Danish real-estate property valuations from 2016-2019.
+Since 2011, the yearly number of real estate properties sold has slightly increased, with 2017 being the year with most sold properties in 10 years (Danmarks Statistik, 2018).
+The price of real estate properties is also rising through 2019 (Danmarks Statistik, 2019).
+Although this generally depicts a willingness of buyers to pay more for real-estate property, and higher valuations from agents, a closer analysis of current and active valuations contributes with local view of which conditions contribute to the valuation of a real-estate property.
+\newline
+\begin{figure}[H]
+\centering
+\caption{}
+\includegraphics[scale=1]{123.png}
+\end{figure}
+
+Figure 1 shows the average square meter price valuation of active offers per municipality in Denmark.
+The maximum square meter price being approximately 8 times higher in the municipality of Gentofte, than Lolland, the municipality with lowest average square meter price valuations.
+A tendency visualized in the figure, is that average square meter price valuations are higher in in highly populated municipalities and in suburban areas surrounding Copenhagen.
+\newline
+
+The valuations included in the research are collected from one of Denmarks largest online real-estate websites named Boliga.dk.
+The Boliga data contains approximately 66 thousand active offerings with valuations ranging from 15 thousand to 85 million.
+This research paper intends to analyze real estate price valuations and which effects geo- and sociodemographic criteria affect valuations, using machine learning models.
+Our research questions is as follows:
+Which features are most relevant for predicting evaluations of real estate properties in Denmark?
+
+The research paper contains a section describing the construction of research data was performed explains the choices of gathering meaningful features for the machine learning model.
+Also, a section revolving the choice and optimization of machine learning models is included, where the intention is to provide insights on our progress on finding the optimal model.
+As a result, a preferable machine learning model is chosen with a discussion of its usability.
 
@@
 3. The feature is poorly formatted and cannot efficiently be recreated. 
+\vspace*{10px} \newline
+\textit{Features Obtained:} \newline
+\begin{tabular}{c c}
+Continuous: & basementSize, buildYear, Ejerudgift, lotSize	, price, rooms, size  \\	
+\end{tabular}\newline 
+\begin{tabular}{c c}
+Categorical: & ForClosure, Type, Municipality, lotSize	, price, rooms, size  \\	
+\end{tabular}\newline
+
 \paragraph{\href{https://www.hvorlangterder.dk}{Hvorlangterder.dk}\newline}
@@
 As Jupyter performs poorly at running long asynchronous tasks and estimated a running time of 18 hours this procedure was run in Visual Studio.
-
+ \vspace*{10px} \newline
+\textit{Features obtained:}\newline
+\begin{tabular}{c c}
+Distances to: & lake, forest, doctor, supermarket,	school, daycare, hospital, train \\	
+\end{tabular}\newline 
+\begin{tabular}{c c}
+\qquad \qquad \qquad \qquad &  pharmacy, library, coast, junction \\	
+\end{tabular}\newline 
 \paragraph{Social and economic factors\newline}
@@
 These are transformed to into ratios, by taking the total population in a given municipality into account.
+ \vspace*{5px} \newline
+\begin{tabular}{c c}
+\textit{Features obtained:}: & Relativ Ledighed, Grundskole, Gymnasiale uddannelser \\	
+\end{tabular}\newline 
+\begin{tabular}{c c}
+\qquad \qquad \qquad \qquad \quad & Erhvervsfaglige uddannelser,	 KVU, 	MVU, Bacheloruddannelser  \\	
+\end{tabular}\newline 
+\begin{tabular}{c c}
+\qquad \qquad \qquad \qquad \quad & LVU, Kommunal\_gennemsnitsinkomst\_2017, Total\_reported\\	
+\end{tabular}\newline 
+\begin{tabular}{c c}
+\qquad \qquad \qquad \qquad \quad & Population\_in\_urban\_development  , Socioeconomic\_index \\	
+\end{tabular}\newline 
+\begin{tabular}{c c}
+\qquad \qquad \qquad \qquad \quad & average\_class\_size	expenses\_sport\_and\_other\_cultural\_activities	  \\	
+\end{tabular}\newline 
+\begin{tabular}{c c}
+\qquad \qquad \qquad \qquad \quad & , expenses\_per\_school\_student	   \\	
+\end{tabular}\newline 
+% 				average_class_size	expenses_sport_and_other_cultural_activities
 \subsection{Merging Data}
@@
 \subsubsection{The Dataset}
-The merged dataset contains 61.618 observations and 37 features.   The features are of both categorical and continuous measures.
+The merged dataset contains 61.618 observations and 37 features.   The features are of both categorical and continuous measures. \newline
 
@@
 \section{Discussion}
-
 \subsection{Data critique}
@@
 are subject to significant bias, since the cooperative housing that enters the marked through a realtor often would be those with critical amount of undesirable characteristics.
+
 \section{Conclusion}

### 2019-08-28 Opsætningexam/DraftExam.tex
update

@@
 The price of real estate properties is also rising through 2019 (Danmarks Statistik, 2019).
-Although this generally depicts a willingness of buyers to pay more for real-estate property, and higher valuations from agents, a closer analysis of current and active valuations contributes with local view of which conditions contribute to the valuation of a real-estate property.
+Although this generally depicts a willingness of buyers to pay more for real-estate property, and higher valuations from agents, a closer analysis of current and active valuations add a local view of which conditions contribute to the valuation of a real-estate property.
 \newline
@@
 The valuations included in the research are collected from one of Denmarks largest online real-estate websites named Boliga.dk.
-The Boliga data contains approximately 66 thousand active offerings with valuations ranging from 15 thousand to 85 million.
+The Boliga data contains approximately 66,000 dkk.
+active offerings with valuations ranging from 15,000 to 85 million dkk.
 This research paper intends to analyze real estate price valuations and which effects geo- and sociodemographic criteria affect valuations, using machine learning models.
@@
 
-The research paper contains a section describing the construction of research data was performed explains the choices of gathering meaningful features for the machine learning model.
-Also, a section revolving the choice and optimization of machine learning models is included, where the intention is to provide insights on our progress on finding the optimal model.
+This research paper contains a section describing the construction of research data and assesses the choices made in gathering meaningful features for the machine learning model.
+Also, a section regarding the choice and optimization of machine learning models is included, where the intention is to provide insights on our progress on finding the optimal model.
 As a result, a preferable machine learning model is chosen with a discussion of its usability.
@@
 \href{https://www.hvorlangterder.dk}{hvorlangterder.dk} returns distances from a given address, to conveniences such as supermarkets, hospitals and schools.   
-The scraping of \href{https://www.hvorlangterder.dk}{hvorlangterder.dk} was achieved by writing a function that took in the GPS-coordinates gathered from Boliga and a list of points of interest.
-It constructed a URL (65,950 URL request), which was scraped and the json response was returned as a dictionary of distances to the points of interest.
-The values from each key in the dictionary was then extracted as a new column in a Pandas DataFrame.\newline
+The scraping of \href{https://www.hvorlangterder.dk}{hvorlangterder.dk} was achieved by writing a function that took in the GPS-coordinates gathered from Boliga.
+It constructed a URL (65,950 URL request), \textcolor{red}{which was scraped and the json response was returned as a dictionary of distances to the points of interest.
+The values from each key in the dictionary was then extracted as a new column in a Pandas DataFrame}.\newline
 As Jupyter performs poorly at running long asynchronous tasks and estimated a running time of 18 hours this procedure was run in Visual Studio.
@@
 \end{tabular}\newline
+
 \paragraph{Social and economic factors\newline}
@@
 \href{https://www.dst.dk/da/Statistik/emner/befolkning-og-valg}{Danmarks Statistik} respectively.
-These factors includes income, reported crime and level of highest completed education etc.
-These are transformed to into ratios, by taking the total population in a given municipality into account.
+These factors include income, reported crime, level of highest completed education etc.
+These are transformed into ratios, by taking the total population in a given municipality into account.
  \vspace*{5px} \newline
@@
 \begin{tabular}{c c}
-\qquad \qquad \qquad \qquad \quad & average\_class\_size	expenses\_sport\_and\_other\_cultural\_activities	  \\	
+\qquad \qquad \qquad \qquad \quad & average\_class\_size,	expenses\_sport\_and\_other\_cultural\_activities	  \\	
 \end{tabular}\newline 
 \begin{tabular}{c c}
-\qquad \qquad \qquad \qquad \quad & , expenses\_per\_school\_student	   \\	
+\qquad \qquad \qquad \qquad \quad & expenses\_per\_school\_student	   \\	
 \end{tabular}\newline 
@@
 
+n.b. 0
+
 \subsubsection{The Dataset}
@@
 The objective by applying Machine Learning is to train a model that can predict pricing of housing listed in near future.
-Two types of predictive models will be used for the sake of returning different outputs: Regression-model to return the pricing as a continuous output.
-As well as a classification-model for predicting the interval which the price is included in.
+\textcolor{red}{Two types of predictive models will be used for the sake of returning different outputs: Regression-model to return the pricing as a continuous output.}  
 \subsection{Fitting the model}
@@
 $$L_{Ridge}(\hat{\beta}) = \left(\sum_{i=1}^{n} (y_i-\hat{y_i}(\beta))^2+\lambda\sum_{j=1}^{p}\hat{\beta_j}^2\right) \qquad s.t \quad \lambda \geq 0 $$
-The Ridge model add bias in exchange for a decrease in variance, resulting in a better prediction model.
 
@@
 Where $\alpha$ denotes the relative mixing between Lasso and Ridge.
+
+\subsection{Perfomance, Precision \& Recall}
+
 \subsection{Optimizing the Hyperparameter}
@@
 \textcolor{red}{The following table} shows the performance of the different models, when trained with their optimal hyperparameter and predicting the test data.
+
 \section{Analysis}
+
+\section{Results}
 
@@
 \begin{center}
-\caption{Key Statistics\label{time}}
+\caption{Prediction Errors\label{time}}
 \begin{tabular}{| c | c | c | c | c | c |} 
 \hline
-   & Price & \, Rooms \ & \ $m^2$ \ & Average Municipal Income \\ \hline
-   Mean & 2,312,798.00 & \ 4.21 \  & \ 127.82 \ & 312,957.03 \\ \hline
-   Std & 2,351,127.00 & 2.12 & 75.67 & 46,095.34 \\ \hline
-   Min & 15,000.00 & 0 & 0 & 257,776 \\ \hline
-   25\% & 985,000.00 & 3 & 82 & 290,973 \\ \hline
-   50\% & 1,695,000.00 & 4 & 123 & 302,153 \\ \hline
-   75\% & 2,895,000.00 & 5 & 167 & 318,745 \\ \hline
-   Max & 85,000,000.00 & 50 & 2,390 & 583,331 \\ \hline
+   & Lasso & \, Ridge \ & \ Elastic Net \ & OLS \\ \hline
+   MSE & 60,103,955,188.37 & \ 55,667,264,851.14 \  & \ 85,824,334,267.16 \ & 2.848e+28 \\ \hline
+  RMSE & 245,161.08 & 235,939.11 & 292,957.91 & 168,763,945,674,352.3 \\ \hline
+   MAE & 47,126.43 & 43,630.55 & 69,582.56 & 2,637,476,978,906.39 \\ \hline
+
 \end{tabular}
@@
 \end{table}
-
-\section{Results}
 

### 2019-08-28 Opsætningexam/Data cleaning/Data cleaning.tex
data cleaning

\documentclass[10pt,a4paper]{report}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\begin{document}
\section{Data cleaning}
The scraping of Boliga left us with 65,950 observations. However, big data is often dirty and requires tidying before it can be used in any meaningful statistical context (Salganik 2018). In the following sections we describe our data cleaning efforts. 
\subsection{Initial clean-up}
The initial clean-up sorted out rows that contained an illogical value. Here we focused our efforts on the removing any and all observations that contained a municipality code of 0. Additionally, we chose to exclude any real estate valued below 100 DKK, while these listings existed on Boliga's website, they were all listings, where the seller wanted  to sell to the highest bidder. We excluded these listings on the basis that they were unrealistically priced compared to the property's real market value.\newline
Boliga subdivides its listings into ten real-estate types. We chose to exclude the typification "other", as there were only 17 houses listed in the category - too few for training our machine learning model. Furthermore, we also removed any listing without coordinates as these were vital for the scraping process on hvorlangerder.dk.\newline
We dropped all observations with an unreasonably high "liggetid", as we saw these instances to not  represent reasonable pricing or demand. We have thus set an arbitrary limit of 3 years (1,095 days), and omitted any observations that has been on the market for longer than that. This results in the omission of approximately 5\% of our dataset. The highest mean "liggetid" on a municipal level was roughly 600 days, so as not to discriminate against the observations from the municipalities with a longer average 'sales time' we set the cut-off somewhat higher than the highest mean. Another option was to set the limit according to each municipality's mean, a solution that was a bit more time consuming, and would have yielded approximately the same result, hence we opted not to do it.
In figure XX the number of rows dropped at each step of the cleaning can be perused.
\begin{center}
\begin{tabular}{|l|c|}
\hline 
Feature & \emph{n} \\
\hline 
Municipality code & 231 \\ 
\hline 
Price & 11 \\ 
\hline 
Coordinates & 275 \\ 
\hline 
Type & 17 \\ 
\hline 
Liggetid & 3,940\\
\hline 
Total\footnote{"The total is the count of how many rows were dropped. Some rows were missing multiple features.} & 4,332\\
\hline
\end{tabular} 
\end{center}

\subsection{Ejerlejlighed's lot size}
Inspecting our data we found that from 8,028 apartments 1,176 of these had a lot size. These listings included the apartment complex' common area, whereas the rest did not. To overcome this discrepancy we chose to set all non-zero values to zero, as not to confuse our model with an inconsistent feature (Raschka \& Mirjalili 2017).

\subsection{Final touch-ups}
After merging the housing info with the demographic data and the distances from hvorlangterder.dk, we removed a single duplicate and deleted all columns not relevant for our analysis. After the clean-up of the data we were left with a dataset consisting of 61,618 observations and 37 features and 1 target variable.

\end{document}

### 2019-08-29 Opsætningexam/DraftExam.tex

@@
 \usepackage{float}
+\usepackage{caption}
 \lhead{}
 \rhead{}
-\chead{}
+\chead{Social Data Science, Summer 2019.}
 
@@
 This report depicts a research performed regarding active Danish real-estate property valuations from 2016-2019.
-Since 2011, the yearly number of real estate properties sold has slightly increased, with 2017 being the year with most sold properties in 10 years (Danmarks Statistik, 2018).
-The price of real estate properties is also rising through 2019 (Danmarks Statistik, 2019).
+Since 2011, the yearly number of real estate properties sold has slightly increased, with 2017 being the year with most sold properties in 10 years \href{https://www.dst.dk/da/Statistik/nyt/NytHtml?cid=27979}{(Danmarks Statistik, 2018)}.
+The price of real estate properties is also rising through 2019 \href{https://www.dst.dk/da/Statistik/nyt/NytHtml?cid=28741}{(Danmarks Statistik, 2019)}.
 Although this generally depicts a willingness of buyers to pay more for real-estate property, and higher valuations from agents, a closer analysis of current and active valuations add a local view of which conditions contribute to the valuation of a real-estate property.
 \newline
-\begin{figure}[H]
+\newcommand{\source}[1]{\caption*{Source: {#1}} }\begin{figure}[H]
 \centering
 \caption{}
-\includegraphics[scale=1]{123.png}
+\includegraphics[scale=0.4]{123.png}
+\source{Own creation, with data from \href{https://www.boliga.dk}{Boliga.dk}}
 \end{figure}
@@
 The valuations included in the research are collected from one of Denmarks largest online real-estate websites named Boliga.dk.
-The Boliga data contains approximately 66,000 dkk.
-active offerings with valuations ranging from 15,000 to 85 million dkk.
+The Boliga data contains approximately 66,000 active offerings with valuations ranging from 15,000 to 85 mil.dkk.
 This research paper intends to analyze real estate price valuations and which effects geo- and sociodemographic criteria affect valuations, using machine learning models.
 Our research questions is as follows:
-Which features are most relevant for predicting evaluations of real estate properties in Denmark?
-
+\begin{center}
+ \textit{Which features are most relevant for predicting evaluations of real estate properties in Denmark?}
+\end{center}
 This research paper contains a section describing the construction of research data and assesses the choices made in gathering meaningful features for the machine learning model.
@@
 \section{Literature Review}
+Within data social science there exist widely differing definitions of big data and machine learning. This section seeks to clarify the use of these terms within the scope of this paper.
+\paragraph{On big data \& machine learning\newline}
+Historically, big data has been a term reserved for data that was unable to be processed by extant software.
+However, recent increases in computational power has enabled data processing of hitherto unheard of quantities of data\footnote{Lazer, David and Jason Radford (2017) \textit{Data ex Machina.
+Introduction to Big Data}.
+Annual Review of Sociology}.
+Today, big data is no longer too cumbersome to analyse.
+Matthew Salganik\footnote{Salganik, Matthew J.
+(2018) \textit{Bit by Bit Bit - Social research in the digital age.}} instead mentions ten typical characteristics of big data.
+Salganik's tentative definition suggests that big data is not as single entity, but includes many different types of systems.
+Among the most important features of Salganik's definition of big data is that the data has a high frequency of observations and is continuously being generated.
+Since the data is always-on it is also drifting, meaning that the structure and population it represents is ever-changing.
+It is therefore important to understand that big data is not a naturally occurring system, but driven by the engineered purpose of the system.
+This algorithmic confounding forces the scientist to be careful regarding any observed human behaviour that is extracted from a single digital system.\newline
+In the analysis of big data it is often useful to employ machine learning as it can identify and predict various nonlinear relationships in big data sets, that otherwise would remain hidden.
+Data scientists' have for the most part optimised the predictive capabilities of the algorithm applied, and as a consequence they have often ignored or trivialised machine learning's potential in causal modelling\footnote{Varian.
+Hal R.
+\textit{Big data: New tricks for econometrics}}.\newline
+The technical and theoretical challenges faced by big data and machine learning research are important to consider, when employing the tools they provide.
+One of the major discussions revolve around machine learning's predictive capabilities.
+Chris Anderson\footnote{Anderson, Chris (2008) \textit{The end of theory: The data deluge makes the scientific method obsolete}} (2008) argues that since the computing power and the scale of data has increased exponentially, our reliance of scientific models could become obsolete.
+Instead of focusing on the theoretical implications of observations, scientists should, according to Anderson, focus on the statistical outputs: In the age of big data, correlation perhaps should supersede causality and consequently social data scientists should not try to develop coherent models or unified theories to explain a social phenomenon.\newline
+However, many social data scientists argue against this point of view.
+Justin Grimmer\footnote{Grimmer, Justin (2015) \textit{We are all social scientists now: how big data, machine learning, and causal inference work together}} claims, that correlations extracted from big data cannot stand alone.
+Large quantities of data is not sufficient to make scientifically valid causal inferences.
+It requires a rigorous research design and clear theoretical assumptions, in order to yield scientifically accurate estimates.
+Indeed social sciences greatest contribution to big data research, comes from the organized framework provided by rigorously tested theory\footnote{Einav, Liran and Jonathan Levin (2014) \textit{Economics in the age of big data}}.\newline
+The contribution from the social sciences to machine learning help create new methods that will be able to utilize the strengths of machine learning to help solve causal inference problems within the framework of a well defined theory\footnote{Athey, Susan (2018) 'The Impact of Machine Learning on Economics' in Ajay Agrawal et al.
+(eds) \textit{The Economics of Artificial Intelligence: An Agenda}}.
+These new approaches could help define what variables to manipulate and how to properly use machine learning within the framework of theoretical assumptions.
+Ultimately, big data and machine learning could increase the scope of the social scientist's field, not only by delivering new data and methods, but by helping the social scientist to focus on new questions\footnote{Mullainathan, Sendhil, and Jann Spiess (2017) \textit{Machine Learning: An Applied Econometric Approach}}.
 
@@
 Salganik mentions that informed consent for everything is an ideal, but in practice impossible to obtain and researchers should instead strive to follow an alternative rule, that he describes as: "some form of consent for most things." \footnote{Salganik, Matthew J.
-(2019) \textit{Bit by Bit Bit - Social research in the digital age.} p.281} Adhering to this, more complex  understanding of the practicality of informed consent, we chose to contact Boliga to inform them of our intent to scrape their website and use the data in an educational context.
+(2018) \textit{Bit by Bit Bit - Social research in the digital age.} p.303} Adhering to this, more complex  understanding of the practicality of informed consent, we chose to contact Boliga to inform them of our intent to scrape their website and use the data in an educational context.
 Boliga responded positively to our inquiry, which we took as informed consent from a third party on behalf of the participating users in our study.\newline
@@
 The scraping process was conducted on Friday the 23rd of August 2019.
-We had advised Boliga of our intent to collect data from their website via our scraper in an effort to identify ourselves and our intent\footnote{Shiab, Nael (2015) \textit{On the Ethics of Web Scraping and Data Journalism.
-Global Investigative Journalism Network.}}.
+We had advised Boliga of our intent to collect data from their website via our scraper in an effort to identify ourselves and our intent\footnote{Shiab, Nael (2015) \textit{On the Ethics of Web Scraping and Data Journalism}.
+Global Investigative Journalism Network.}.
 In order to scrape the data of interest we familiarized ourselves with the HTML-structure of Boliga.
@@
 \begin{tabular}{c c}
-Continuous: & basementSize, buildYear, Ejerudgift, lotSize	, price, rooms, size  \\	
+Continuous: & basementSize, buildYear, ownersExspenses, lotSize	, price, rooms, size  \\	
 \end{tabular}\newline 
@@
 Categorical: & ForClosure, Type, Municipality, lotSize	, price, rooms, size  \\	
-\end{tabular}\newline
-
+\end{tabular}
 \paragraph{\href{https://www.hvorlangterder.dk}{Hvorlangterder.dk}\newline}
@@
 \qquad \qquad \qquad \qquad &  pharmacy, library, coast, junction \\	
-\end{tabular}\newline
-
+\end{tabular}
 \paragraph{Social and economic factors\newline}
@@
 \begin{tabular}{c c}
-\textit{Features obtained:}: & Relativ Ledighed, Grundskole, Gymnasiale uddannelser \\	
+\textit{Features obtained:}: & unemployment\_relative, primary\_school\_educ, high\_school\_educ \\	
 \end{tabular}\newline 
 \begin{tabular}{c c}
-\qquad \qquad \qquad \qquad \quad & Erhvervsfaglige uddannelser,	 KVU, 	MVU, Bacheloruddannelser  \\	
+\small (relative to population) & vocational\_educ,	 SHE, 	MHE, bachelors\_degree  \\	
 \end{tabular}\newline 
 \begin{tabular}{c c}
-\qquad \qquad \qquad \qquad \quad & LVU, Kommunal\_gennemsnitsinkomst\_2017, Total\_reported\\	
+\qquad \qquad \qquad \qquad \quad & LHE, avg\_municipal\_income\_2017, Total\_reported\_crime\\	
 \end{tabular}\newline 
@@
 \end{tabular}\newline 
-% 				average_class_size	expenses_sport_and_other_cultural_activities
+\small {All educational features are a measure of highest completed education. Furthermore SHE, MHE, LHE are abbreviations of short-, medium- and long-cycle higher education}. 
+\normalsize
+\subsection{Log Analysis}
+
 \subsection{Merging Data}
+Pandas objects can be combined in different ways according to the nature of features in the dataset.
+Relational database style operations are based on linking keys together, thereby maintaining the relationship between the combined datasets\footnote{McKinney, W.
+(2018).
+\textit{Data Wrangling: Join, Combine and Reshape}.
+p.
+231 }
+
+The data collection and scraping process provided a total of 15 Datasets from Boliga, Hvorlangterder, DAWA, the Danish Police, Social- \& Indenrigsministeriet and Danmarks Statistik.
+This section will describe how each dataset was merged, using pandas relational database styled merge and join operations.
+
+\paragraph{Boliga.dk\newline}
+An evaluation of the Boliga datasets features and their ability to support further data collection led to the utilization of the following features:
+
+-	[Longitude, Latitude]: Geographical placements of the properties
+
+-	Municipality: a numeric code for municipalities in Denmark
+
+The Boliga dataset acts as a master dataset and was joined or merged upon throughout the process, and acts as the “left” of all operations.
+The Longitude and Latitude features serve as specific coordinates for valued properties but are in few cases repetitive regarding different apartments from the same complex.
+The municipality code was used for translation purposes between the master dataset and other datasets.
+
+\paragraph{DAWA\newline}
+The DAWA dataset was scraped with an input of a distinct municipality code from the master dataset, returning a dataframe of municipality names for each code.
+This dataframe was merged onto the Boliga dataframe as a many-to-one merge with municipality code as the merge keys.
+The scraped municipality names from DAWA was used as the merge key for all further merges of municipal data.
+
+\paragraph{Danmarks Statistik, Danish Police \& Social og Indenrigsministeriet\newline}
+Of the municipality-based data collected, the merging of these to our master dataframe was subsequently performed identically.
+Every dataset contained a column for unique municipality names and values for the given feature of the dataset.
+A many-to-one left merge was performed with the master dataframe, using municipality names.
+The result being a master dataframe containing municipal specific features for properties.
+
+The Danish Police datasets contained totals for different categories of crimes reported within municipalities.
+These datasets were outer joined with an index set to contain municipality names.
+Afterwards, the values were added to each other, providing a total of reported crimes within each municipality.
+The police statistics webpage does not specify whether different types of reported crimes can relate to a single case, but we assessed that the number of crimes reported provides a meaningful feature either way.
+The dataset containing total reported crimes per municipality, was merged with the master dataset in the same fashion as previous municipality-based features.
+
+\paragraph{Hvorlangterder.dk\newline}
+The hvorlangterder scrape provided location specific features, taking an input of Latitude and Longitude coordinates.
+The scraping function, which was created for returning location-based features, created a column for the row specific values.
+Therefore, a merge operation was not necessary, but could alternatively have been managed with a one-to-one inner-merge id.
+As few coordinates regarding apartment properties are repetitive, these are not suitable for merging upon.
 
 \subsection{Data Cleaning}
+The scraping of Boliga left us with 65,950 observations.
+However, big data is often dirty and requires tidying before it can be used in any meaningful statistical context (Salganik 2018).
+In the following sections we describe our data cleaning efforts.
+\subsubsection{Initial clean-up}
+The initial clean-up sorted out rows that contained an illogical value.
+Here we focused our efforts on the removing any and all observations that contained a municipality code of 0.
+Additionally, we chose to exclude any real estate valued below 100 DKK, while these listings existed on Boliga's website, they were all listings, where the seller wanted  to sell to the highest bidder.
+We excluded these listings on the basis that they were unrealistically priced compared to the property's real market value.\newline
+Boliga subdivides its listings into ten real-estate types.
+We chose to exclude the typification "other", as there were only 17 houses listed in the category - too few for training our machine learning model.
+Furthermore, we also removed any listing without coordinates as these were vital for the scraping process on hvorlangerder.dk.\newline
+We dropped all observations with an unreasonably high "liggetid", as we saw these instances to not  represent reasonable pricing or demand.
+We have thus set an arbitrary limit of 3 years (1,095 days), and omitted any observations that has been on the market for longer than that.
+This results in the omission of approximately 5\% of our dataset.
+The highest mean "liggetid" on a municipal level was roughly 600 days, so as not to discriminate against the observations from the municipalities with a longer average 'sales time' we set the cut-off somewhat higher than the highest mean.
+Another option was to set the limit according to each municipality's mean, a solution that was a bit more time consuming, and would have yielded approximately the same result, hence we opted not to do it.
+In figure XX the number of rows dropped at each step of the cleaning can be perused.
+\begin{center}
+\begin{tabular}{|l|c|}
+\hline 
+Feature & \emph{n} \\
+\hline 
+Municipality code & 231 \\ 
+\hline 
+Price & 11 \\ 
+\hline 
+Coordinates & 275 \\ 
+\hline 
+Type & 17 \\ 
+\hline 
+Liggetid & 3,940\\
+\hline 
+Total\footnote{"The total is the count of how many rows were dropped. Some rows were missing multiple features.} & 4,332\\
+\hline
+\end{tabular} 
+\end{center}
 
-A few of the listed housing, have been listed for over a decade.
-These are considered outliers, which are overly priced considering their characteristics.
-The outliers are excluded, because they would otherwise only contribute to further bias of overestimation.
-The total number of excluded housing are approximately 4000.
+\subsubsection{Ejerlejlighed's lot size}
+Inspecting our data we found that from 8,028 apartments 1,176 of these had a lot size.
+These listings included the apartment complex' common area, whereas the rest did not.
+To overcome this discrepancy we chose to set all non-zero values to zero, as not to confuse our model with an inconsistent feature (Raschka \& Mirjalili 2017).
+
+\subsubsection{Final touch-ups}
+After merging the housing info with the demographic data and the distances from hvorlangterder.dk, we removed a single duplicate and deleted all columns not relevant for our analysis.
+After the clean-up of the data we were left with a dataset consisting of 61,618  observations and 37 features and 1 target variable.
 
 \subsection{Descriptive Statistics}
-\begin{table}[h!]
+In this section, we will examine the more apparent patterns of our collected data. This is done to familiarize ourselves with the data, before we commence on the analysis.
+\subsubsection{Key Statistics}
+Some key statistical characteristic is presented in table 1:
+\begin{table}[H]
 \begin{center}
@@
 \end{table} 
+Initially, it should be addressed that some of the properties has 0 rooms and consists of 0 $m^2$.
+This is due to the fact that we have also included land on which housing has not yet been build.
+Examining the 25\%-quintile and the 75\%-quintile of the valuation prices, it becomes apparent that there are some substantial outliers both to the cheaper and to expensive side.
+This is also the case with rooms and $m^2$, where the highest values are sizably higher than the 75\%-quintile.
+It is worth noting, that there is quite a big difference between the lowest average municipal income of DKK 257,776.
+and the highest of DKK 583,331.
+This difference becomes further noteworthy when assessing the 75\%-quintile.
+The difference from the 75\%-quintile to the highest average municipal income is more than 4 times the difference of the 75\%-quintile and the lowest income.
+The income distribution is visualised in the following figure:
 \begin{figure}[H]
@@
    \caption{}
-   \includegraphics[width=\linewidth]{Barplot_Estate2.png} 
+   \includegraphics[width=\linewidth]{Box1.png} 
   \label{fig:}
 \end{figure}
+The boxplot illustrates that the distribution is heavily left-skewed, where some municipalities has a sizably higher average income than the rest of the Danish municipalities.
 
-n.b. 0
+\subsubsection{Prices in Municipalities}
+We plot the average square meter valuation price in the different municipalities:
+\begin{figure}[H]
+  \centering
+   \caption{}
+   \includegraphics[width=\linewidth]{Box2.png} 
+  \label{fig:}
+\end{figure}
+It becomes apparent that the distribution is quite left-skewed and that there are a few municipalities who’s price per square meter is much higher than the rest of the municipalities.
+Recalling the geoplot in figure 1, these expensive outliers are heavily concentrated around- and north of Copenhagen.
+The distribution looks similar to that of figure 2 (The previous boxplot), though we cannot declare any correlation between average municipal income and average municipal price per square meter.
+Nonetheless, it becomes apparent that the valuation price of property is highly discriminated by municipal factors.
+The scope of this assignment is exactly to examine these factors and attempt to use these to evaluate an unseen, out-of-sample property.
+
+\subsubsection{Property Type}
+Another worthwhile consideration is that we have included all types of properties.
+It would be reasonable to assume that there is an average difference in valuation pricing depending on the type of property.
+Figure 4 displays the median valuation price for each type:
+\begin{figure}[H]
+  \centering
+   \caption{}
+   \includegraphics[width=\linewidth]{bar1.png} 
+  \label{fig:}
+\end{figure}
+It is interesting to note that the most expensive properties are apartments as opposed to houses.
+This is not especially surprising though, as it is a well-established trend that real estate prices in major cities are skyrocketing.
+Refraining from delving deeper into to a discussion of global urbanization, we retain the fact that property type does have an apparently significant effect on valuation pricings on average.
+We will include the ‘type’ feature in our impending model training to control for this effect.
 
 \subsubsection{The Dataset}
-The merged dataset contains 61.618 observations and 37 features.   The features are of both categorical and continuous measures. \newline
-
-\subsubsection{Selecting Features}
+The merged dataset contains 61.618 observations and 37 features.   The features are of both categorical and continuous measures. Skal dette ikke bare op i Merging data?\newline
 
@@
 \subsection{Supervised Machine Learning}
-The objective by applying Machine Learning is to train a model that can predict pricing of housing listed in near future.
-\textcolor{red}{Two types of predictive models will be used for the sake of returning different outputs: Regression-model to return the pricing as a continuous output.}  
+The objective by applying Machine Learning is to train a model that are able to make predictions in near future or never seen data.
+By feeding a model with labeled data as well as data samples, ML will define the algorithms that predicts the best\footnote{Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow}.
+p.
+3}.
+This project, implements a ML regression prediction model to predict pricing of housing listed in near future.
 \subsection{Fitting the model}
@@
 Varian.
-\textit{Big data: New tricks for econometrics.
-Journal of Economic Perspectives}.
+\textit{Big data: New tricks for econometrics}.
+Journal of Economic Perspectives.
 p.19}.
@@
 \subsubsection{Ridge}
-The ridge model penalizes with the sum of squared coefficients. Opposed to Lasso, Ridge do not force features to be omitted. Ridge minimizes:
+The ridge model penalizes with the sum of squared coefficients.
+Opposed to Lasso, Ridge do not force features to be omitted.
+Instead Ridge penalizes the parameter estimates and decreases them towards zero.
+Ridge minimizes:
 $$L_{Ridge}(\hat{\beta}) = \left(\sum_{i=1}^{n} (y_i-\hat{y_i}(\beta))^2+\lambda\sum_{j=1}^{p}\hat{\beta_j}^2\right) \qquad s.t \quad \lambda \geq 0 $$
@@
 \subsubsection{Elastic-net}
-The Elastic net is a combination of Lasso and Ridge. Elastic net minimizes the function: 
+The Elastic net combines the penalizing terms of Lasso and Ridge, with $\alpha$ defining the relative weights between Lasso and Ridge. Elastic net minimizes the function: 
 $$L_{elasticnet}(\hat{\beta}) = \frac{\sum_{i=1}^{n}\left(y_i-\hat{y_i}(\beta)\right)^2}{2n} + \lambda\left(\frac{1-\alpha}{2}\sum_{j=1}^{p}\hat{\beta_j}^2+\alpha\sum_{j=1}^{p}|\hat{\beta_j}|\right)$$
 $$0 \leq \alpha \leq 1 \quad \wedge \quad \lambda \geq 0$$
-Where $\alpha$ denotes the relative mixing between Lasso and Ridge.
 
-\subsection{Perfomance, Precision \& Recall}
+\subsection{Selecting Features}
+In case regularization is not sufficient to cope with the overfitting of the model.
+Exclusion of features are a viable approach.
+With the number of scraped features in this project, taking into consideration.
+A recurring overfitting of the model would be likely.
+As a consequence a deliberate exclusion of features of interest will need to be carried out.
 
@@
 
+\subsection{Predictive Performance}
+With the hyperparameters optimized, final model performance can be evaluated.
+Once more a cross-validation is carried out, which return the average performance-error of each model.
+By retraining the models on the complete training set and testing on the independent test set, performance measures are obtained\footnote{Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow}.
+p.192}.
+\newline The performances of the models are simply measured by MSE, RMSE and MAE.
+\newline
+$$ MSE = \frac{1}{n}\sum_{i=1}^{n}(y_i-\hat{y_i})^2$$
+
+$$ RMSE = \sqrt{\frac{1}{n}\sum_{i=1}^{n}(y_i-\hat{y_i})^2}$$
+$$ MAE = \frac{1}{n}\sum_{i=1}^{n}|y_i-\hat{y_i}|$$
+
 \section{Analysis}
+A number of features are excluded before the training of the model.
+The exclusion was determined, quite simply, by investigation of the correlation between the complete set of features and the valuation price.
+A list of the excluded features are found in appendix 11.0.1.
+The model used for ML are found in appendix 11.0.2.
 
-\section{Results}
+The initial 10-fold cross-validation to obtain the optimal values of the hyperparameters in each regularization yields.
+\begin{table}[h!]
+\begin{center}
+\caption{Optimal hyperparameters\label{time}}
+\begin{tabular}{ c  c  c } 
+   $\lambda_{Lasso}$ & $\lambda_{Ridge}$ &  $\lambda_{Elastic Net}$ \\ \hline
+   1 & 1 & 1 \\ \hline
+\end{tabular}
+\end{center}
+\end{table} 
+The prediction-error of each model
 
@@
    MAE & 47,126.43 & 43,630.55 & 69,582.56 & 2,637,476,978,906.39 \\ \hline
-
 \end{tabular}
@@
 
+\section{Results}
+\begin{figure}[H]
+\centering
+\caption{Predicted Valuation vs. Actual Valuation}
+%\includegraphics[scale=0.4]{}
+%\source{Own creation, with data from \href{https://www.boliga.dk}{Boliga.dk}}
+\end{figure}
+
 \section{Discussion}
 \subsection{Data critique}
-Another interesting prediction which could have been obtained using the same methods, would have been to estimate expected selling prices.
+Another interesting prediction which could have been done using the same methods, would have been to predict selling prices.
 This could have been done simply by scraping data on sold housing instead.
 This could be of more value for private agents, whose main interest should be the selling price of their housing.
+%This approach would undoubtedly get a greater data basis.
+needs to add time series trends
 \newline 
@@
 A significant amount of potential important factors can not be acquired.
-For an example the view from the listed housing will for sure have great impact of the valuation price.
-Another factor of interest could have been a evaluation of the condition of the housing, unfortunately the "statement of property" red.
-(tilstandrapport) are not publicly accessible.
+For an example the view from the listed housing will for sure be of great impact of the valuation price.
+Another factor of interest could have been a evaluation of the condition of the housing, unfortunately the statement of property\footnote{red.
+Tilstandsrapport} are not publicly accessible.
 \newline
@@
 are subject to significant bias, since the cooperative housing that enters the marked through a realtor often would be those with critical amount of undesirable characteristics.
+Like debt - which deflate the valuation accordingly.
+
+\subsection{Model Limitations and Irrelevancy}
+The necessity to exclude municipality dummies as regressors in the prediction models.
+Leaves the model to only separate municipalities by the socio-economic factors, which are subject to low variance.
+This makes distinction between municipality a lot more difficult as well as uncertain.
+Without the municipality dummies, the interpretation of the prediction results are more insecure.
+%Instead of predicting the valuation of a given estate, of a given type, in a given municipality or city.
+It predicts the valuation of a estate at a \textit{more or less} location in Denmark by type, only geographically controlled by distances to various conveniences.
+Geographical boundaries could have been limited way more, resulting in easier interpretation of predictions. Potentially by predicting only for a specific city or municipality. \\
+If one intended to predict valuations country-wide more realistic, a model for each municipality could have been more satisfactory.
+Resulting in 98 separate models.
+The evident downside of this approach being the prospect of limitations in available data (some municipalities has very few listings).
+Another approach could have been to group cities which share characteristics. Ex. The three biggest cities, the provinces, the islands, the country-side towns.
 
 \section{Conclusion}
-
+Even after regularization, and deliberate exclusion of features. Our model still suffers from overfitting. 
 \section{An Ethical Overview}
-
 The ethical principles of social research are anchored in the fundamental human rights, which are broadly formulated in the UN Declaration of Human Rights.
 Additional policies and declarations that codify principles of research ethics and the ethical treatment of research participants include the Nuremberg Code, the Helsinki Declaration, the Belmont Report, and the Menlo Report\footnote{Salganik, Matthew J.
-(2019) \textit{Bit by Bit Bit - Social research in the digital age.}}\, \footnote{European Commission (2018).
+(2018) \textit{Bit by Bit Bit - Social research in the digital age.}}\, \footnote{European Commission (2018).
 \textit{Ethics in Social Sciences and the Humanities}}.
@@
 Other examples of misuse of data acquired from Facebook include the Harvard-run experiment, where students' data was used to create new knowledge about how social networks form and how these networks and their actors' behavior co-evolve, and the emotional contagion experiment from 2012, where approximately 700,000 users were involved in a research experiment to examine the extent to which a person's emotions are affected by the emotions of the people they interact with (Salganik.
-2019).\newline
+2018).\newline
 From this it should be evident that clear ethical guidelines are required in order to protect the user's privacy from tech-savvy companies.
@@
 \section{Litterature}
-\ Foster, Ian; Rayid Ghani Ron S. Jarmin, Frauke Kreuter, Julia Lane; \textit{Big Data in Social Sciences, A Practical Guide to Methods and Tools}, CRS Press 2017
+\ Foster, Ian; Rayid Ghani Ron S. Jarmin, Frauke Kreuter, Julia Lane; \textit{Big Data in Social Sciences, A Practical Guide to Methods and Tools}, CRS Press 2017 \newline
 
-Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow}, $2^{nd}$editon, Packt Publishing 2017.
+Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow}, $2^{nd}$editon, Packt Publishing 2017. \newline
 
-Hal R. Varian. \textit{Big data: New tricks for econometrics. Journal of Economic Perspectives}, 28(2):3–28, 2014.
+Varian. Hal R. \textit{Big data: New tricks for econometrics}. Journal of Economic Perspectives, 28(2):3–28, 2014. \newline
 
-Consumer Data Research Center, UK  [CDRC] (2018) \textit{The General Data Protection Regulation \& Social Science Research} [Online]: \href{https://ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020_ethics-soc-science-humanities_en.pdf}{ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020\_ethics-soc-science-humanities\_en.pdf} [Accessed on 25/08/2019]
+Consumer Data Research Center, UK  [CDRC] (2018) \textit{The General Data Protection Regulation \& Social Science Research} [Online]: \href{https://ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020_ethics-soc-science-humanities_en.pdf}{ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020\_ethics-soc-science-humanities\_en.pdf} [Accessed on 25/08/2019]\newline
 
 European Commission (2018).
-\textit{Ethics in Social Sciences and the Humanities} [Online]: \href{https://ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020_ethics-soc-science-humanities_en.pdf}{https://ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020\_ethics-soc-science-humanities\_en.pdf} [Accessed on 25/08/2019]
+\textit{Ethics in Social Sciences and the Humanities} [Online]: \href{https://ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020_ethics-soc-science-humanities_en.pdf}{https://ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020\_ethics-soc-science-humanities\_en.pdf} [Accessed on 25/08/2019] \newline
 
@@
 Encounter, March 1969, pp.
-52-56 [Online]: \href{http://www.unz.com/print/Encounter-1969mar-00052}{http://www.unz.com/print/Encounter-1969mar-00052} [Accessed on 25/08/2019]
+52-56 [Online]: \href{http://www.unz.com/print/Encounter-1969mar-00052}{http://www.unz.com/print/Encounter-1969mar-00052} [Accessed on 25/08/2019]\newline
 
@@
 286, Issue 5444, pp.
-1475 [Online]: \href{https://science.sciencemag.org/content/286/5444/1475.full}{https://science.sciencemag.org/content/286/5444/1475.full} [Accessed on 25/08/2019] DOI: 10.1126/science.286.5444.1475
+1475 [Online]: \href{https://science.sciencemag.org/content/286/5444/1475.full}{https://science.sciencemag.org/content/286/5444/1475.full} [Accessed on 25/08/2019] DOI: 10.1126/science.286.5444.1475 \newline
 
-Salganik, Matthew J. (2019) \textit{Bit by Bit Bit - Social research in the digital age.} Princeton, NJ: Princeton University Press.
+Salganik, Matthew J. (2018) \textit{Bit by Bit Bit - Social research in the digital age.} Princeton, NJ: Princeton University Press.\newline
 
-Sample, Ian (2019, Fri 16 Aug 2019) \textit{and tech specialists need Hippocratic oath, says academic.} The Guardian [Online]: \href{https://www.theguardian.com/science/2019/aug/16/mathematicians-need-doctor-style-hippocratic-oath-says-academic-hannah-fry} [Accessed on 25/08/2019]
+Sample, Ian (2019, Fri 16 Aug 2019) \textit{and tech specialists need Hippocratic oath, says academic.} The Guardian [Online]: \href{https://www.theguardian.com/science/2019/aug/16/mathematicians-need-doctor-style-hippocratic-oath-says-academic-hannah-fry} [Accessed on 25/08/2019]\newline
 
-Vox.com (2018) \textit{The Cambridge Analytica Facebook scandal} [Online]: \href{https://www.vox.com/2018/4/10/17207394/cambridge-analytica-facebook-zuckerberg-trump-privacy-scandal} [Accessed on 26/08/2019]
+Vox.com (2018) \textit{The Cambridge Analytica Facebook scandal} [Online]: \href{https://www.vox.com/2018/4/10/17207394/cambridge-analytica-facebook-zuckerberg-trump-privacy-scandal} [Accessed on 26/08/2019] \newline
 
-Boligagruppen.dk (2019) \textit{Om boliga gruppen} [Online]: \href{https://www.boligagruppen.dk}{www.boligagruppen.dk}: [Accessed on 27/08/2019]
+Boligagruppen.dk (2019) \textit{Om boliga gruppen} [Online]: \href{https://www.boligagruppen.dk}{www.boligagruppen.dk}: [Accessed on 27/08/2019] \newline
 
 Shiab, Nael (2015) \textit{On the Ethics of Web Scraping and Data Journalism.
-Global Investigative Journalism Network.} [Online]: \href{https://gijn.org/2015/08/12/on-the-ethics-of-web-scraping-and-data-journalism/}{gijn.org/2015/08/12/on-the-ethics-of-web-scraping-and-data-journalism/}: [Accessed on 27/08/2019]
+Global Investigative Journalism Network.} [Online]: \href{https://gijn.org/2015/08/12/on-the-ethics-of-web-scraping-and-data-journalism/}{gijn.org/2015/08/12/on-the-ethics-of-web-scraping-and-data-journalism/}: [Accessed on 27/08/2019] \newline
+
+McKinney, W. (2018). 'Data Wrangling: Join, Combine and Reshape'. In W. McKinney, \textit{Python for Data Analysis}. Sebastopol: O'Reilly Media Inc. \newline
+
+Athey, Susan (2018) 'The Impact of Machine Learning on Economics' in Ajay Agrawal et al.
+(eds) \textit{The Economics of Artificial Intelligence: An Agenda} (2019).
+Chicago: University of Chicago Press.
+\newline
+
+Einav, Liran and Jonathan Levin (2014) \textit{Economics in the age of big data}. Science, vol. 346, November. \newline
+
+Grimmer, Justin (2015) \textit{We are all social scientists now: how big data, machine learning, and causal inference work together}.
+PS: Political Science \& Politics, vol.
+48, January: 80-83.
+\newline
+
+Lazer, David and Jason Radford (2017) \textit{Data ex Machina. Introduction to Big Data. Annual Review of Sociology}, vol. 43, August. \newline
+
+Mullainathan, Sendhil, and Jann Spiess (2017) \textit{Machine Learning: An Applied Econometric Approach}. Journal of Economic Perspectives, vol. 31 (2): 87-106. \newline
+
+Anderson, Chris (2008) \textit{The end of theory: The data deluge makes the scientific method obsolete}.
+Wired, 16-07 [Online] \href{https://www.wired.com/2008/06/pb-theory/}{www.wired.com/2008/06/pb-theory/} [Accessed on 27/08/2019]
+
+%Varian, Hal R. (2014) Big Data: New Tricks for Econometrics. Journal of Economic Perspectives. Vol. 28, April: 3-27 \newline
+
+\newpage
+\section{Appendixs}
+\subsubsection{}
+Excluded Features:\newline
+municipality, lotSize, unemployment, Total\_reported\_crime, Socioeconomic\_index, expenses\_per\_school\_student, expenses\_sport\_and\_other\_cultural\_activities, forest\_distance, coast\_distance, isForeclosure, owners\_expense
+\subsubsection{}
+The model used for prediction
+$$ \hat{Y_i}=\alpha+\hat{\beta}^T\textbf{X}_i+\hat{\epsilon_i}$$
+$$\textbf{X}_i=\begin{bmatrix}
+           basementSize \\
+           buildYear \\
+           rooms \\
+           size \\
+           primarySchool\_educ \\
+           high\_school\_educ \\
+           vocational\_educ \\
+           SHE \\
+           MHE \\
+           bachelors\_degree \\
+           LHE \\
+           avg\_municipal\_income\_2017 \\
+           Population\_in\_urban\_development \\
+           Socioeconomic\_index \\
+           lake\_distance\\
+           doctor\_distance \\
+           supermarket\_distance \\
+           school\_distance \\
+           daycare\_distance \\
+           hospital\_distance \\
+           train\_distance \\
+           pharmacy\_distance \\
+           library\_distance \\
+         \end{bmatrix}$$
 \end{document}

### 2019-08-29 Opsætningexam/DraftExam.tex
Få rettelser
e

@@
 
-\subsection{Model Limitations and Irrelevancy}
+\subsection{Model Limitations}
 The necessity to exclude municipality dummies as regressors in the prediction models.
@@
 \section{Conclusion}
-Even after regularization, and deliberate exclusion of features. Our model still suffers from overfitting. 
+In this assignment, we have used machine learning to train a model to predict valuation prices of real estate in Denmark.
+We did this by scraping Boliga.dk for all of their active houses for sale and combining this with municipal data on income, education, schools and urbanization.
+Additionally, we also scraped data from hvorlangterder.dk which calculates the distance from an address, to different every-day commodities such as hospitals, schools and shopping.
+We have explained how we carried out our gathering of data, how we have structured the data and how we cleaned it.
+
+We performed descriptive statistics on the data to gain a better acquaintance with the data. 
+We conducted feature selection by assessing the correlation between the different features and the target variable, which in our assignment has been the valuation price. 
+We trained both a Lasso- and a Ridge regression model and compared their performances with the performance of a standard linear regression.
+Though k-fold cross-validation, we estimated the optimized hyperparameters for both regularization models.
+We found that the Ridge regression performed best on average, with the performance measure being the smallest mean square error of the model.
+We have assessed to which degree we have managed to find a good bias-variance-balance for our model and concluded that our model suffers from a degree of overfitting.
+This was done by examining the validation curve of our final model.
+
+Finally, we have discussed the results of our analysis. We have critically assessed the boundaries of our research and drawn up potential possibilities for improvement.
+
 \section{An Ethical Overview}

### 2019-08-29 Opsætningexam/DraftExam.tex
d

@@
 \section{Analysis}
-A number of features are excluded before the training of the model.
+A number of features are excluded before training the model.
 The exclusion was determined, quite simply, by investigation of the correlation between the complete set of features and the valuation price.
@@
 
-The initial 10-fold cross-validation to obtain the optimal values of the hyperparameters in each regularization yields.
+The initial 5-fold cross-validation to obtain the optimal values of the hyperparameters in each regularization yields. 
 \begin{table}[h!]
 \begin{center}
-\caption{Optimal hyperparameters\label{time}}
-\begin{tabular}{ c  c  c } 
-   $\lambda_{Lasso}$ & $\lambda_{Ridge}$ &  $\lambda_{Elastic Net}$ \\ \hline
-   1 & 1 & 1 \\ \hline
+\caption{Optimal hyperparameters, two degrees polynomial features\label{time}}
+\begin{tabular}{ c | c  c  c } 
+  & $\lambda_{Lasso}$ & $\lambda_{Ridge}$ &  $\lambda_{Elastic Net}$ \\ \hline
+2 degrees  & 372.76 & 26.83 & 1 \\ \hline
+3 degrees  & 2310.13 & 432.88 & 1
 \end{tabular}
@@
 \end{table}
-The prediction-error of each model
 
-\begin{table}[h!]
+The prediction-errors of each model, with two and three degrees of polynomial features respectively, are printed below:
+\begin{table}[H]
 \begin{center}
-\caption{Prediction Errors\label{time}}
+\caption{Prediction Errors. \label{time}}
 \begin{tabular}{| c | c | c | c | c | c |} 
 \hline
-   & Lasso & \, Ridge \ & \ Elastic Net \ & OLS \\ \hline
-   MSE & 60,103,955,188.37 & \ 55,667,264,851.14 \  & \ 85,824,334,267.16 \ & 2.848e+28 \\ \hline
-  RMSE & 245,161.08 & 235,939.11 & 292,957.91 & 168,763,945,674,352.3 \\ \hline
-   MAE & 47,126.43 & 43,630.55 & 69,582.56 & 2,637,476,978,906.39 \\ \hline
+   & \ MSE \ & \, RMSE \ & \ MAE \ \\ \hline
+   Lasso 2-deg & 59,081,597,331.11 & \ 243,067.06 \  & \ 47,660.52 \ \\ 
+  Ridge 2-deg & 62,416,553,466.45 & 249,833.05 & 51,306.19  \\ 
+  Elastic net 2-deg & 1 & 1 & 1  \\ 
+  OLS 2-deg & 64,297,245,726.80 & 253,569.02 & 52,035.52  \\ \hline 
+  Lasso 3-deg & 60,103,955,188.37 & 245,161.08 & 47,126.43  \\ 
+  Ridge 3-deg & 55,667,264,851.14 & 235,939.11 & 43,630.55  \\ 
+  Elastic Net 3-deg & 1 & 1 & 1  \\
+  OLS 3-deg & 2.848e+28 & 168,763,945,674,352.3 & 2,637,476,978,906.39  \\ \hline
 \end{tabular}
@@
 \end{table}
+The Ridge model with three degrees of polynomial features are selected as the best performing model. Both according to MAE
+
+\begin{figure}[H]
+\centering
+\caption{}
+\includegraphics[scale=1]{ValCurveRidge3deg.png}
+%\source{}
+\end{figure}
 
@@
 Another approach could have been to group cities which share characteristics. Ex. The three biggest cities, the provinces, the islands, the country-side towns.
+
+\subsection{Model Selection}
+Instead of only assessing the different models by MAE and RMSE.
+The Information criteria of the respective models could have been introduced.
+Which could have altered the selection of preferred model.
+Both AIC and BIC, would likely have suggested Lasso, with 2-degrees of polynomial features, as preferred model.
+As both measurement are increasing in numbers of estimated parameters.
 
@@
 Anderson, Chris (2008) \textit{The end of theory: The data deluge makes the scientific method obsolete}.
-Wired, 16-07 [Online] \href{https://www.wired.com/2008/06/pb-theory/}{www.wired.com/2008/06/pb-theory/} [Accessed on 27/08/2019]
+Wired, 16-07 [Online] \href{https://www.wired.com/2008/06/pb-theory/}{www.wired.com/2008/06/pb-theory/} [Accessed on 27/08/2019]\newline
+
+Peckov, Aleksandar.
+(2012)  \textit{A Machine Learning Approach To Polynomial Regression}.
+Available at \href{http://kt.ijs.si/theses/phd_aleksandar_peckov.pdf}{kt.ijs.si/theses/phd\_aleksandar\_peckov.pdf}.
+Doctoral Dissertation.
+Jozef Stefan International Postgraduate School.
+Ljubljana, Slovenia, October 2012
 
@@
 \subsubsection{}
-The model used for prediction
-$$ \hat{Y_i}=\alpha+\hat{\beta}^T\textbf{X}_i+\hat{\epsilon_i}$$
-$$\textbf{X}_i=\begin{bmatrix}
+The model used for prediction: 
+$$ \hat{Y_i}=\beta_0+\sum_{i=1}^n\hat{\beta_i}\textbf{T}_i+\hat{\epsilon_i},\quad T_i=\prod_{j=i}^mX_j^{d_i,j}
+\quad\footnote{Peckov, Aleksandar. \textit{A Machine Learning Approach To Polynomial Regression} p. 9}$$
+\small{$m$ being total number of features, $d_i,j$ denoting degree of polynomial features. 
+$$\textbf{X}_j=\begin{bmatrix}
            basementSize \\
@@
            size \\
-           primarySchool\_educ \\
+           primary\_school\_educ \\
            high\_school\_educ \\

### 2019-08-29 Opsætningexam/DraftExam.tex
r

@@
 The valuations included in the research are collected from one of Denmarks largest online real-estate websites named Boliga.dk.
-The Boliga data contains approximately 66,000 active offerings with valuations ranging from 15,000 to 85 mil.dkk.
+The Boliga data contains approximately 66,000 active offerings with valuations ranging from 15,000 to 85 million.
+DKK.
 This research paper intends to analyze real estate price valuations and which effects geo- and sociodemographic criteria affect valuations, using machine learning models.
@@
 This algorithmic confounding forces the scientist to be careful regarding any observed human behaviour that is extracted from a single digital system.\newline
-In the analysis of big data it is often useful to employ machine learning as it can identify and predict various nonlinear relationships in big data sets, that otherwise would remain hidden.
+In the analysis of big data it is often useful to employ machine learning as it can identify and predict various non-linear relationships in big data sets, that otherwise would remain hidden.
 Data scientists' have for the most part optimised the predictive capabilities of the algorithm applied, and as a consequence they have often ignored or trivialised machine learning's potential in causal modelling\footnote{Varian.
@@
 \subsubsection{Ridge}
-The ridge model penalizes with the sum of squared coefficients.
-Opposed to Lasso, Ridge do not force features to be omitted.
-Instead Ridge penalizes the parameter estimates and decreases them towards zero.
-Ridge minimizes:
+The ridge model penalizes with the sum of squared coefficients. Opposed to Lasso, Ridge do not force features to be omitted. Instead Ridge penalizes the magnitude of the coefficients. Ridge minimizes:
 $$L_{Ridge}(\hat{\beta}) = \left(\sum_{i=1}^{n} (y_i-\hat{y_i}(\beta))^2+\lambda\sum_{j=1}^{p}\hat{\beta_j}^2\right) \qquad s.t \quad \lambda \geq 0 $$
@@
 \end{table}
-The Ridge model with three degrees of polynomial features are selected as the best performing model. Both according to MAE
+The Ridge model with three degrees of polynomial features are selected as the best performing model. In regard to MAE as well as MSE.\newline
+We examine the validation curve, figure \textcolor{red}{XX}, of the model to examine whether we have found a good bias-variance-balance with our optimized hyperparameter.
+We plot the average train and cross-validation performance for different values of $\lambda$:
 
@@
 \caption{}
-\includegraphics[scale=1]{ValCurveRidge3deg.png}
+\includegraphics[scale=0.6]{ValCurveRidge3deg.png}
 %\source{}
 \end{figure}
+The dotted line approximately represents the optimized value of lambda from our previously conducted k-fold cross-validation.
+
+Firstly, we are somewhat satisfied with the average performance of the model.
+With an MSE of approximately $55·10^10$ and a MAE of DKK 43,630.55, we find that the model performs quite well on unseen data.
+The curve suggest that we have found the optimal degree of regularization with our hyperparameter.
+Had we chosen a smaller value of $\lambda$, the model would have had too high variance and thus been overfit.
+This is deduced by how poorly the validation predictions performs at smaller lambdas, as opposed to the training performance.
+On the contrary, had we chosen a greater value of $\lambda$, the model would have been too biased.
+This is illustrated by how poorly the training data, as well as the validation data, performs at higher values of $\lambda$ .
+In that case, we would have underfit our model.
+Nonetheless, it is apparent that our model performs better on the training data, which indicates that it retains a degree of overfitting.
+For the abovementioned reasons, it would not be meaningful to minimize this performance gab by adjusting the hyperparameter.
+Other options for decreasing the variance of the model, could be to include more training data, but as illustrated by the learning curve, this would not seem to make for more less variance.
+Lastly, as overfitting is often caused by a sizeable number of features, omission would be a reasonable mean.
+As we have already conducted feature selection on the basis of correlations, we did not find a feasible way to conduct further selection.
+This could be a subject for further studies, to investigate whether this could improve the performance and evaluation of the model.
+\newline
+In conclusion, it would seem that we have found the hyperparameter which yields the optimal bias-variance-trade-off.
+We can thus conclude that we have optimized our model under the given circumstances.
+
+The learning-curve is depicted in figure \textcolor{red}{XX}
 
@@
 are subject to significant bias, since the cooperative housing that enters the marked through a realtor often would be those with critical amount of undesirable characteristics.
-Like debt - which deflate the valuation accordingly.
 
@@
 The model used for prediction: 
-$$ \hat{Y_i}=\beta_0+\sum_{i=1}^n\hat{\beta_i}\textbf{T}_i+\hat{\epsilon_i},\quad T_i=\prod_{j=i}^mX_j^{d_i,j}
-\quad\footnote{Peckov, Aleksandar. \textit{A Machine Learning Approach To Polynomial Regression} p. 9}$$
-\small{$m$ being total number of features, $d_i,j$ denoting degree of polynomial features. 
+$$ \hat{Y_i}=\hat{\beta_0}+\sum_{i=1}^p\hat{\beta_i}\textbf{T}_i+\hat{\epsilon_i},\quad T_i=\prod_{j=i}^pX_j^{d_i,j}
+\quad\footnote{Peckov, Aleksandar. \textit{A Machine Learning Approach To Polynomial Regression} p. 6-9}$$
+\small{$p$ being total number of features, $d_i,j$ denoting degree of polynomial features. 
 $$\textbf{X}_j=\begin{bmatrix}

### 2019-08-29 Opsætningexam/DraftExam.tex
g

@@
 Furthermore, we consulted with Boliga's Terms and Conditions to avoid any legal ramifications and the appropriate contractual terms of interest can be seen in \href{https://www.boliga.dk/vilkaar-og-betingelser}{§10 Terms and Conditions}.
-In order to comply with these terms we refrained from burdening their website's performance by implementing a time.sleep function, which causes each scraping iteration to pause for 0.5 seconds before commencing on scraping the next page (see appendix XX).
+In order to comply with these terms we refrained from burdening their website's performance by implementing a time.sleep function, which causes each scraping iteration to pause for 0.5 seconds before commencing on scraping the next page \textcolor{red}{(see appendix XX)}.
 Furthermore, Boliga prohibits the use of automated scrapers and bots, which we did not do, as our scraping was done in a specified time-frame and we did not automate the procedure to be done on multiple occasions.
@@
 A number of features are excluded before training the model.
-The exclusion was determined, quite simply, by investigation of the correlation between the complete set of features and the valuation price.
+The exclusion was determined, quite simply, by investigation of the correlation between the complete set of features and the target variable.
 A list of the excluded features are found in appendix 11.0.1.
@@
 Firstly, we are somewhat satisfied with the average performance of the model.
-With an MSE of approximately $55·10^10$ and a MAE of DKK 43,630.55, we find that the model performs quite well on unseen data.
+With an MSE of approximately $55\cdot10^{10}$ and a MAE of DKK 43,630.55, we find that the model performs quite well on unseen data.
 The curve suggest that we have found the optimal degree of regularization with our hyperparameter.
@@
 The learning-curve is depicted in figure \textcolor{red}{XX}
+\begin{figure}[H]
+\centering
+\caption{}
+\includegraphics[scale=0.6]{Learncurvridge.png}
+%\source{}
+\end{figure}
 
@@
 Both AIC and BIC, would likely have suggested Lasso, with 2-degrees of polynomial features, as preferred model.
-As both measurement are increasing in numbers of estimated parameters.
+As both measurement are increasing in numbers of estimated parameters\footnote{Peckov, Aleksandar.
+(2012)  \textit{A Machine Learning Approach To Polynomial Regression}}.
 

### 2019-08-29 Opsætningexam/Analysis/Analysis.tex
analyse

--- 2019-08-29 Opsætningexam/DraftExam.tex
@@
 \begin{document}
-\includepdf[pages=-]{forside.pdf}
-\newpage
-\onehalfspacing
-
-\tableofcontents
-\newpage
-\section{Introduction}
-This report depicts a research performed regarding active Danish real-estate property valuations from 2016-2019.
-Since 2011, the yearly number of real estate properties sold has slightly increased, with 2017 being the year with most sold properties in 10 years \href{https://www.dst.dk/da/Statistik/nyt/NytHtml?cid=27979}{(Danmarks Statistik, 2018)}.
-The price of real estate properties is also rising through 2019 \href{https://www.dst.dk/da/Statistik/nyt/NytHtml?cid=28741}{(Danmarks Statistik, 2019)}.
-Although this generally depicts a willingness of buyers to pay more for real-estate property, and higher valuations from agents, a closer analysis of current and active valuations add a local view of which conditions contribute to the valuation of a real-estate property.
-\newline
-\newcommand{\source}[1]{\caption*{Source: {#1}} }\begin{figure}[H]
-\centering
-\caption{}
-\includegraphics[scale=0.4]{123.png}
-\source{Own creation, with data from \href{https://www.boliga.dk}{Boliga.dk}}
-\end{figure}
-
-Figure 1 shows the average square meter price valuation of active offers per municipality in Denmark.
-The maximum square meter price being approximately 8 times higher in the municipality of Gentofte, than Lolland, the municipality with lowest average square meter price valuations.
-A tendency visualized in the figure, is that average square meter price valuations are higher in in highly populated municipalities and in suburban areas surrounding Copenhagen.
-\newline
-
-The valuations included in the research are collected from one of Denmarks largest online real-estate websites named Boliga.dk.
-The Boliga data contains approximately 66,000 active offerings with valuations ranging from 15,000 to 85 mil.dkk.
-This research paper intends to analyze real estate price valuations and which effects geo- and sociodemographic criteria affect valuations, using machine learning models.
-Our research questions is as follows:
-\begin{center}
- \textit{Which features are most relevant for predicting evaluations of real estate properties in Denmark?}
-\end{center}
-This research paper contains a section describing the construction of research data and assesses the choices made in gathering meaningful features for the machine learning model.
-Also, a section regarding the choice and optimization of machine learning models is included, where the intention is to provide insights on our progress on finding the optimal model.
-As a result, a preferable machine learning model is chosen with a discussion of its usability.
-
-\section{Literature Review}
-Within data social science there exist widely differing definitions of big data and machine learning. This section seeks to clarify the use of these terms within the scope of this paper.
-\paragraph{On big data \& machine learning\newline}
-Historically, big data has been a term reserved for data that was unable to be processed by extant software.
-However, recent increases in computational power has enabled data processing of hitherto unheard of quantities of data\footnote{Lazer, David and Jason Radford (2017) \textit{Data ex Machina.
-Introduction to Big Data}.
-Annual Review of Sociology}.
-Today, big data is no longer too cumbersome to analyse.
-Matthew Salganik\footnote{Salganik, Matthew J.
-(2018) \textit{Bit by Bit Bit - Social research in the digital age.}} instead mentions ten typical characteristics of big data.
-Salganik's tentative definition suggests that big data is not as single entity, but includes many different types of systems.
-Among the most important features of Salganik's definition of big data is that the data has a high frequency of observations and is continuously being generated.
-Since the data is always-on it is also drifting, meaning that the structure and population it represents is ever-changing.
-It is therefore important to understand that big data is not a naturally occurring system, but driven by the engineered purpose of the system.
-This algorithmic confounding forces the scientist to be careful regarding any observed human behaviour that is extracted from a single digital system.\newline
-In the analysis of big data it is often useful to employ machine learning as it can identify and predict various nonlinear relationships in big data sets, that otherwise would remain hidden.
-Data scientists' have for the most part optimised the predictive capabilities of the algorithm applied, and as a consequence they have often ignored or trivialised machine learning's potential in causal modelling\footnote{Varian.
-Hal R.
-\textit{Big data: New tricks for econometrics}}.\newline
-The technical and theoretical challenges faced by big data and machine learning research are important to consider, when employing the tools they provide.
-One of the major discussions revolve around machine learning's predictive capabilities.
-Chris Anderson\footnote{Anderson, Chris (2008) \textit{The end of theory: The data deluge makes the scientific method obsolete}} (2008) argues that since the computing power and the scale of data has increased exponentially, our reliance of scientific models could become obsolete.
-Instead of focusing on the theoretical implications of observations, scientists should, according to Anderson, focus on the statistical outputs: In the age of big data, correlation perhaps should supersede causality and consequently social data scientists should not try to develop coherent models or unified theories to explain a social phenomenon.\newline
-However, many social data scientists argue against this point of view.
-Justin Grimmer\footnote{Grimmer, Justin (2015) \textit{We are all social scientists now: how big data, machine learning, and causal inference work together}} claims, that correlations extracted from big data cannot stand alone.
-Large quantities of data is not sufficient to make scientifically valid causal inferences.
-It requires a rigorous research design and clear theoretical assumptions, in order to yield scientifically accurate estimates.
-Indeed social sciences greatest contribution to big data research, comes from the organized framework provided by rigorously tested theory\footnote{Einav, Liran and Jonathan Levin (2014) \textit{Economics in the age of big data}}.\newline
-The contribution from the social sciences to machine learning help create new methods that will be able to utilize the strengths of machine learning to help solve causal inference problems within the framework of a well defined theory\footnote{Athey, Susan (2018) 'The Impact of Machine Learning on Economics' in Ajay Agrawal et al.
-(eds) \textit{The Economics of Artificial Intelligence: An Agenda}}.
-These new approaches could help define what variables to manipulate and how to properly use machine learning within the framework of theoretical assumptions.
-Ultimately, big data and machine learning could increase the scope of the social scientist's field, not only by delivering new data and methods, but by helping the social scientist to focus on new questions\footnote{Mullainathan, Sendhil, and Jann Spiess (2017) \textit{Machine Learning: An Applied Econometric Approach}}.
-
-\section{Data Description \& Ethics}
-
-\subsection{Ethical Considerations in the Current Research Project}
-In the current paper the appropriate care and consideration has been given to the ethical concerns regarding the scraping, processing, and the presentation of the data.
-Drawing upon the European Comissions\footnote{European Commission (2018).
-\textit{Ethics in Social Sciences and the Humanities}} ethical guidelines and principles for ethical conduct in social data science, the potential harm to users of Boliga's web-page were carefully considered.
-As a step to prevent the mosaic effect and in an effort to anonymize the scraped data only aggregated data will be presented in this paper, so that no single observation can be identified from the analysed data.\newline
-No informed consent has been obtained from the users of the site, prompting us to consider the consequences of the lack thereof, as informed consent is paramount to the proper, ethical conduct in social science.
-However, sometimes, as in this instance, informed consent can be logistically impossible to collect from all participants in the study.
-Salganik mentions that informed consent for everything is an ideal, but in practice impossible to obtain and researchers should instead strive to follow an alternative rule, that he describes as: "some form of consent for most things." \footnote{Salganik, Matthew J.
-(2018) \textit{Bit by Bit Bit - Social research in the digital age.} p.303} Adhering to this, more complex  understanding of the practicality of informed consent, we chose to contact Boliga to inform them of our intent to scrape their website and use the data in an educational context.
-Boliga responded positively to our inquiry, which we took as informed consent from a third party on behalf of the participating users in our study.\newline
-In considering the legal ramifications of our research and to make sure we adhere to the seven principles of GDPR, and other appropriate legislation and legal contracts, we consulted the general guidelines introduced by the Consumer Data Research Center.
-In particular we noted that we are justified to collect and use the data on the lawful basis of legitimate interests.
-Furthermore, we consulted with Boliga's Terms and Conditions to avoid any legal ramifications and the appropriate contractual terms of interest can be seen in \href{https://www.boliga.dk/vilkaar-og-betingelser}{§10 Terms and Conditions}.
-In order to comply with these terms we refrained from burdening their website's performance by implementing a time.sleep function, which causes each scraping iteration to pause for 0.5 seconds before commencing on scraping the next page (see appendix XX).
-Furthermore, Boliga prohibits the use of automated scrapers and bots, which we did not do, as our scraping was done in a specified time-frame and we did not automate the procedure to be done on multiple occasions.
-\subsection{Data Scraping Process}
-In the following paragraphs our scraping efforts will be described. The scrapers can be examined in the attached Jupyter Notebooks labelled \textcolor{red}{XX and XX.} 
-\paragraph{\href{https://www.boliga.dk}{Boliga}\newline}
-Our data comes from \href{https://www.boliga.dk}{Boliga.dk}, the largest independent online web-portal for real-estate sales in Denmark and has access to unique features such as "liggetid", price-development and access to BBR - the Danish Building and Housing Register \footnote{\href{https://www.boligagruppen.dk}{www.boligagruppen.dk}}.
-Giving us unique insights into the pricing of real-estate in all 98 municipalities of Denmark.
-At the time of scraping 65,950 properties were for sale.\newline
-The scraping process was conducted on Friday the 23rd of August 2019.
-We had advised Boliga of our intent to collect data from their website via our scraper in an effort to identify ourselves and our intent\footnote{Shiab, Nael (2015) \textit{On the Ethics of Web Scraping and Data Journalism}.
-Global Investigative Journalism Network.}.
-In order to scrape the data of interest we familiarized ourselves with the HTML-structure of Boliga.
-On the basis of these insights we constructed a code, which were able to scrape every page, containing information pertaining the currently listed real-estates on Boliga.
-The scraper requested all information available from each individual page, which surmounted to 1,319 URL requests.
-\newline
-For each URL, 34 features and the target variable (price) was collected.
-Table \textcolor{red}{XX} provides an overview of the features with a short description, and whether the feature has been dropped or saved for later usage.
-There are three reasons for a feature to be dropped:\newline
-1. The feature does not act with independent characteristics according to the research,\newline
-2. The feature contains insufficient data,\newline
-3. The feature is poorly formatted and cannot efficiently be recreated. 
-\vspace*{10px} \newline
-\textit{Features Obtained:} \newline
-\begin{tabular}{c c}
-Continuous: & basementSize, buildYear, ownersExspenses, lotSize	, price, rooms, size  \\	
-\end{tabular}\newline 
-\begin{tabular}{c c}
-Categorical: & ForClosure, Type, Municipality, lotSize	, price, rooms, size  \\	
-\end{tabular}
-\paragraph{\href{https://www.hvorlangterder.dk}{Hvorlangterder.dk}\newline}
-\href{https://www.hvorlangterder.dk}{hvorlangterder.dk} returns distances from a given address, to conveniences such as supermarkets, hospitals and schools.   
-The scraping of \href{https://www.hvorlangterder.dk}{hvorlangterder.dk} was achieved by writing a function that took in the GPS-coordinates gathered from Boliga.
-It constructed a URL (65,950 URL request), \textcolor{red}{which was scraped and the json response was returned as a dictionary of distances to the points of interest.
-The values from each key in the dictionary was then extracted as a new column in a Pandas DataFrame}.\newline
-As Jupyter performs poorly at running long asynchronous tasks and estimated a running time of 18 hours this procedure was run in Visual Studio.
- \vspace*{10px} \newline
-\textit{Features obtained:}\newline
-\begin{tabular}{c c}
-Distances to: & lake, forest, doctor, supermarket,	school, daycare, hospital, train \\	
-\end{tabular}\newline 
-\begin{tabular}{c c}
-\qquad \qquad \qquad \qquad &  pharmacy, library, coast, junction \\	
-\end{tabular}
-\paragraph{Social and economic factors\newline}
-Social and economic factors on municipality level is collected from \href{https://statistik.politi.dk/QvAJAXZfc/opendoc.htm?document=QlikApplication%2F2999_Public\%2FPublic_IndsatsResultater.qvw}{statistik.politi.dk} and
-\href{https://www.dst.dk/da/Statistik/emner/befolkning-og-valg}{Danmarks Statistik} respectively.
-These factors include income, reported crime, level of highest completed education etc.
-These are transformed into ratios, by taking the total population in a given municipality into account.
- \vspace*{5px} \newline
-\begin{tabular}{c c}
-\textit{Features obtained:}: & unemployment\_relative, primary\_school\_educ, high\_school\_educ \\	
-\end{tabular}\newline 
-\begin{tabular}{c c}
-\small (relative to population) & vocational\_educ,	 SHE, 	MHE, bachelors\_degree  \\	
-\end{tabular}\newline 
-\begin{tabular}{c c}
-\qquad \qquad \qquad \qquad \quad & LHE, avg\_municipal\_income\_2017, Total\_reported\_crime\\	
-\end{tabular}\newline 
-\begin{tabular}{c c}
-\qquad \qquad \qquad \qquad \quad & Population\_in\_urban\_development  , Socioeconomic\_index \\	
-\end{tabular}\newline 
-\begin{tabular}{c c}
-\qquad \qquad \qquad \qquad \quad & average\_class\_size,	expenses\_sport\_and\_other\_cultural\_activities	  \\	
-\end{tabular}\newline 
-\begin{tabular}{c c}
-\qquad \qquad \qquad \qquad \quad & expenses\_per\_school\_student	   \\	
-\end{tabular}\newline 
-\small {All educational features are a measure of highest completed education. Furthermore SHE, MHE, LHE are abbreviations of short-, medium- and long-cycle higher education}. 
-\normalsize
-\subsection{Log Analysis}
-
-\subsection{Merging Data}
-Pandas objects can be combined in different ways according to the nature of features in the dataset.
-Relational database style operations are based on linking keys together, thereby maintaining the relationship between the combined datasets\footnote{McKinney, W.
-(2018).
-\textit{Data Wrangling: Join, Combine and Reshape}.
-p.
-231 }
-
-The data collection and scraping process provided a total of 15 Datasets from Boliga, Hvorlangterder, DAWA, the Danish Police, Social- \& Indenrigsministeriet and Danmarks Statistik.
-This section will describe how each dataset was merged, using pandas relational database styled merge and join operations.
-
-\paragraph{Boliga.dk\newline}
-An evaluation of the Boliga datasets features and their ability to support further data collection led to the utilization of the following features:
-
--	[Longitude, Latitude]: Geographical placements of the properties
-
--	Municipality: a numeric code for municipalities in Denmark
-
-The Boliga dataset acts as a master dataset and was joined or merged upon throughout the process, and acts as the “left” of all operations.
-The Longitude and Latitude features serve as specific coordinates for valued properties but are in few cases repetitive regarding different apartments from the same complex.
-The municipality code was used for translation purposes between the master dataset and other datasets.
-
-\paragraph{DAWA\newline}
-The DAWA dataset was scraped with an input of a distinct municipality code from the master dataset, returning a dataframe of municipality names for each code.
-This dataframe was merged onto the Boliga dataframe as a many-to-one merge with municipality code as the merge keys.
-The scraped municipality names from DAWA was used as the merge key for all further merges of municipal data.
-
-\paragraph{Danmarks Statistik, Danish Police \& Social og Indenrigsministeriet\newline}
-Of the municipality-based data collected, the merging of these to our master dataframe was subsequently performed identically.
-Every dataset contained a column for unique municipality names and values for the given feature of the dataset.
-A many-to-one left merge was performed with the master dataframe, using municipality names.
-The result being a master dataframe containing municipal specific features for properties.
-
-The Danish Police datasets contained totals for different categories of crimes reported within municipalities.
-These datasets were outer joined with an index set to contain municipality names.
-Afterwards, the values were added to each other, providing a total of reported crimes within each municipality.
-The police statistics webpage does not specify whether different types of reported crimes can relate to a single case, but we assessed that the number of crimes reported provides a meaningful feature either way.
-The dataset containing total reported crimes per municipality, was merged with the master dataset in the same fashion as previous municipality-based features.
-
-\paragraph{Hvorlangterder.dk\newline}
-The hvorlangterder scrape provided location specific features, taking an input of Latitude and Longitude coordinates.
-The scraping function, which was created for returning location-based features, created a column for the row specific values.
-Therefore, a merge operation was not necessary, but could alternatively have been managed with a one-to-one inner-merge id.
-As few coordinates regarding apartment properties are repetitive, these are not suitable for merging upon.
-
-\subsection{Data Cleaning}
-The scraping of Boliga left us with 65,950 observations.
-However, big data is often dirty and requires tidying before it can be used in any meaningful statistical context (Salganik 2018).
-In the following sections we describe our data cleaning efforts.
-\subsubsection{Initial clean-up}
-The initial clean-up sorted out rows that contained an illogical value.
-Here we focused our efforts on the removing any and all observations that contained a municipality code of 0.
-Additionally, we chose to exclude any real estate valued below 100 DKK, while these listings existed on Boliga's website, they were all listings, where the seller wanted  to sell to the highest bidder.
-We excluded these listings on the basis that they were unrealistically priced compared to the property's real market value.\newline
-Boliga subdivides its listings into ten real-estate types.
-We chose to exclude the typification "other", as there were only 17 houses listed in the category - too few for training our machine learning model.
-Furthermore, we also removed any listing without coordinates as these were vital for the scraping process on hvorlangerder.dk.\newline
-We dropped all observations with an unreasonably high "liggetid", as we saw these instances to not  represent reasonable pricing or demand.
-We have thus set an arbitrary limit of 3 years (1,095 days), and omitted any observations that has been on the market for longer than that.
-This results in the omission of approximately 5\% of our dataset.
-The highest mean "liggetid" on a municipal level was roughly 600 days, so as not to discriminate against the observations from the municipalities with a longer average 'sales time' we set the cut-off somewhat higher than the highest mean.
-Another option was to set the limit according to each municipality's mean, a solution that was a bit more time consuming, and would have yielded approximately the same result, hence we opted not to do it.
-In figure XX the number of rows dropped at each step of the cleaning can be perused.
-\begin{center}
-\begin{tabular}{|l|c|}
-\hline 
-Feature & \emph{n} \\
-\hline 
-Municipality code & 231 \\ 
-\hline 
-Price & 11 \\ 
-\hline 
-Coordinates & 275 \\ 
-\hline 
-Type & 17 \\ 
-\hline 
-Liggetid & 3,940\\
-\hline 
-Total\footnote{"The total is the count of how many rows were dropped. Some rows were missing multiple features.} & 4,332\\
-\hline
-\end{tabular} 
-\end{center}
-
-\subsubsection{Ejerlejlighed's lot size}
-Inspecting our data we found that from 8,028 apartments 1,176 of these had a lot size.
-These listings included the apartment complex' common area, whereas the rest did not.
-To overcome this discrepancy we chose to set all non-zero values to zero, as not to confuse our model with an inconsistent feature (Raschka \& Mirjalili 2017).
-
-\subsubsection{Final touch-ups}
-After merging the housing info with the demographic data and the distances from hvorlangterder.dk, we removed a single duplicate and deleted all columns not relevant for our analysis.
-After the clean-up of the data we were left with a dataset consisting of 61,618  observations and 37 features and 1 target variable.
-
-\subsection{Descriptive Statistics}
-In this section, we will examine the more apparent patterns of our collected data. This is done to familiarize ourselves with the data, before we commence on the analysis.
-\subsubsection{Key Statistics}
-Some key statistical characteristic is presented in table 1:
-\begin{table}[H]
-\begin{center}
-\caption{Key Statistics\label{time}}
-\begin{tabular}{| c | c | c | c | c | c |} 
-\hline
-   & Price & \, Rooms \ & \ $m^2$ \ & Average Municipal Income \\ \hline
-   Mean & 2,312,798.00 & \ 4.21 \  & \ 127.82 \ & 312,957.03 \\ \hline
-   Std & 2,351,127.00 & 2.12 & 75.67 & 46,095.34 \\ \hline
-   Min & 15,000.00 & 0 & 0 & 257,776 \\ \hline
-   25\% & 985,000.00 & 3 & 82 & 290,973 \\ \hline
-   50\% & 1,695,000.00 & 4 & 123 & 302,153 \\ \hline
-   75\% & 2,895,000.00 & 5 & 167 & 318,745 \\ \hline
-   Max & 85,000,000.00 & 50 & 2,390 & 583,331 \\ \hline
-\end{tabular}
-\end{center}
-\end{table} 
-Initially, it should be addressed that some of the properties has 0 rooms and consists of 0 $m^2$.
-This is due to the fact that we have also included land on which housing has not yet been build.
-Examining the 25\%-quintile and the 75\%-quintile of the valuation prices, it becomes apparent that there are some substantial outliers both to the cheaper and to expensive side.
-This is also the case with rooms and $m^2$, where the highest values are sizably higher than the 75\%-quintile.
-It is worth noting, that there is quite a big difference between the lowest average municipal income of DKK 257,776.
-and the highest of DKK 583,331.
-This difference becomes further noteworthy when assessing the 75\%-quintile.
-The difference from the 75\%-quintile to the highest average municipal income is more than 4 times the difference of the 75\%-quintile and the lowest income.
-The income distribution is visualised in the following figure:
-\begin{figure}[H]
-  \centering
-   \caption{}
-   \includegraphics[width=\linewidth]{Box1.png} 
-  \label{fig:}
-\end{figure}
-The boxplot illustrates that the distribution is heavily left-skewed, where some municipalities has a sizably higher average income than the rest of the Danish municipalities.
-
-\subsubsection{Prices in Municipalities}
-We plot the average square meter valuation price in the different municipalities:
-\begin{figure}[H]
-  \centering
-   \caption{}
-   \includegraphics[width=\linewidth]{Box2.png} 
-  \label{fig:}
-\end{figure}
-It becomes apparent that the distribution is quite left-skewed and that there are a few municipalities who’s price per square meter is much higher than the rest of the municipalities.
-Recalling the geoplot in figure 1, these expensive outliers are heavily concentrated around- and north of Copenhagen.
-The distribution looks similar to that of figure 2 (The previous boxplot), though we cannot declare any correlation between average municipal income and average municipal price per square meter.
-Nonetheless, it becomes apparent that the valuation price of property is highly discriminated by municipal factors.
-The scope of this assignment is exactly to examine these factors and attempt to use these to evaluate an unseen, out-of-sample property.
-
-\subsubsection{Property Type}
-Another worthwhile consideration is that we have included all types of properties.
-It would be reasonable to assume that there is an average difference in valuation pricing depending on the type of property.
-Figure 4 displays the median valuation price for each type:
-\begin{figure}[H]
-  \centering
-   \caption{}
-   \includegraphics[width=\linewidth]{bar1.png} 
-  \label{fig:}
-\end{figure}
-It is interesting to note that the most expensive properties are apartments as opposed to houses.
-This is not especially surprising though, as it is a well-established trend that real estate prices in major cities are skyrocketing.
-Refraining from delving deeper into to a discussion of global urbanization, we retain the fact that property type does have an apparently significant effect on valuation pricings on average.
-We will include the ‘type’ feature in our impending model training to control for this effect.
-
-\subsubsection{The Dataset}
-The merged dataset contains 61.618 observations and 37 features.   The features are of both categorical and continuous measures. Skal dette ikke bare op i Merging data?\newline
-
-\section{Methods}
-\subsection{Supervised Machine Learning}
-The objective by applying Machine Learning is to train a model that are able to make predictions in near future or never seen data.
-By feeding a model with labeled data as well as data samples, ML will define the algorithms that predicts the best\footnote{Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow}.
-p.
-3}.
-This project, implements a ML regression prediction model to predict pricing of housing listed in near future.
-\subsection{Fitting the model}
-The potential problems of underfitting and overfitting should be assessed when fitting a model.
-A model is underfitted if it hardly captures the variation of the sample data.
-It is then said that the model has \textit{high bias}.
-A model is overfitted, when it is overly sensitive to the idiosyncrasy of the sample data and captures the variation in too great detail.
-This problem often comes with the introduction of a sizeable number of features.
-Overfit models are said to have \textit{high variance}\footnote{Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow}.
-p.73}.
-In both cases, the model will generalize poorly.
-A key step in defining a decent model in machine learning is to find an optimal bias-variance-balance, by tuning the complexity of one’s model.
-This is done through \textit{regularization}.
-In this project three different types of regularization are applied; Lasso, Ridge and Elastic net.
-
-\subsubsection{Lasso}
-Regularization by Lasso, will penalize complexity of the model by the sum of the absolute value of the coefficients.
-This penalty will make the model less complex and more appropriate for prediction.
-\footnote{Foster, Ian; Rayid Ghani Ron S.
-Jarmin, Frauke Kreuter, Julia Lane; \textit{Big Data in Social Sciences, A Practical Guide to Methods and Tools} p.
-173}\, \footnote{Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow} p.
-332}
-\newline Lasso minimizes: $$L_{Lasso}(\hat{\beta}) = \left(\sum_{i=1}^{n} (y_i-\hat{y_i}(\beta))^2+\lambda\sum_{j=1}^{p}|\hat{\beta_j}|\right) \qquad s.t \quad \lambda \geq 0 $$
-Another convenient attribute of the Lasso penalty is that some estimates are set equal to zero and thereby produce sparse models\footnote{Hal R.
-Varian.
-\textit{Big data: New tricks for econometrics}.
-Journal of Economic Perspectives.
-p.19}.
-Lasso thereby performs the feature selection automatic.
-\subsubsection{Ridge}
-The ridge model penalizes with the sum of squared coefficients.
-Opposed to Lasso, Ridge do not force features to be omitted.
-Instead Ridge penalizes the parameter estimates and decreases them towards zero.
-Ridge minimizes:
-$$L_{Ridge}(\hat{\beta}) = \left(\sum_{i=1}^{n} (y_i-\hat{y_i}(\beta))^2+\lambda\sum_{j=1}^{p}\hat{\beta_j}^2\right) \qquad s.t \quad \lambda \geq 0 $$
-
-\subsubsection{Elastic-net}
-The Elastic net combines the penalizing terms of Lasso and Ridge, with $\alpha$ defining the relative weights between Lasso and Ridge. Elastic net minimizes the function: 
-$$L_{elasticnet}(\hat{\beta}) = \frac{\sum_{i=1}^{n}\left(y_i-\hat{y_i}(\beta)\right)^2}{2n} + \lambda\left(\frac{1-\alpha}{2}\sum_{j=1}^{p}\hat{\beta_j}^2+\alpha\sum_{j=1}^{p}|\hat{\beta_j}|\right)$$
-$$0 \leq \alpha \leq 1 \quad \wedge \quad \lambda \geq 0$$
-
-\subsection{Selecting Features}
-In case regularization is not sufficient to cope with the overfitting of the model.
-Exclusion of features are a viable approach.
-With the number of scraped features in this project, taking into consideration.
-A recurring overfitting of the model would be likely.
-As a consequence a deliberate exclusion of features of interest will need to be carried out.
-
-\subsection{Optimizing the Hyperparameter}
-To minimize the mean squared errors of our Lasso and Ridge regression we performed k-fold cross validation to optimize the hyperparameter $\lambda$. 
-We split the data into a test set and a development set, consisting of respectively 20\% and 80\% of the total observations.
-Subsequently, we use k-fold cross-validation to randomly split the development set into k folds, where k-1 folds are used to train the model.
-The remaining fold is used to validate the model’s generalizability by calculating the mean squared errors of the trained model’s prediction of the left-out fold\footnote{Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow}.
-p.191}.
-This process is repeated k times and each time a new fold is left out for validation.
-Since we are working with a relatively large dataset we chose to split our data into 5 folds, and computed the average MSE for the 5 iterations.
-By using the k-fold cross-validation method we relieve ourselves of the concern that the estimation of our model’s performance is simply due to a lucky or unlucky split of the data.
-\newline
-We performed this procedure for 12 different values of $\lambda$ spanning between \textcolor{red}{$10^(-4) and 10^4$}.
-We chose the value of $\lambda$ which yields the smallest average MSE over the 5 folds.
-We both calculated the optimal hyperparameters for a Ridge regression model, a Lasso regression model and an Elastic Net regression model.
-\textcolor{red}{The following table} shows the performance of the different models, when trained with their optimal hyperparameter and predicting the test data.
-
-\subsection{Predictive Performance}
-With the hyperparameters optimized, final model performance can be evaluated.
-Once more a cross-validation is carried out, which return the average performance-error of each model.
-By retraining the models on the complete training set and testing on the independent test set, performance measures are obtained\footnote{Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow}.
-p.192}.
-\newline The performances of the models are simply measured by MSE, RMSE and MAE.
-\newline
-$$ MSE = \frac{1}{n}\sum_{i=1}^{n}(y_i-\hat{y_i})^2$$
-
-$$ RMSE = \sqrt{\frac{1}{n}\sum_{i=1}^{n}(y_i-\hat{y_i})^2}$$
-$$ MAE = \frac{1}{n}\sum_{i=1}^{n}|y_i-\hat{y_i}|$$
 
@@
 A number of features are excluded before training the model.
-The exclusion was determined, quite simply, by investigation of the correlation between the complete set of features and the valuation price.
+The exclusion was determined by investigating the pairwise correlation between the complete set of features and the valuation price.
 A list of the excluded features are found in appendix 11.0.1.
@@
 
-The initial 5-fold cross-validation to obtain the optimal values of the hyperparameters in each regularization yields. 
+The initial 5-fold cross-validation to obtain the optimal values of the hyperparameters in each regularization yields, can be seen in table 1.
 \begin{table}[h!]
@@
 \begin{center}
-\caption{Prediction Errors. \label{time}}
+\caption{Prediction Errors, two degrees of polynomial features \label{time}}
 \begin{tabular}{| c | c | c | c | c | c |} 
 \hline
-   & \ MSE \ & \, RMSE \ & \ MAE \ \\ \hline
-   Lasso 2-deg & 59,081,597,331.11 & \ 243,067.06 \  & \ 47,660.52 \ \\ 
-  Ridge 2-deg & 62,416,553,466.45 & 249,833.05 & 51,306.19  \\ 
-  Elastic net 2-deg & 1 & 1 & 1  \\ 
-  OLS 2-deg & 64,297,245,726.80 & 253,569.02 & 52,035.52  \\ \hline 
-  Lasso 3-deg & 60,103,955,188.37 & 245,161.08 & 47,126.43  \\ 
-  Ridge 3-deg & 55,667,264,851.14 & 235,939.11 & 43,630.55  \\ 
-  Elastic Net 3-deg & 1 & 1 & 1  \\
-  OLS 3-deg & 2.848e+28 & 168,763,945,674,352.3 & 2,637,476,978,906.39  \\ \hline
+   & Lasso & \, Ridge \ & \ Elastic Net \ & OLS \\ \hline
+   MSE & 59,081,597,331.11 & \ 62,416,553,466.45 \  & \ 1 \ & 64,297,245,726.80 \\ \hline
+  RMSE & 243,067.06 & 249,833.05 & 1 & 253,569.02 \\ \hline
+   MAE & 47,660.52 & 51,306.19 & 1 & 52,035.52 \\ \hline
 \end{tabular}
@@
 \end{table}
-The Ridge model with three degrees of polynomial features are selected as the best performing model. Both according to MAE
+\begin{table}[H]
+\begin{center}
+\caption{Prediction Errors, three degrees of polynomial features\label{time}}
+\begin{tabular}{| c | c | c | c | c | c |} 
+\hline
+   & Lasso & \, Ridge \ & \ Elastic Net \ & OLS \\ \hline
+   MSE & 60,103,955,188.37 & \ 55,667,264,851.14 \  & \ 85,824,334,267.16 \ & 2.848e+28 \\ \hline
+  RMSE & 245,161.08 & 235,939.11 & 292,957.91 & 168,763,945,674,352.3 \\ \hline
+   MAE & 47,126.43 & 43,630.55 & 69,582.56 & 2,637,476,978,906.39 \\ \hline
+\end{tabular}
+\end{center}
+\end{table}
+%DET ER KUN DENNE DEL
+Since our efforts are aimed at predicting the valuation of a given real-estate, we want to penalize the size of the error the MSE-score is a better indicator for our model's performance as opposed to the mean absolute error (MAE).
+Since MSE squares the error terms, it gives a relatively high weight to large errors, which is desirable for our current aim.
 
-\begin{figure}[H]
-\centering
-\caption{}
-\includegraphics[scale=1]{ValCurveRidge3deg.png}
-%\source{}
-\end{figure}
+From table XX it is evident that the machine learning model with two degrees of polynomial features performs best with a regularization by LASSO as it has the lowest measures of difference between the predicted price and the true price, with a MSE of 5.91E+10, whilst the model with 3 degrees of polynomial features regularized by ridge regression performs even better with a MSE 5.57E+10.
+Therefore, we chose this model as the final model from which we will conduct the rest of the analysis with.
+%SLUT
 
@@
 
-\section{Discussion}
-\subsection{Data critique}
-Another interesting prediction which could have been done using the same methods, would have been to predict selling prices.
-This could have been done simply by scraping data on sold housing instead.
-This could be of more value for private agents, whose main interest should be the selling price of their housing.
-%This approach would undoubtedly get a greater data basis.
-needs to add time series trends
-\newline 
-In a prediction-model like this it is near impossible to evade some form of omitted variable bias.
-A significant amount of potential important factors can not be acquired.
-For an example the view from the listed housing will for sure be of great impact of the valuation price.
-Another factor of interest could have been a evaluation of the condition of the housing, unfortunately the statement of property\footnote{red.
-Tilstandsrapport} are not publicly accessible.
-\newline
-The prediction of the cooperative housing valuation %\footnote{http://housingpeople.dk/en/housing-guide/housing-types/cooperative-andelsbolig/},
-are subject to significant bias, since the cooperative housing that enters the marked through a realtor often would be those with critical amount of undesirable characteristics.
-Like debt - which deflate the valuation accordingly.
-
-\subsection{Model Limitations}
-The necessity to exclude municipality dummies as regressors in the prediction models.
-Leaves the model to only separate municipalities by the socio-economic factors, which are subject to low variance.
-This makes distinction between municipality a lot more difficult as well as uncertain.
-Without the municipality dummies, the interpretation of the prediction results are more insecure.
-%Instead of predicting the valuation of a given estate, of a given type, in a given municipality or city.
-It predicts the valuation of a estate at a \textit{more or less} location in Denmark by type, only geographically controlled by distances to various conveniences.
-Geographical boundaries could have been limited way more, resulting in easier interpretation of predictions. Potentially by predicting only for a specific city or municipality. \\
-If one intended to predict valuations country-wide more realistic, a model for each municipality could have been more satisfactory.
-Resulting in 98 separate models.
-The evident downside of this approach being the prospect of limitations in available data (some municipalities has very few listings).
-Another approach could have been to group cities which share characteristics. Ex. The three biggest cities, the provinces, the islands, the country-side towns.
-
-\subsection{Model Selection}
-Instead of only assessing the different models by MAE and RMSE.
-The Information criteria of the respective models could have been introduced.
-Which could have altered the selection of preferred model.
-Both AIC and BIC, would likely have suggested Lasso, with 2-degrees of polynomial features, as preferred model.
-As both measurement are increasing in numbers of estimated parameters.
-
-\section{Conclusion}
-In this assignment, we have used machine learning to train a model to predict valuation prices of real estate in Denmark.
-We did this by scraping Boliga.dk for all of their active houses for sale and combining this with municipal data on income, education, schools and urbanization.
-Additionally, we also scraped data from hvorlangterder.dk which calculates the distance from an address, to different every-day commodities such as hospitals, schools and shopping.
-We have explained how we carried out our gathering of data, how we have structured the data and how we cleaned it.
-
-We performed descriptive statistics on the data to gain a better acquaintance with the data. 
-We conducted feature selection by assessing the correlation between the different features and the target variable, which in our assignment has been the valuation price. 
-We trained both a Lasso- and a Ridge regression model and compared their performances with the performance of a standard linear regression.
-Though k-fold cross-validation, we estimated the optimized hyperparameters for both regularization models.
-We found that the Ridge regression performed best on average, with the performance measure being the smallest mean square error of the model.
-We have assessed to which degree we have managed to find a good bias-variance-balance for our model and concluded that our model suffers from a degree of overfitting.
-This was done by examining the validation curve of our final model.
-
-Finally, we have discussed the results of our analysis. We have critically assessed the boundaries of our research and drawn up potential possibilities for improvement.
-
-\section{An Ethical Overview}
-The ethical principles of social research are anchored in the fundamental human rights, which are broadly formulated in the UN Declaration of Human Rights.
-Additional policies and declarations that codify principles of research ethics and the ethical treatment of research participants include the Nuremberg Code, the Helsinki Declaration, the Belmont Report, and the Menlo Report\footnote{Salganik, Matthew J.
-(2018) \textit{Bit by Bit Bit - Social research in the digital age.}}\, \footnote{European Commission (2018).
-\textit{Ethics in Social Sciences and the Humanities}}.
-These codes and addendums originate mostly in the biomedical field, though they encompass the central principles applied to all human research, which have led some academics to call for a Hippocratic oath for data scientists to safeguard against powerful new technologies under development in laboratories and tech firms\footnote{Rotblat, Joseph (1999) \textit{A Hippocratic Oath for Scientists}}\, \footnote{Sample, Ian (2019, Fri 16 Aug 2019) \textit{and tech specialists need Hippocratic oath, says academic.}}.
-This discussion is nothing new however, as a tentative reformulation of the Hippocratic oath was introduced by Karl Popper\footnote{Popper, Karl (1969) \textit{The Moral Responsibility of the Scientist}}, wherein he stressed the importance of professional responsibility, a critical mind, and an overriding loyalty towards the betterment of mankind.\newline
-Matthew Salganik offer four principles deduced from the Belmont and Menlo Report that should guide the ethical deliberations of the researcher: 1) the respect for persons, that is individuals should be treated as autonomous and if circumstances require it individuals should be entitled to additional protections.
-2) Beneficence stresses the importance of doing no harm and to maximize the possible benefits and minimizing any potential harms.
-3) The principle of justice touches upon the importance of the distribution of burdens and benefits of the social scientist's research.
-This principle stress that is should not be a single stratum of society that bears the costs of the research while another stratum benefits.
-4) The fourth and final principle is the respect for law and public interest, according to Salganik, the principle consists of two distinct elements, that is compliance to relevant laws and legal contracts and transparency-based accountability.
-It is worth noting that Popper’s tentative Hippocratic oath mirrors the first three principles put forth by Salganik, stressing the importance of the ethical conduct of the researcher.\newline
-The need for rigid ethical standards within computational social science was made apparent by the Cambridge Analytica Scandal that broke on the 17th of March 2018.
-Where Steve Bannon could reveal that between 2013 and 2015 Cambridge Analytica had exploited a loophole in Facebook’s API which allowed the company to harvest profile data from 87 million Facebook users, without the user’s permission and use the harvested data to construct a massive targeted marketing database based on the user’s likes and interests\footnote{Vox.com (2018) \textit{The Cambridge Analytica Facebook scandal} [Online]}.
-Other examples of misuse of data acquired from Facebook include the Harvard-run experiment, where students' data was used to create new knowledge about how social networks form and how these networks and their actors' behavior co-evolve, and the emotional contagion experiment from 2012, where approximately 700,000 users were involved in a research experiment to examine the extent to which a person's emotions are affected by the emotions of the people they interact with (Salganik.
-2018).\newline
-From this it should be evident that clear ethical guidelines are required in order to protect the user's privacy from tech-savvy companies.
-To this end, the European Parliament introduced the General Data Protection Regulation (GDPR).
-With its seven overarching principles the GDPR seeks to formalize the procedures involved in the data processing and storing of sensitive and private information (CDRC\footnote{Consumer Data Research Center, UK  [CDRC] (2018) \textit{The General Data Protection Regulation \& Social Science Research} [Online]:}).
-These principles include and expand upon the principles found in the Belmont and Menlo Report.
-The most important consideration, however, must be that even a dataset comprising tens of thousands of observations involve human beings who must be protected from adverse side-effects of the social research.
-There is considerable evidence that point to the fact that even in anonymized data sets it can be possible to backtrack an individual's identity.
-A researcher must therefore be mindful of the mosaic effect if the dataset combines large amount of data from various sources (European Commission 2018).
-
-\newpage
-\section{Litterature}
-\ Foster, Ian; Rayid Ghani Ron S. Jarmin, Frauke Kreuter, Julia Lane; \textit{Big Data in Social Sciences, A Practical Guide to Methods and Tools}, CRS Press 2017 \newline
-
-Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow}, $2^{nd}$editon, Packt Publishing 2017. \newline
-
-Varian. Hal R. \textit{Big data: New tricks for econometrics}. Journal of Economic Perspectives, 28(2):3–28, 2014. \newline
-
-Consumer Data Research Center, UK  [CDRC] (2018) \textit{The General Data Protection Regulation \& Social Science Research} [Online]: \href{https://ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020_ethics-soc-science-humanities_en.pdf}{ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020\_ethics-soc-science-humanities\_en.pdf} [Accessed on 25/08/2019]\newline
-
-European Commission (2018).
-\textit{Ethics in Social Sciences and the Humanities} [Online]: \href{https://ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020_ethics-soc-science-humanities_en.pdf}{https://ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020\_ethics-soc-science-humanities\_en.pdf} [Accessed on 25/08/2019] \newline
-
-Popper, Karl (1969) \textit{The Moral Responsibility of the Scientist}.
-Encounter, March 1969, pp.
-52-56 [Online]: \href{http://www.unz.com/print/Encounter-1969mar-00052}{http://www.unz.com/print/Encounter-1969mar-00052} [Accessed on 25/08/2019]\newline
-
-Rotblat, Joseph (1999) \textit{A Hippocratic Oath for Scientists}.
-Science, November 1999: Vol.
-286, Issue 5444, pp.
-1475 [Online]: \href{https://science.sciencemag.org/content/286/5444/1475.full}{https://science.sciencemag.org/content/286/5444/1475.full} [Accessed on 25/08/2019] DOI: 10.1126/science.286.5444.1475 \newline
-
-Salganik, Matthew J. (2018) \textit{Bit by Bit Bit - Social research in the digital age.} Princeton, NJ: Princeton University Press.\newline
-
-Sample, Ian (2019, Fri 16 Aug 2019) \textit{and tech specialists need Hippocratic oath, says academic.} The Guardian [Online]: \href{https://www.theguardian.com/science/2019/aug/16/mathematicians-need-doctor-style-hippocratic-oath-says-academic-hannah-fry} [Accessed on 25/08/2019]\newline
-
-Vox.com (2018) \textit{The Cambridge Analytica Facebook scandal} [Online]: \href{https://www.vox.com/2018/4/10/17207394/cambridge-analytica-facebook-zuckerberg-trump-privacy-scandal} [Accessed on 26/08/2019] \newline
-
-Boligagruppen.dk (2019) \textit{Om boliga gruppen} [Online]: \href{https://www.boligagruppen.dk}{www.boligagruppen.dk}: [Accessed on 27/08/2019] \newline
-
-Shiab, Nael (2015) \textit{On the Ethics of Web Scraping and Data Journalism.
-Global Investigative Journalism Network.} [Online]: \href{https://gijn.org/2015/08/12/on-the-ethics-of-web-scraping-and-data-journalism/}{gijn.org/2015/08/12/on-the-ethics-of-web-scraping-and-data-journalism/}: [Accessed on 27/08/2019] \newline
-
-McKinney, W. (2018). 'Data Wrangling: Join, Combine and Reshape'. In W. McKinney, \textit{Python for Data Analysis}. Sebastopol: O'Reilly Media Inc. \newline
-
-Athey, Susan (2018) 'The Impact of Machine Learning on Economics' in Ajay Agrawal et al.
-(eds) \textit{The Economics of Artificial Intelligence: An Agenda} (2019).
-Chicago: University of Chicago Press.
-\newline
-
-Einav, Liran and Jonathan Levin (2014) \textit{Economics in the age of big data}. Science, vol. 346, November. \newline
-
-Grimmer, Justin (2015) \textit{We are all social scientists now: how big data, machine learning, and causal inference work together}.
-PS: Political Science \& Politics, vol.
-48, January: 80-83.
-\newline
-
-Lazer, David and Jason Radford (2017) \textit{Data ex Machina. Introduction to Big Data. Annual Review of Sociology}, vol. 43, August. \newline
-
-Mullainathan, Sendhil, and Jann Spiess (2017) \textit{Machine Learning: An Applied Econometric Approach}. Journal of Economic Perspectives, vol. 31 (2): 87-106. \newline
-
-Anderson, Chris (2008) \textit{The end of theory: The data deluge makes the scientific method obsolete}.
-Wired, 16-07 [Online] \href{https://www.wired.com/2008/06/pb-theory/}{www.wired.com/2008/06/pb-theory/} [Accessed on 27/08/2019]\newline
-
-Peckov, Aleksandar.
-(2012)  \textit{A Machine Learning Approach To Polynomial Regression}.
-Available at \href{http://kt.ijs.si/theses/phd_aleksandar_peckov.pdf}{kt.ijs.si/theses/phd\_aleksandar\_peckov.pdf}.
-Doctoral Dissertation.
-Jozef Stefan International Postgraduate School.
-Ljubljana, Slovenia, October 2012
-
-%Varian, Hal R. (2014) Big Data: New Tricks for Econometrics. Journal of Economic Perspectives. Vol. 28, April: 3-27 \newline
-
-\newpage
-\section{Appendixs}
-\subsubsection{}
-Excluded Features:\newline
-municipality, lotSize, unemployment, Total\_reported\_crime, Socioeconomic\_index, expenses\_per\_school\_student, expenses\_sport\_and\_other\_cultural\_activities, forest\_distance, coast\_distance, isForeclosure, owners\_expense
-\subsubsection{}
-The model used for prediction: 
-$$ \hat{Y_i}=\beta_0+\sum_{i=1}^n\hat{\beta_i}\textbf{T}_i+\hat{\epsilon_i},\quad T_i=\prod_{j=i}^mX_j^{d_i,j}
-\quad\footnote{Peckov, Aleksandar. \textit{A Machine Learning Approach To Polynomial Regression} p. 9}$$
-\small{$m$ being total number of features, $d_i,j$ denoting degree of polynomial features. 
-$$\textbf{X}_j=\begin{bmatrix}
-           basementSize \\
-           buildYear \\
-           rooms \\
-           size \\
-           primary\_school\_educ \\
-           high\_school\_educ \\
-           vocational\_educ \\
-           SHE \\
-           MHE \\
-           bachelors\_degree \\
-           LHE \\
-           avg\_municipal\_income\_2017 \\
-           Population\_in\_urban\_development \\
-           Socioeconomic\_index \\
-           lake\_distance\\
-           doctor\_distance \\
-           supermarket\_distance \\
-           school\_distance \\
-           daycare\_distance \\
-           hospital\_distance \\
-           train\_distance \\
-           pharmacy\_distance \\
-           library\_distance \\
-         \end{bmatrix}$$
 \end{document}

### 2019-08-29 Opsætningexam/DraftExam.tex
+

@@
 Ultimately, big data and machine learning could increase the scope of the social scientist's field, not only by delivering new data and methods, but by helping the social scientist to focus on new questions\footnote{Mullainathan, Sendhil, and Jann Spiess (2017) \textit{Machine Learning: An Applied Econometric Approach}}.
+
+\paragraph{Ethical concerns in the petabyte age\newline}
+The ethical principles of social research are anchored in the fundamental human rights, which are broadly formulated in the UN Declaration of Human Rights.
+Additional policies and declarations that codify principles of research ethics and the ethical treatment of research participants include the Nuremberg Code, the Helsinki Declaration, the Belmont Report, and the Menlo Report\footnote{Salganik, Matthew J.
+(2018) \textit{Bit by Bit Bit - Social research in the digital age.}}\, \footnote{European Commission (2018).
+\textit{Ethics in Social Sciences and the Humanities}}.
+These codes and addendums originate mostly in the biomedical field, though they encompass the central principles applied to all human research, which have led some academics to call for a Hippocratic oath for data scientists to safeguard against powerful new technologies under development in laboratories and tech firms\footnote{Rotblat, Joseph (1999) \textit{A Hippocratic Oath for Scientists}}\, \footnote{Sample, Ian (2019, Fri 16 Aug 2019) \textit{and tech specialists need Hippocratic oath, says academic.}}.
+This discussion is nothing new however, as a tentative reformulation of the Hippocratic oath was introduced by Karl Popper\footnote{Popper, Karl (1969) \textit{The Moral Responsibility of the Scientist}}, wherein he stressed the importance of professional responsibility, a critical mind, and an overriding loyalty towards the betterment of mankind.\newline
+Matthew Salganik offer four principles deduced from the Belmont and Menlo Report that should guide the ethical deliberations of the researcher: 1) the respect for persons, that is individuals should be treated as autonomous and if circumstances require it individuals should be entitled to additional protections.
+2) Beneficence stresses the importance of doing no harm and to maximize the possible benefits and minimizing any potential harms.
+3) The principle of justice touches upon the importance of the distribution of burdens and benefits of the social scientist's research.
+This principle stress that is should not be a single stratum of society that bears the costs of the research while another stratum benefits.
+4) The fourth and final principle is the respect for law and public interest, according to Salganik, the principle consists of two distinct elements, that is compliance to relevant laws and legal contracts and transparency-based accountability.
+It is worth noting that Popper’s tentative Hippocratic oath mirrors the first three principles put forth by Salganik, stressing the importance of the ethical conduct of the researcher.\newline
+The need for rigid ethical standards within computational social science was made apparent by the Cambridge Analytica Scandal that broke on the 17th of March 2018.
+Where Steve Bannon could reveal that between 2013 and 2015 Cambridge Analytica had exploited a loophole in Facebook’s API which allowed the company to harvest profile data from 87 million Facebook users, without the user’s permission and use the harvested data to construct a massive targeted marketing database based on the user’s likes and interests\footnote{Vox.com (2018) \textit{The Cambridge Analytica Facebook scandal} [Online]}.
+Other examples of misuse of data acquired from Facebook include the Harvard-run experiment, where students' data was used to create new knowledge about how social networks form and how these networks and their actors' behavior co-evolve, and the emotional contagion experiment from 2012, where approximately 700,000 users were involved in a research experiment to examine the extent to which a person's emotions are affected by the emotions of the people they interact with (Salganik.
+2018).\newline
+From this it should be evident that clear ethical guidelines are required in order to protect the user's privacy from tech-savvy companies.
+To this end, the European Parliament introduced the General Data Protection Regulation (GDPR).
+With its seven overarching principles the GDPR seeks to formalize the procedures involved in the data processing and storing of sensitive and private information (CDRC\footnote{Consumer Data Research Center, UK  [CDRC] (2018) \textit{The General Data Protection Regulation \& Social Science Research} [Online]:}).
+These principles include and expand upon the principles found in the Belmont and Menlo Report.
+The most important consideration, however, must be that even a dataset comprising tens of thousands of observations involve human beings who must be protected from adverse side-effects of the social research.
+There is considerable evidence that point to the fact that even in anonymized data sets it can be possible to backtrack an individual's identity.
+A researcher must therefore be mindful of the mosaic effect if the dataset combines large amount of data from various sources (European Commission 2018).
 
@@
 
+\paragraph{Learning Curve}
+We examine the learning curve of the model to examine whether the model suffers from immediate over- or underfitting problems and whether these would be remedied by collecting more data\footnote{Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow} p.
+196}
+The following plot illustrates the learning curve of our model:
+\begin{figure}[H]
+\centering
+\caption{}
+\includegraphics[scale=0.6]{Learncurvridge.png}
+%\source{}
+\end{figure}
+The plotted curved represent the average performance of the sets, while the width of the plotted curves expresses the 95\%-confidence interval of the performance.  
+Interpreting the graph could appear quite daunting, as the performances on the validation set are very inconsistent and varies a lot.
+Though inconsistent, it seems as if the gap is decreasing between the performances of the training- and validation sets as the sample size increases.
+At around 33,000 observations the validation curve drastically decreases and both curves flatten out.
+Though the confidence interval of the validation performance is still noteworthy it also improves dramatically when the sample gets sufficiently high.
+Just before 40,000 observations, the confidence interval of the validation curve actually drops below the train curve, which should not be possible.
+We have not found a meaningful explanation aside from noise or chance \footnote{\href{https://jakevdp.github.io/PythonDataScienceHandbook/05.03-hyperparameters-and-model-validation.html}{jakevdp.github.io/PythonDataScienceHandbook/05.03-hyperparameters-and-model-validation.html}}
+All in all, the learning curve would indicate that the performance of the model will not benefit from additional training data.
+
+\paragraph{Validation Curve}
+We examine the validation curve of the model to see whether we have found a good bias-variance-trade-off with our optimized hyperparameter.
+We plot the average train and cross-validation performance for different values of $\lambda$:
 \begin{figure}[H]
@@
 
-Firstly, we are somewhat satisfied with the average performance of the model.
-With an MSE of approximately $55\cdot10^{10}$ and a MAE of DKK 43,630.55, we find that the model performs quite well on unseen data.
+\textcolor{red}{Firstly, we are somewhat satisfied with the average performance of the model.
+With an MSE of approximately $55\cdot10^{10}$ and a MAE of DKK 43,630.55, we find that the model performs quite well on unseen data.}
 The curve suggest that we have found the optimal degree of regularization with our hyperparameter.
@@
 For the abovementioned reasons, it would not be meaningful to minimize this performance gab by adjusting the hyperparameter.
-Other options for decreasing the variance of the model, could be to include more training data, but as illustrated by the learning curve, this would not seem to make for more less variance.
+Other options for decreasing the variance of the model, could be to include more training data, but as illustrated by the learning curve, \textcolor{red}{this would not seem to make for more less variance}.
 Lastly, as overfitting is often caused by a sizeable number of features, omission would be a reasonable mean.
@@
 We can thus conclude that we have optimized our model under the given circumstances.
-
-The learning-curve is depicted in figure \textcolor{red}{XX}
-\begin{figure}[H]
-\centering
-\caption{}
-\includegraphics[scale=0.6]{Learncurvridge.png}
-%\source{}
-\end{figure}
 
@@
 
-\section{An Ethical Overview}
-The ethical principles of social research are anchored in the fundamental human rights, which are broadly formulated in the UN Declaration of Human Rights.
-Additional policies and declarations that codify principles of research ethics and the ethical treatment of research participants include the Nuremberg Code, the Helsinki Declaration, the Belmont Report, and the Menlo Report\footnote{Salganik, Matthew J.
-(2018) \textit{Bit by Bit Bit - Social research in the digital age.}}\, \footnote{European Commission (2018).
-\textit{Ethics in Social Sciences and the Humanities}}.
-These codes and addendums originate mostly in the biomedical field, though they encompass the central principles applied to all human research, which have led some academics to call for a Hippocratic oath for data scientists to safeguard against powerful new technologies under development in laboratories and tech firms\footnote{Rotblat, Joseph (1999) \textit{A Hippocratic Oath for Scientists}}\, \footnote{Sample, Ian (2019, Fri 16 Aug 2019) \textit{and tech specialists need Hippocratic oath, says academic.}}.
-This discussion is nothing new however, as a tentative reformulation of the Hippocratic oath was introduced by Karl Popper\footnote{Popper, Karl (1969) \textit{The Moral Responsibility of the Scientist}}, wherein he stressed the importance of professional responsibility, a critical mind, and an overriding loyalty towards the betterment of mankind.\newline
-Matthew Salganik offer four principles deduced from the Belmont and Menlo Report that should guide the ethical deliberations of the researcher: 1) the respect for persons, that is individuals should be treated as autonomous and if circumstances require it individuals should be entitled to additional protections.
-2) Beneficence stresses the importance of doing no harm and to maximize the possible benefits and minimizing any potential harms.
-3) The principle of justice touches upon the importance of the distribution of burdens and benefits of the social scientist's research.
-This principle stress that is should not be a single stratum of society that bears the costs of the research while another stratum benefits.
-4) The fourth and final principle is the respect for law and public interest, according to Salganik, the principle consists of two distinct elements, that is compliance to relevant laws and legal contracts and transparency-based accountability.
-It is worth noting that Popper’s tentative Hippocratic oath mirrors the first three principles put forth by Salganik, stressing the importance of the ethical conduct of the researcher.\newline
-The need for rigid ethical standards within computational social science was made apparent by the Cambridge Analytica Scandal that broke on the 17th of March 2018.
-Where Steve Bannon could reveal that between 2013 and 2015 Cambridge Analytica had exploited a loophole in Facebook’s API which allowed the company to harvest profile data from 87 million Facebook users, without the user’s permission and use the harvested data to construct a massive targeted marketing database based on the user’s likes and interests\footnote{Vox.com (2018) \textit{The Cambridge Analytica Facebook scandal} [Online]}.
-Other examples of misuse of data acquired from Facebook include the Harvard-run experiment, where students' data was used to create new knowledge about how social networks form and how these networks and their actors' behavior co-evolve, and the emotional contagion experiment from 2012, where approximately 700,000 users were involved in a research experiment to examine the extent to which a person's emotions are affected by the emotions of the people they interact with (Salganik.
-2018).\newline
-From this it should be evident that clear ethical guidelines are required in order to protect the user's privacy from tech-savvy companies.
-To this end, the European Parliament introduced the General Data Protection Regulation (GDPR).
-With its seven overarching principles the GDPR seeks to formalize the procedures involved in the data processing and storing of sensitive and private information (CDRC\footnote{Consumer Data Research Center, UK  [CDRC] (2018) \textit{The General Data Protection Regulation \& Social Science Research} [Online]:}).
-These principles include and expand upon the principles found in the Belmont and Menlo Report.
-The most important consideration, however, must be that even a dataset comprising tens of thousands of observations involve human beings who must be protected from adverse side-effects of the social research.
-There is considerable evidence that point to the fact that even in anonymized data sets it can be possible to backtrack an individual's identity.
-A researcher must therefore be mindful of the mosaic effect if the dataset combines large amount of data from various sources (European Commission 2018).
-
 \newpage
@@
 Jozef Stefan International Postgraduate School.
-Ljubljana, Slovenia, October 2012
+Ljubljana, Slovenia, October 2012.
+[Accessed on 29/08/2019]
 
+(https://jakevdp.github.io/PythonDataScienceHandbook/05.03-hyperparameters-and-model-validation.html). [Accessed on 29/08/2019]
 %Varian, Hal R. (2014) Big Data: New Tricks for Econometrics. Journal of Economic Perspectives. Vol. 28, April: 3-27 \newline

### 2019-08-29 Opsætningexam/DraftExam.tex
e

@@
 \section{Introduction}
-This report depicts a research performed regarding active Danish real-estate property valuations from 2016-2019.
+This report depictss a research performed regarding active Danish real-estate property valuations from 2016-2019.
 Since 2011, the yearly number of real estate properties sold has slightly increased, with 2017 being the year with most sold properties in 10 years \href{https://www.dst.dk/da/Statistik/nyt/NytHtml?cid=27979}{(Danmarks Statistik, 2018)}.
@@
 Ultimately, big data and machine learning could increase the scope of the social scientist's field, not only by delivering new data and methods, but by helping the social scientist to focus on new questions\footnote{Mullainathan, Sendhil, and Jann Spiess (2017) \textit{Machine Learning: An Applied Econometric Approach}}.
-
-\paragraph{Ethical concerns in the petabyte age\newline}
-The ethical principles of social research are anchored in the fundamental human rights, which are broadly formulated in the UN Declaration of Human Rights.
-Additional policies and declarations that codify principles of research ethics and the ethical treatment of research participants include the Nuremberg Code, the Helsinki Declaration, the Belmont Report, and the Menlo Report\footnote{Salganik, Matthew J.
-(2018) \textit{Bit by Bit Bit - Social research in the digital age.}}\, \footnote{European Commission (2018).
-\textit{Ethics in Social Sciences and the Humanities}}.
-These codes and addendums originate mostly in the biomedical field, though they encompass the central principles applied to all human research, which have led some academics to call for a Hippocratic oath for data scientists to safeguard against powerful new technologies under development in laboratories and tech firms\footnote{Rotblat, Joseph (1999) \textit{A Hippocratic Oath for Scientists}}\, \footnote{Sample, Ian (2019, Fri 16 Aug 2019) \textit{and tech specialists need Hippocratic oath, says academic.}}.
-This discussion is nothing new however, as a tentative reformulation of the Hippocratic oath was introduced by Karl Popper\footnote{Popper, Karl (1969) \textit{The Moral Responsibility of the Scientist}}, wherein he stressed the importance of professional responsibility, a critical mind, and an overriding loyalty towards the betterment of mankind.\newline
-Matthew Salganik offer four principles deduced from the Belmont and Menlo Report that should guide the ethical deliberations of the researcher: 1) the respect for persons, that is individuals should be treated as autonomous and if circumstances require it individuals should be entitled to additional protections.
-2) Beneficence stresses the importance of doing no harm and to maximize the possible benefits and minimizing any potential harms.
-3) The principle of justice touches upon the importance of the distribution of burdens and benefits of the social scientist's research.
-This principle stress that is should not be a single stratum of society that bears the costs of the research while another stratum benefits.
-4) The fourth and final principle is the respect for law and public interest, according to Salganik, the principle consists of two distinct elements, that is compliance to relevant laws and legal contracts and transparency-based accountability.
-It is worth noting that Popper’s tentative Hippocratic oath mirrors the first three principles put forth by Salganik, stressing the importance of the ethical conduct of the researcher.\newline
-The need for rigid ethical standards within computational social science was made apparent by the Cambridge Analytica Scandal that broke on the 17th of March 2018.
-Where Steve Bannon could reveal that between 2013 and 2015 Cambridge Analytica had exploited a loophole in Facebook’s API which allowed the company to harvest profile data from 87 million Facebook users, without the user’s permission and use the harvested data to construct a massive targeted marketing database based on the user’s likes and interests\footnote{Vox.com (2018) \textit{The Cambridge Analytica Facebook scandal} [Online]}.
-Other examples of misuse of data acquired from Facebook include the Harvard-run experiment, where students' data was used to create new knowledge about how social networks form and how these networks and their actors' behavior co-evolve, and the emotional contagion experiment from 2012, where approximately 700,000 users were involved in a research experiment to examine the extent to which a person's emotions are affected by the emotions of the people they interact with (Salganik.
-2018).\newline
-From this it should be evident that clear ethical guidelines are required in order to protect the user's privacy from tech-savvy companies.
-To this end, the European Parliament introduced the General Data Protection Regulation (GDPR).
-With its seven overarching principles the GDPR seeks to formalize the procedures involved in the data processing and storing of sensitive and private information (CDRC\footnote{Consumer Data Research Center, UK  [CDRC] (2018) \textit{The General Data Protection Regulation \& Social Science Research} [Online]:}).
-These principles include and expand upon the principles found in the Belmont and Menlo Report.
-The most important consideration, however, must be that even a dataset comprising tens of thousands of observations involve human beings who must be protected from adverse side-effects of the social research.
-There is considerable evidence that point to the fact that even in anonymized data sets it can be possible to backtrack an individual's identity.
-A researcher must therefore be mindful of the mosaic effect if the dataset combines large amount of data from various sources (European Commission 2018).
 
@@
 
+\section{An Ethical Overview}
+The ethical principles of social research are anchored in the fundamental human rights, which are broadly formulated in the UN Declaration of Human Rights.
+Additional policies and declarations that codify principles of research ethics and the ethical treatment of research participants include the Nuremberg Code, the Helsinki Declaration, the Belmont Report, and the Menlo Report\footnote{Salganik, Matthew J.
+(2018) \textit{Bit by Bit Bit - Social research in the digital age.}}\, \footnote{European Commission (2018).
+\textit{Ethics in Social Sciences and the Humanities}}.
+These codes and addendums originate mostly in the biomedical field, though they encompass the central principles applied to all human research, which have led some academics to call for a Hippocratic oath for data scientists to safeguard against powerful new technologies under development in laboratories and tech firms\footnote{Rotblat, Joseph (1999) \textit{A Hippocratic Oath for Scientists}}\, \footnote{Sample, Ian (2019, Fri 16 Aug 2019) \textit{and tech specialists need Hippocratic oath, says academic.}}.
+This discussion is nothing new however, as a tentative reformulation of the Hippocratic oath was introduced by Karl Popper\footnote{Popper, Karl (1969) \textit{The Moral Responsibility of the Scientist}}, wherein he stressed the importance of professional responsibility, a critical mind, and an overriding loyalty towards the betterment of mankind.\newline
+Matthew Salganik offer four principles deduced from the Belmont and Menlo Report that should guide the ethical deliberations of the researcher: 1) the respect for persons, that is individuals should be treated as autonomous and if circumstances require it individuals should be entitled to additional protections.
+2) Beneficence stresses the importance of doing no harm and to maximize the possible benefits and minimizing any potential harms.
+3) The principle of justice touches upon the importance of the distribution of burdens and benefits of the social scientist's research.
+This principle stress that is should not be a single stratum of society that bears the costs of the research while another stratum benefits.
+4) The fourth and final principle is the respect for law and public interest, according to Salganik, the principle consists of two distinct elements, that is compliance to relevant laws and legal contracts and transparency-based accountability.
+It is worth noting that Popper’s tentative Hippocratic oath mirrors the first three principles put forth by Salganik, stressing the importance of the ethical conduct of the researcher.\newline
+The need for rigid ethical standards within computational social science was made apparent by the Cambridge Analytica Scandal that broke on the 17th of March 2018.
+Where Steve Bannon could reveal that between 2013 and 2015 Cambridge Analytica had exploited a loophole in Facebook’s API which allowed the company to harvest profile data from 87 million Facebook users, without the user’s permission and use the harvested data to construct a massive targeted marketing database based on the user’s likes and interests\footnote{Vox.com (2018) \textit{The Cambridge Analytica Facebook scandal} [Online]}.
+Other examples of misuse of data acquired from Facebook include the Harvard-run experiment, where students' data was used to create new knowledge about how social networks form and how these networks and their actors' behavior co-evolve, and the emotional contagion experiment from 2012, where approximately 700,000 users were involved in a research experiment to examine the extent to which a person's emotions are affected by the emotions of the people they interact with (Salganik.
+2018).\newline
+From this it should be evident that clear ethical guidelines are required in order to protect the user's privacy from tech-savvy companies.
+To this end, the European Parliament introduced the General Data Protection Regulation (GDPR).
+With its seven overarching principles the GDPR seeks to formalize the procedures involved in the data processing and storing of sensitive and private information (CDRC\footnote{Consumer Data Research Center, UK  [CDRC] (2018) \textit{The General Data Protection Regulation \& Social Science Research} [Online]:}).
+These principles include and expand upon the principles found in the Belmont and Menlo Report.
+The most important consideration, however, must be that even a dataset comprising tens of thousands of observations involve human beings who must be protected from adverse side-effects of the social research.
+There is considerable evidence that point to the fact that even in anonymized data sets it can be possible to backtrack an individual's identity.
+A researcher must therefore be mindful of the mosaic effect if the dataset combines large amount of data from various sources (European Commission 2018).
+
 \newpage

### 2019-08-29 Opsætningexam/DraftExam.tex
samletversionmankanlæse

--- 2019-08-29 Opsætningexam/DraftExam.tex
@@
 \end{table}
-The Ridge model with three degrees of polynomial features are selected as the best performing model. In regard to MAE as well as MSE.\newline
+Since our efforts are aimed at predicting the valuation of a given real-estate, we want to penalize the size of the error the MSE-score is a better indicator for our model's performance as opposed to the mean absolute error (MAE).
+Since MSE squares the error terms, it gives a relatively high weight to large errors, which is desirable for our current aim.
+
+From table XX it is evident that the machine learning model with two degrees of polynomial features performs best with a regularization by LASSO as it has the lowest measures of difference between the predicted price and the true price, with a MSE of 5.91E+10, whilst the model with 3 degrees of polynomial features regularized by ridge regression performs even better with a MSE 5.57E+10.
+Therefore, we chose this model as the final model from which we will conduct the rest of the analysis with.
+\newline
+
 We examine the validation curve, figure \textcolor{red}{XX}, of the model to examine whether we have found a good bias-variance-balance with our optimized hyperparameter.
@@
 For the abovementioned reasons, it would not be meaningful to minimize this performance gab by adjusting the hyperparameter.
-Other options for decreasing the variance of the model, could be to include more training data, but as illustrated by the learning curve, \textcolor{red}{this would not seem to make for more less variance}.
+Other options for decreasing the variance of the model, could be to include more training data, but as illustrated by the learning curve, this would not seem effect the variance.
 Lastly, as overfitting is often caused by a sizeable number of features, omission would be a reasonable mean.
@@
 \section{Discussion}
+\subsection{No grit search}
+
 \subsection{Data critique}
@@
 Finally, we have discussed the results of our analysis. We have critically assessed the boundaries of our research and drawn up potential possibilities for improvement.
+
+\section{An Ethical Overview}
+The ethical principles of social research are anchored in the fundamental human rights, which are broadly formulated in the UN Declaration of Human Rights.
+Additional policies and declarations that codify principles of research ethics and the ethical treatment of research participants include the Nuremberg Code, the Helsinki Declaration, the Belmont Report, and the Menlo Report\footnote{Salganik, Matthew J.
+(2018) \textit{Bit by Bit Bit - Social research in the digital age.}}\, \footnote{European Commission (2018).
+\textit{Ethics in Social Sciences and the Humanities}}.
+These codes and addendums originate mostly in the biomedical field, though they encompass the central principles applied to all human research, which have led some academics to call for a Hippocratic oath for data scientists to safeguard against powerful new technologies under development in laboratories and tech firms\footnote{Rotblat, Joseph (1999) \textit{A Hippocratic Oath for Scientists}}\, \footnote{Sample, Ian (2019, Fri 16 Aug 2019) \textit{and tech specialists need Hippocratic oath, says academic.}}.
+This discussion is nothing new however, as a tentative reformulation of the Hippocratic oath was introduced by Karl Popper\footnote{Popper, Karl (1969) \textit{The Moral Responsibility of the Scientist}}, wherein he stressed the importance of professional responsibility, a critical mind, and an overriding loyalty towards the betterment of mankind.\newline
+Matthew Salganik offer four principles deduced from the Belmont and Menlo Report that should guide the ethical deliberations of the researcher: 1) the respect for persons, that is individuals should be treated as autonomous and if circumstances require it individuals should be entitled to additional protections.
+2) Beneficence stresses the importance of doing no harm and to maximize the possible benefits and minimizing any potential harms.
+3) The principle of justice touches upon the importance of the distribution of burdens and benefits of the social scientist's research.
+This principle stress that is should not be a single stratum of society that bears the costs of the research while another stratum benefits.
+4) The fourth and final principle is the respect for law and public interest, according to Salganik, the principle consists of two distinct elements, that is compliance to relevant laws and legal contracts and transparency-based accountability.
+It is worth noting that Popper’s tentative Hippocratic oath mirrors the first three principles put forth by Salganik, stressing the importance of the ethical conduct of the researcher.\newline
+The need for rigid ethical standards within computational social science was made apparent by the Cambridge Analytica Scandal that broke on the 17th of March 2018.
+Where Steve Bannon could reveal that between 2013 and 2015 Cambridge Analytica had exploited a loophole in Facebook’s API which allowed the company to harvest profile data from 87 million Facebook users, without the user’s permission and use the harvested data to construct a massive targeted marketing database based on the user’s likes and interests\footnote{Vox.com (2018) \textit{The Cambridge Analytica Facebook scandal} [Online]}.
+Other examples of misuse of data acquired from Facebook include the Harvard-run experiment, where students' data was used to create new knowledge about how social networks form and how these networks and their actors' behavior co-evolve, and the emotional contagion experiment from 2012, where approximately 700,000 users were involved in a research experiment to examine the extent to which a person's emotions are affected by the emotions of the people they interact with (Salganik.
+2018).\newline
+From this it should be evident that clear ethical guidelines are required in order to protect the user's privacy from tech-savvy companies.
+To this end, the European Parliament introduced the General Data Protection Regulation (GDPR).
+With its seven overarching principles the GDPR seeks to formalize the procedures involved in the data processing and storing of sensitive and private information (CDRC\footnote{Consumer Data Research Center, UK  [CDRC] (2018) \textit{The General Data Protection Regulation \& Social Science Research} [Online]:}).
+These principles include and expand upon the principles found in the Belmont and Menlo Report.
+The most important consideration, however, must be that even a dataset comprising tens of thousands of observations involve human beings who must be protected from adverse side-effects of the social research.
+There is considerable evidence that point to the fact that even in anonymized data sets it can be possible to backtrack an individual's identity.
+A researcher must therefore be mindful of the mosaic effect if the dataset combines large amount of data from various sources (European Commission 2018).
 

### 2019-08-29 Opsætningexam/DraftExam.tex
3
push

@@
 \section{Introduction}
-This report depicts a research performed regarding active Danish real-estate property valuations from 2016-2019.
-Since 2011, the yearly number of real estate properties sold has slightly increased, with 2017 being the year with most sold properties in 10 years \href{https://www.dst.dk/da/Statistik/nyt/NytHtml?cid=27979}{(Danmarks Statistik, 2018)}.
+This report depicts a research performed regarding active Danish real estate property valuations.
+Since 2011, the annual number of real estate properties sold has slightly increased, with 2017 being the year with most sold properties in 10 years \href{https://www.dst.dk/da/Statistik/nyt/NytHtml?cid=27979}{(Danmarks Statistik, 2018)}.
 The price of real estate properties is also rising through 2019 \href{https://www.dst.dk/da/Statistik/nyt/NytHtml?cid=28741}{(Danmarks Statistik, 2019)}.
-Although this generally depicts a willingness of buyers to pay more for real-estate property, and higher valuations from agents, a closer analysis of current and active valuations add a local view of which conditions contribute to the valuation of a real-estate property.
+Although this generally depicts a willingness of buyers to pay more for real estate property, and higher valuations from realtors, a closer analysis of active valuations adds a local view of which conditions contribute to the valuation of a real estate property.
 \newline
@@
 Figure 1 shows the average square meter price valuation of active offers per municipality in Denmark.
-The maximum square meter price being approximately 8 times higher in the municipality of Gentofte, than Lolland, the municipality with lowest average square meter price valuations.
-A tendency visualized in the figure, is that average square meter price valuations are higher in in highly populated municipalities and in suburban areas surrounding Copenhagen.
+The maximum square meter price being approximately 8 times higher in the municipality of Gentofte, than Lolland, the municipality with the lowest average square meter price valuations.
+A tendency visualized in the figure, is that average square meter price valuations are higher in highly populated municipalities and in suburban areas surrounding Copenhagen.
 \newline
 
-The valuations included in the research are collected from one of Denmarks largest online real-estate websites named Boliga.dk.
-The Boliga data contains approximately 66,000 active offerings with valuations ranging from 15,000 to 85 million.
-DKK.
-This research paper intends to analyze real estate price valuations and which effects geo- and sociodemographic criteria affect valuations, using machine learning models.
-Our research questions is as follows:
+The valuations included in the research are collected from one of Denmarks largest online real estate websites named Boliga.dk.
+The Boliga data contains approximately 66,000 active offerings with valuations ranging from DKK.
+15,000 to DKK.
+85 million.
+This research paper intends to analyze real estate price valuations and which geo- and sociodemographic criteria affect valuations, using machine learning models.
+Our research question is as follows:
 \begin{center}
- \textit{Which features are most relevant for predicting evaluations of real estate properties in Denmark?}
+ \textit{Which features are most relevant for predicting valuations of real estate properties in Denmark?}
 \end{center}
-This research paper contains a section describing the construction of research data and assesses the choices made in gathering meaningful features for the machine learning model.
-Also, a section regarding the choice and optimization of machine learning models is included, where the intention is to provide insights on our progress on finding the optimal model.
-As a result, a preferable machine learning model is chosen with a discussion of its usability.
+This research paper contains a section describing the construction of research data and assesses the choices made in gathering meaningful features for the dataset.
+Also, a section regarding the choice and optimization of machine learning models is included, where the intention is to provide insights on our progress of finding the optimal model.
+As a result, the best performing model is chosen with a discussion of its usability.
 
 \section{Literature Review}
-Within data social science there exist widely differing definitions of big data and machine learning. This section seeks to clarify the use of these terms within the scope of this paper.
-\paragraph{On big data \& machine learning\newline}
+Within social data science there exist widely differing definitions of big data and machine learning. This section seeks to clarify the use of these terms within the scope of this paper.
+\paragraph{On Big Data \& Machine Learning\newline}
 Historically, big data has been a term reserved for data that was unable to be processed by extant software.
@@
 (2018) \textit{Bit by Bit Bit - Social research in the digital age.}} instead mentions ten typical characteristics of big data.
-Salganik's tentative definition suggests that big data is not as single entity, but includes many different types of systems.
+Salganik's tentative definition suggests that big data is not a single entity, but includes many different types of systems.
 Among the most important features of Salganik's definition of big data is that the data has a high frequency of observations and is continuously being generated.
@@
 It is therefore important to understand that big data is not a naturally occurring system, but driven by the engineered purpose of the system.
-This algorithmic confounding forces the scientist to be careful regarding any observed human behaviour that is extracted from a single digital system.\newline
+This algorithmic confounding force the scientist to be careful regarding any observed human behaviour that is extracted from a single digital system.\newline
 In the analysis of big data it is often useful to employ machine learning as it can identify and predict various non-linear relationships in big data sets, that otherwise would remain hidden.
@@
 One of the major discussions revolve around machine learning's predictive capabilities.
-Chris Anderson\footnote{Anderson, Chris (2008) \textit{The end of theory: The data deluge makes the scientific method obsolete}} (2008) argues that since the computing power and the scale of data has increased exponentially, our reliance of scientific models could become obsolete.
+Chris Anderson\footnote{Anderson, Chris.
+(2008), \textit{The end of theory: The data deluge makes the scientific method obsolete}} argues that since the computing power and the scale of data has increased exponentially, our reliance on scientific models could become obsolete.
 Instead of focusing on the theoretical implications of observations, scientists should, according to Anderson, focus on the statistical outputs: In the age of big data, correlation perhaps should supersede causality and consequently social data scientists should not try to develop coherent models or unified theories to explain a social phenomenon.\newline
@@
 It requires a rigorous research design and clear theoretical assumptions, in order to yield scientifically accurate estimates.
-Indeed social sciences greatest contribution to big data research, comes from the organized framework provided by rigorously tested theory\footnote{Einav, Liran and Jonathan Levin (2014) \textit{Economics in the age of big data}}.\newline
+Indeed the social sciences greatest contribution to big data research, comes from the organized framework provided by rigorously tested theory\footnote{Einav, Liran and Jonathan Levin (2014) \textit{Economics in the age of big data}}.\newline
 The contribution from the social sciences to machine learning help create new methods that will be able to utilize the strengths of machine learning to help solve causal inference problems within the framework of a well defined theory\footnote{Athey, Susan (2018) 'The Impact of Machine Learning on Economics' in Ajay Agrawal et al.
@@
 Drawing upon the European Comissions\footnote{European Commission (2018).
-\textit{Ethics in Social Sciences and the Humanities}} ethical guidelines and principles for ethical conduct in social data science, the potential harm to users of Boliga's web-page were carefully considered.
+\textit{Ethics in Social Sciences and the Humanities}} guidelines and principles for ethical conduct in social data science, the potential harm to users of Boliga's web-page were carefully considered.
 As a step to prevent the mosaic effect and in an effort to anonymize the scraped data only aggregated data will be presented in this paper, so that no single observation can be identified from the analysed data.\newline
 No informed consent has been obtained from the users of the site, prompting us to consider the consequences of the lack thereof, as informed consent is paramount to the proper, ethical conduct in social science.
-However, sometimes, as in this instance, informed consent can be logistically impossible to collect from all participants in the study.
+However, as in this instance, informed consent can be logistically impossible to collect from all participants in the study.
 Salganik mentions that informed consent for everything is an ideal, but in practice impossible to obtain and researchers should instead strive to follow an alternative rule, that he describes as: "some form of consent for most things." \footnote{Salganik, Matthew J.
-(2018) \textit{Bit by Bit Bit - Social research in the digital age.} p.303} Adhering to this, more complex  understanding of the practicality of informed consent, we chose to contact Boliga to inform them of our intent to scrape their website and use the data in an educational context.
+(2018) \textit{Bit by Bit - Social research in the digital age.} p.303} Adhering to this, more complex understanding of the practicality of informed consent, we chose to contact Boliga to inform them of our intent to scrape their website and use the data in an educational context\footnote{Shiab, Nael (2015) \textit{On the Ethics of Web Scraping and Data Journalism}.
 Boliga responded positively to our inquiry, which we took as informed consent from a third party on behalf of the participating users in our study.\newline
@@
 Furthermore, we consulted with Boliga's Terms and Conditions to avoid any legal ramifications and the appropriate contractual terms of interest can be seen in \href{https://www.boliga.dk/vilkaar-og-betingelser}{§10 Terms and Conditions}.
-In order to comply with these terms we refrained from burdening their website's performance by implementing a time.sleep function, which causes each scraping iteration to pause for 0.5 seconds before commencing on scraping the next page \textcolor{red}{(see appendix XX)}.
-Furthermore, Boliga prohibits the use of automated scrapers and bots, which we did not do, as our scraping was done in a specified time-frame and we did not automate the procedure to be done on multiple occasions.
+In order to comply with these terms we refrained from burdening their website's performance by implementing a time.sleep function.
+This causes each scraping iteration to pause for 0.5 seconds before commencing on scraping the next page \textcolor{red}{(see Jupyter XX)}.
 \subsection{Data Scraping Process}
@@
 \paragraph{\href{https://www.boliga.dk}{Boliga}\newline}
-Our data comes from \href{https://www.boliga.dk}{Boliga.dk}, the largest independent online web-portal for real-estate sales in Denmark and has access to unique features such as "liggetid", price-development and access to BBR - the Danish Building and Housing Register \footnote{\href{https://www.boligagruppen.dk}{www.boligagruppen.dk}}.
-Giving us unique insights into the pricing of real-estate in all 98 municipalities of Denmark.
-At the time of scraping 65,950 properties were for sale.\newline
-The scraping process was conducted on Friday the 23rd of August 2019.
-We had advised Boliga of our intent to collect data from their website via our scraper in an effort to identify ourselves and our intent\footnote{Shiab, Nael (2015) \textit{On the Ethics of Web Scraping and Data Journalism}.
+Our data comes from \href{https://www.boliga.dk}{Boliga.dk}, the largest independent online web-portal for real estate sales in Denmark and has access to unique features such as days-for-sale, price-development and access to BBR - the Danish Building and Housing Register \footnote{\href{https://www.boligagruppen.dk}{www.boligagruppen.dk}}.
+Giving us unique insights into the pricing of real estate in all 98 municipalities of Denmark.
+65,950 properties were for sale at the time of scraping.\newline
+The scraping process was conducted on Friday the $23^{rd}$ of August 2019.
 Global Investigative Journalism Network.}.
 In order to scrape the data of interest we familiarized ourselves with the HTML-structure of Boliga.
-On the basis of these insights we constructed a code, which were able to scrape every page, containing information pertaining the currently listed real-estates on Boliga.
+On the basis of these insights we constructed a code, which was able to scrape every page, containing information pertaining the currently listed real estates on Boliga.
 The scraper requested all information available from each individual page, which surmounted to 1,319 URL requests.
 \newline
-For each URL, 34 features and the target variable (price) was collected.
+For each listed property, 34 features and the target variable (price) was collected.
 Table \textcolor{red}{XX} provides an overview of the features with a short description, and whether the feature has been dropped or saved for later usage.
@@
 3. The feature is poorly formatted and cannot efficiently be recreated. 
+11 features are considered to be of interest.
 \vspace*{10px} \newline
@@
 \begin{tabular}{c c}
-Categorical: & ForClosure, Type, Municipality, lotSize	, price, rooms, size  \\	
+Categorical: & ForClosure, Type, Municipality, lotSize	 \\	
 \end{tabular}
 \paragraph{\href{https://www.hvorlangterder.dk}{Hvorlangterder.dk}\newline}
-\href{https://www.hvorlangterder.dk}{hvorlangterder.dk} returns distances from a given address, to conveniences such as supermarkets, hospitals and schools.   
+\href{https://www.hvorlangterder.dk}{hvorlangterder.dk} returns distances from a given address, to everyday commodities such as supermarkets, hospitals and schools.   
 The scraping of \href{https://www.hvorlangterder.dk}{hvorlangterder.dk} was achieved by writing a function that took in the GPS-coordinates gathered from Boliga.
-It constructed a URL (65,950 URL request), \textcolor{red}{which was scraped and the json response was returned as a dictionary of distances to the points of interest.
-The values from each key in the dictionary was then extracted as a new column in a Pandas DataFrame}.\newline
-As Jupyter performs poorly at running long asynchronous tasks and estimated a running time of 18 hours this procedure was run in Visual Studio.
+The function returned 65,950 URL responses, from which relevant information was extracted.\newline
+As Jupyter performs poorly when running long asynchronous tasks and estimated a running time of 18 hours this procedure was run in Visual Studio.
  \vspace*{10px} \newline
@@
 \end{tabular}
-\paragraph{Social and economic factors\newline}
-Social and economic factors on municipality level is collected from \href{https://statistik.politi.dk/QvAJAXZfc/opendoc.htm?document=QlikApplication%2F2999_Public\%2FPublic_IndsatsResultater.qvw}{statistik.politi.dk} and
+\paragraph{Socioeconomic Factors\newline}
+Socioeconomic factors on municipality level was collected from \href{https://statistik.politi.dk/QvAJAXZfc/opendoc.htm?document=QlikApplication%2F2999_Public\%2FPublic_IndsatsResultater.qvw}{statistik.politi.dk} and
 \href{https://www.dst.dk/da/Statistik/emner/befolkning-og-valg}{Danmarks Statistik} respectively.
-These factors include income, reported crime, level of highest completed education etc.
+The factors include income, reported crime, level of highest completed education etc.
 These are transformed into ratios, by taking the total population in a given municipality into account.
@@
 \end{tabular}\newline 
-\small {All educational features are a measure of highest completed education. Furthermore SHE, MHE, LHE are abbreviations of short-, medium- and long-cycle higher education}. 
+\footnotesize{\textit{All educational features are a measure of highest completed education. Furthermore SHE, MHE, LHE are abbreviations of short-, medium- and long-cycle higher education}}. 
 \normalsize
-\subsection{Log Analysis}
+\subsection{Analysis of Scraping Logs}
+Three datasets were obtained through web scraping from Boliga.dk, Hvorlangterder.dk and DAWA.dk.
+This section will analyze the logs created in the scraping process, with the intention of providing evidence of the data quality.
+The analysis the scraping logs was done according to Snorres demand on analyzing logs.
+\paragraph{Response Code}
+When parsing data from websites, the goal is to receive a response code ‘200’, expressing a successful request.
+\textcolor{red}{Fig XA} displays response codes for the duration of the web scrapings.
+Every single request received a response code 200.
+Further evaluation of the response codes was not necessary.
+\begin{figure}[H]
+  \centering
+   \caption{}
+   \includegraphics[width=\linewidth]{1log.png} 
+  \label{fig:}
+\end{figure}
+
+\paragraph{Error Codes}
+\textcolor{red}{Figure XB} plots errors codes received throughout the duration of the scrapings.
+Boliga and DAWA received no errors, while hvorlangterder received a total of 80 errors.
+The error code returns the same response in all 80 cases: \small{\textbf{('Connection aborted.', RemoteDisconnected('Remote end closed connection without response'))}}
+\begin{figure}[H]
+  \centering
+   \caption{}
+   \includegraphics[width=\linewidth]{2log.png} 
+  \label{fig:}
+\end{figure}
+To understand the errors, a closer manual analysis of the log was performed on requests receiving errors.
+The errors occur in random intervals and are subsequently followed by another request to an identical URL.
+Therefore, we assessed that these errors were due to connection problems or server traffic.
+Since the errors were corrected by a following request, we assessed it would not affect the research.
+
+\paragraph{Server Response Times}
+An indicator of poor data quality is varying the response times from the server being scraped.
+\textcolor{red}{Figure XC} plots changes in response times for the duration of the web scrapings.
+The 3 data sources all resulted in few variations of response times.
+Responses times differing from usual within the logs, have been assessed to be caused by two either a slow server time or connection, or due to larger quantities of data being requested.
+To validate the quality of data, manual control of the returned result and the webpage result was performed, without the notice of significant corruptions in the data to be utilized in the research.
+\begin{figure}[H]
+  \centering
+   \caption{}
+   \includegraphics[width=\linewidth]{3log.png} 
+  \label{fig:}
+\end{figure}
+
+\paragraph{Response Sizes}
+To validate the response quality, an assessment of the response size was performed.
+\textcolor{red}{Figure XD} plots response sizes throughout the duration of the web scrapings.
+Boliga contains a single noticeable large response size within short time, while hvorlangterder response sizes vary throughout the scrape.
+The DAWA scrape resulted in indifferent response sizes, and therefore needed no further investigation.
+\begin{figure}[H]
+  \centering
+   \caption{}
+   \includegraphics[width=\linewidth]{4log.png} 
+  \label{fig:}
+\end{figure}
+With a further analysis the distribution of sample sizes in figure XE, the Boliga and DAWA response sizes seem to be close to normally distributed, except for two single cases of large sample sizes in the Boliga log.
+By manually assessing the returned output of the Boliga scrape, these two requests were found to return a larger amount of data than usual.
+The two requests were made to two pages, where few properties contain nested dictionary attributes approximately 59 times larger than the average size of dictionaries within the ‘image’ data column.
+These dictionaries are image descriptions, and are not utilized within this research.
+These larger responses were deemed as not polluting the results of the research.
+\begin{figure}[H]
+  \centering
+   \caption{}
+   \includegraphics[width=\linewidth]{5log.png} 
+  \label{fig:}
+\end{figure}
+\textcolor{red}{Figure XE depicts that the hvorlangerder response sizes are a bit left scewed, while Figure XD} shows that the distribution of large sizes happens during the middle of the scrape.
+With a further glimpse into the log, we observed two things.
+First, all response sizes of 0 are related to the errors, displayed in figure XB.
+The variance of responses could be explained by the type of data retrieved from the scrape.
+The request was set to return names, addresses, distances and other information, which sizes are varying in nature.
+When extracting the value from every single key of the dictionary output, no errors or missing values were found.
+Further control of samples of large and small sizes were performed without discovering flaws.
+The response sizes from hvorlangterder are found to vary by nature, which may explain the difference.
+
+\paragraph{Assesment of the Scraping Logs}
+The individual analyses of the scraping logs showed minor suspicious traits which were assessed manually through the output or logs.
+The most concerning analysis being difference in response sizes and response times from the hvorlangterder scrape.
+This scrape consumed large amounts of time and computing power, as every single observation from the Boliga data, had to be input for requesting a response.
+In an extensive research, these problems could be handled by gaining direct access to the website instead of scraping and would benefit by running on a server with greater computing power.
+The results of the data collection were evaluated to be satisfying, and not corrupting the results of our research, as fairly reasonable explanations for noticeable dissimilarities within the logs were found.
+
+\paragraph{Critique of Logs Using Scraping Class}
+In the process of analyzing the scraping logs, minor flaws from the scraping library named ‘scraping\_class’ were detected.
+The returned columns ‘t’ and ‘delta\_t’ contained non-generic formats of epoch time.
+This was fixed by applying string manipulation and datetime conversions.
 
@@
 Here we focused our efforts on the removing any and all observations that contained a municipality code of 0.
-Additionally, we chose to exclude any real estate valued below 100 DKK, while these listings existed on Boliga's website, they were all listings, where the seller wanted  to sell to the highest bidder.
+Additionally, we chose to exclude any real estate valued below DKK.
+100, while these listings existed on Boliga's website, they were all listings, where the seller wanted  to sell to the highest bidder.
 We excluded these listings on the basis that they were unrealistically priced compared to the property's real market value.\newline
-Boliga subdivides its listings into ten real-estate types.
+Boliga subdivides its listings into ten real estate types.
 We chose to exclude the typification "other", as there were only 17 houses listed in the category - too few for training our machine learning model.
 Furthermore, we also removed any listing without coordinates as these were vital for the scraping process on hvorlangerder.dk.\newline
-We dropped all observations with an unreasonably high "liggetid", as we saw these instances to not  represent reasonable pricing or demand.
+We dropped all observations with an unreasonably high days-for-sale, as we saw these instances to not  represent reasonable pricing or demand.
 We have thus set an arbitrary limit of 3 years (1,095 days), and omitted any observations that has been on the market for longer than that.
 This results in the omission of approximately 5\% of our dataset.
-The highest mean "liggetid" on a municipal level was roughly 600 days, so as not to discriminate against the observations from the municipalities with a longer average 'sales time' we set the cut-off somewhat higher than the highest mean.
+The highest mean "days-for-sale" on a municipal level was roughly 600 days, so as not to discriminate against the observations from the municipalities with a longer average 'sales time' we set the cut-off somewhat higher than the highest mean.
 Another option was to set the limit according to each municipality's mean, a solution that was a bit more time consuming, and would have yielded approximately the same result, hence we opted not to do it.
@@
 \hline 
-Liggetid & 3,940\\
+days-for-sale & 3,940\\
 \hline 
@@
 \end{table}
-Since our efforts are aimed at predicting the valuation of a given real-estate, we want to penalize the size of the error the MSE-score is a better indicator for our model's performance as opposed to the mean absolute error (MAE).
+Since our efforts are aimed at predicting the valuation of a given real estate, we want to penalize the size of the error the MSE-score is a better indicator for our model's performance as opposed to the mean absolute error (MAE).
 Since MSE squares the error terms, it gives a relatively high weight to large errors, which is desirable for our current aim.
@@
 \newpage
-\section{Appendixs}
+\section{Appendix}
 \subsubsection{}

### 2019-08-29 Opsætningexam/DraftExam.tex
fd

@@
 Salganik mentions that informed consent for everything is an ideal, but in practice impossible to obtain and researchers should instead strive to follow an alternative rule, that he describes as: "some form of consent for most things." \footnote{Salganik, Matthew J.
-(2018) \textit{Bit by Bit - Social research in the digital age.} p.303} Adhering to this, more complex understanding of the practicality of informed consent, we chose to contact Boliga to inform them of our intent to scrape their website and use the data in an educational context\footnote{Shiab, Nael (2015) \textit{On the Ethics of Web Scraping and Data Journalism}.
+(2018) \textit{Bit by Bit - Social research in the digital age.} p.303} Adhering to this, more complex understanding of the practicality of informed consent, we chose to contact Boliga to inform them of our intent to scrape their website and use the data in an educational context\footnote{Shiab, Nael (2015) \textit{On the Ethics of Web Scraping and Data Journalism}}.
 Boliga responded positively to our inquiry, which we took as informed consent from a third party on behalf of the participating users in our study.\newline
@@
 The scraping process was conducted on Friday the $23^{rd}$ of August 2019.
-Global Investigative Journalism Network.}.
+Global Investigative Journalism Network.
 In order to scrape the data of interest we familiarized ourselves with the HTML-structure of Boliga.

### 2019-08-29 Opsætningexam/DraftExam.tex
p

@@
 The analysis the scraping logs was done according to Snorres demand on analyzing logs.
-\paragraph{Response Code}
+\paragraph{Response Code\newline}
 When parsing data from websites, the goal is to receive a response code ‘200’, expressing a successful request.
@@
 
-\paragraph{Error Codes}
+\paragraph{Error Codes\newline}
 \textcolor{red}{Figure XB} plots errors codes received throughout the duration of the scrapings.
@@
 
-\paragraph{Server Response Times}
+\paragraph{Server Response Times\newline}
 An indicator of poor data quality is varying the response times from the server being scraped.
@@
 
-\paragraph{Response Sizes}
+\paragraph{Response Sizes\newline}
 To validate the response quality, an assessment of the response size was performed.
@@
 
-\paragraph{Assesment of the Scraping Logs}
+\paragraph{Assesment of the Scraping Logs\newline}
 The individual analyses of the scraping logs showed minor suspicious traits which were assessed manually through the output or logs.
@@
 
-\paragraph{Critique of Logs Using Scraping Class}
+\paragraph{Critique of Logs Using Scraping Class\newline}
 In the process of analyzing the scraping logs, minor flaws from the scraping library named ‘scraping\_class’ were detected.

### 2019-08-29 Opsætningexam/DraftExam.tex
ny

@@
 The maximum square meter price being approximately 8 times higher in the municipality of Gentofte, than Lolland, the municipality with the lowest average square meter price valuations.
-A tendency visualized in the figure, is that average square meter price valuations are higher in highly populated municipalities and in suburban areas surrounding Copenhagen.
+A tendency visualised in the figure, is that average square meter price valuations are higher in highly populated municipalities and in suburban areas surrounding Copenhagen.
 \newline
@@
 85 million.
-This research paper intends to analyze real estate price valuations and which geo- and sociodemographic criteria affect valuations, using machine learning models.
+This research paper intends to analyse real estate price valuations and which geo- and sociodemographic criteria affect valuations, using machine learning models.
 Our research question is as follows:
@@
 It requires a rigorous research design and clear theoretical assumptions, in order to yield scientifically accurate estimates.
-Indeed the social sciences greatest contribution to big data research, comes from the organized framework provided by rigorously tested theory\footnote{Einav, Liran and Jonathan Levin (2014) \textit{Economics in the age of big data}}.\newline
-The contribution from the social sciences to machine learning help create new methods that will be able to utilize the strengths of machine learning to help solve causal inference problems within the framework of a well defined theory\footnote{Athey, Susan (2018) 'The Impact of Machine Learning on Economics' in Ajay Agrawal et al.
+Indeed the social sciences greatest contribution to big data research, comes from the organised framework provided by rigorously tested theory\footnote{Einav, Liran and Jonathan Levin (2014) \textit{Economics in the age of big data}}.\newline
+The contribution from the social sciences to machine learning help create new methods that will be able to utilise the strengths of machine learning to help solve causal inference problems within the framework of a well defined theory\footnote{Athey, Susan (2018) 'The Impact of Machine Learning on Economics' in Ajay Agrawal et al.
 (eds) \textit{The Economics of Artificial Intelligence: An Agenda}}.
@@
 \textit{Ethics in Social Sciences and the Humanities}} guidelines and principles for ethical conduct in social data science, the potential harm to users of Boliga's web-page were carefully considered.
-As a step to prevent the mosaic effect and in an effort to anonymize the scraped data only aggregated data will be presented in this paper, so that no single observation can be identified from the analysed data.\newline
+As a step to prevent the mosaic effect and in an effort to anonymise the scraped data only aggregated data will be presented in this paper, so that no single observation can be identified from the analysed data.\newline
 No informed consent has been obtained from the users of the site, prompting us to consider the consequences of the lack thereof, as informed consent is paramount to the proper, ethical conduct in social science.
@@
 Global Investigative Journalism Network.
-In order to scrape the data of interest we familiarized ourselves with the HTML-structure of Boliga.
+In order to scrape the data of interest we familiarised ourselves with the HTML-structure of Boliga.
 On the basis of these insights we constructed a code, which was able to scrape every page, containing information pertaining the currently listed real estates on Boliga.
@@
 \end{tabular}
+
+\paragraph{DAWA\newline}
+
 \paragraph{Socioeconomic Factors\newline}
@@
 Three datasets were obtained through web scraping from Boliga.dk, Hvorlangterder.dk and DAWA.dk.
-This section will analyze the logs created in the scraping process, with the intention of providing evidence of the data quality.
+This section will analyse the logs created in the scraping process, with the intention of providing evidence of the data quality.
 The analysis the scraping logs was done according to Snorres demand on analyzing logs.
@@
 Responses times differing from usual within the logs, have been assessed to be caused by two either a slow server time or connection, or due to larger quantities of data being requested.
-To validate the quality of data, manual control of the returned result and the webpage result was performed, without the notice of significant corruptions in the data to be utilized in the research.
+To validate the quality of data, manual control of the returned result and the webpage result was performed, without the notice of significant corruptions in the data to be utilised in the research.
 \begin{figure}[H]
@@
 The two requests were made to two pages, where few properties contain nested dictionary attributes approximately 59 times larger than the average size of dictionaries within the ‘image’ data column.
-These dictionaries are image descriptions, and are not utilized within this research.
+These dictionaries are image descriptions, and are not utilised within this research.
 These larger responses were deemed as not polluting the results of the research.
@@
 \subsection{Descriptive Statistics}
-In this section, we will examine the more apparent patterns of our collected data. This is done to familiarize ourselves with the data, before we commence on the analysis.
+In this section, we will examine the more apparent patterns of our collected data. This is done to familiarise ourselves with the data, before we commence on the analysis.
 \subsubsection{Key Statistics}
@@
 p.73}.
-In both cases, the model will generalize poorly.
+In both cases, the model will generalise poorly.
 A key step in defining a decent model in machine learning is to find an optimal bias-variance-balance, by tuning the complexity of one’s model.
@@
 \subsubsection{Lasso}
-Regularization by Lasso, will penalize complexity of the model by the sum of the absolute value of the coefficients.
+Regularization by Lasso, will penalise complexity of the model by the sum of the absolute value of the coefficients.
 This penalty will make the model less complex and more appropriate for prediction.
@@
 332}
-\newline Lasso minimizes: $$L_{Lasso}(\hat{\beta}) = \left(\sum_{i=1}^{n} (y_i-\hat{y_i}(\beta))^2+\lambda\sum_{j=1}^{p}|\hat{\beta_j}|\right) \qquad s.t \quad \lambda \geq 0 $$
+\newline Lasso minimises: $$L_{Lasso}(\hat{\beta}) = \left(\sum_{i=1}^{n} (y_i-\hat{y_i}(\beta))^2+\lambda\sum_{j=1}^{p}|\hat{\beta_j}|\right) \qquad s.t \quad \lambda \geq 0 $$
 Another convenient attribute of the Lasso penalty is that some estimates are set equal to zero and thereby produce sparse models\footnote{Hal R.
@@
 \subsubsection{Ridge}
-The ridge model penalizes with the sum of squared coefficients. Opposed to Lasso, Ridge do not force features to be omitted. Instead Ridge penalizes the magnitude of the coefficients. Ridge minimizes:
+The ridge model penalises with the sum of squared coefficients. Opposed to Lasso, Ridge do not force features to be omitted. Instead Ridge penalises the magnitude of the coefficients. Ridge minimises:
 $$L_{Ridge}(\hat{\beta}) = \left(\sum_{i=1}^{n} (y_i-\hat{y_i}(\beta))^2+\lambda\sum_{j=1}^{p}\hat{\beta_j}^2\right) \qquad s.t \quad \lambda \geq 0 $$
@@
 \subsubsection{Elastic-net}
-The Elastic net combines the penalizing terms of Lasso and Ridge, with $\alpha$ defining the relative weights between Lasso and Ridge. Elastic net minimizes the function: 
+The Elastic net combines the penalizing terms of Lasso and Ridge, with $\alpha$ defining the relative weights between Lasso and Ridge. Elastic net minimises the function: 
 $$L_{elasticnet}(\hat{\beta}) = \frac{\sum_{i=1}^{n}\left(y_i-\hat{y_i}(\beta)\right)^2}{2n} + \lambda\left(\frac{1-\alpha}{2}\sum_{j=1}^{p}\hat{\beta_j}^2+\alpha\sum_{j=1}^{p}|\hat{\beta_j}|\right)$$
@@
 \subsection{Optimizing the Hyperparameter}
-To minimize the mean squared errors of our Lasso and Ridge regression we performed k-fold cross validation to optimize the hyperparameter $\lambda$. 
+To minimise the mean squared errors of our Lasso and Ridge regression we performed k-fold cross validation to optimise the hyperparameter $\lambda$. 
 We split the data into a test set and a development set, consisting of respectively 20\% and 80\% of the total observations.
@@
 \subsection{Predictive Performance}
-With the hyperparameters optimized, final model performance can be evaluated.
+With the hyperparameters optimised, final model performance can be evaluated.
 Once more a cross-validation is carried out, which return the average performance-error of each model.
@@
 \end{table}
-Since our efforts are aimed at predicting the valuation of a given real estate, we want to penalize the size of the error the MSE-score is a better indicator for our model's performance as opposed to the mean absolute error (MAE).
+Since our efforts are aimed at predicting the valuation of a given real estate, we want to penalise the size of the error the MSE-score is a better indicator for our model's performance as opposed to the mean absolute error (MAE).
 Since MSE squares the error terms, it gives a relatively high weight to large errors, which is desirable for our current aim.
 
-From table XX it is evident that the machine learning model with two degrees of polynomial features performs best with a regularization by LASSO as it has the lowest measures of difference between the predicted price and the true price, with a MSE of 5.91E+10, whilst the model with 3 degrees of polynomial features regularized by ridge regression performs even better with a MSE 5.57E+10.
+From table XX it is evident that the machine learning model with two degrees of polynomial features performs best with a regularization by LASSO as it has the lowest measures of difference between the predicted price and the true price, with a MSE of 5.91E+10, whilst the model with 3 degrees of polynomial features regularised by ridge regression performs even better with a MSE 5.57E+10.
 Therefore, we chose this model as the final model from which we will conduct the rest of the analysis with.
@@
 
-We examine the validation curve, figure \textcolor{red}{XX}, of the model to examine whether we have found a good bias-variance-balance with our optimized hyperparameter.
+We examine the validation curve, figure \textcolor{red}{XX}, of the model to examine whether we have found a good bias-variance-balance with our optimised hyperparameter.
 We plot the average train and cross-validation performance for different values of $\lambda$:
@@
 \paragraph{Validation Curve}
-We examine the validation curve of the model to see whether we have found a good bias-variance-trade-off with our optimized hyperparameter.
+We examine the validation curve of the model to see whether we have found a good bias-variance-trade-off with our optimised hyperparameter.
 We plot the average train and cross-validation performance for different values of $\lambda$:
@@
 \end{figure}
-The dotted line approximately represents the optimized value of lambda from our previously conducted k-fold cross-validation.
+The dotted line approximately represents the optimised value of lambda from our previously conducted k-fold cross-validation.
 
@@
 Nonetheless, it is apparent that our model performs better on the training data, which indicates that it retains a degree of overfitting.
-For the abovementioned reasons, it would not be meaningful to minimize this performance gab by adjusting the hyperparameter.
+For the abovementioned reasons, it would not be meaningful to minimise this performance gab by adjusting the hyperparameter.
 Other options for decreasing the variance of the model, could be to include more training data, but as illustrated by the learning curve, this would not seem effect the variance.
@@
 In conclusion, it would seem that we have found the hyperparameter which yields the optimal bias-variance-trade-off.
-We can thus conclude that we have optimized our model under the given circumstances.
+We can thus conclude that we have optimised our model under the given circumstances.
 
@@
 We trained both a Lasso- and a Ridge regression model and compared their performances with the performance of a standard linear regression.
-Though k-fold cross-validation, we estimated the optimized hyperparameters for both regularization models.
+Though k-fold cross-validation, we estimated the optimised hyperparameters for both regularization models.
 We found that the Ridge regression performed best on average, with the performance measure being the smallest mean square error of the model.
@@
 Matthew Salganik offer four principles deduced from the Belmont and Menlo Report that should guide the ethical deliberations of the researcher: 1) the respect for persons, that is individuals should be treated as autonomous and if circumstances require it individuals should be entitled to additional protections.
-2) Beneficence stresses the importance of doing no harm and to maximize the possible benefits and minimizing any potential harms.
+2) Beneficence stresses the importance of doing no harm and to maximise the possible benefits and minimizing any potential harms.
 3) The principle of justice touches upon the importance of the distribution of burdens and benefits of the social scientist's research.
@@
 To this end, the European Parliament introduced the General Data Protection Regulation (GDPR).
-With its seven overarching principles the GDPR seeks to formalize the procedures involved in the data processing and storing of sensitive and private information (CDRC\footnote{Consumer Data Research Center, UK  [CDRC] (2018) \textit{The General Data Protection Regulation \& Social Science Research} [Online]:}).
+With its seven overarching principles the GDPR seeks to formalise the procedures involved in the data processing and storing of sensitive and private information (CDRC\footnote{Consumer Data Research Center, UK  [CDRC] (2018) \textit{The General Data Protection Regulation \& Social Science Research} [Online]:}).
 These principles include and expand upon the principles found in the Belmont and Menlo Report.
 The most important consideration, however, must be that even a dataset comprising tens of thousands of observations involve human beings who must be protected from adverse side-effects of the social research.
-There is considerable evidence that point to the fact that even in anonymized data sets it can be possible to backtrack an individual's identity.
+There is considerable evidence that point to the fact that even in anonymised data sets it can be possible to backtrack an individual's identity.
 A researcher must therefore be mindful of the mosaic effect if the dataset combines large amount of data from various sources (European Commission 2018).

### 2019-08-29 Opsætningexam/DraftExam.tex
d

@@
 \usepackage{caption}
+\usepackage{footnote}
+\makesavenoteenv{tabular}
+\usepackage{tablefootnote}
 \lhead{}
@@
 The valuations included in the research are collected from one of Denmarks largest online real estate websites named Boliga.dk.
-The Boliga data contains approximately 66,000 active offerings with valuations ranging from DKK.
-15,000 to DKK.
-85 million.
+The Boliga data contains approximately 66,000 active offerings with valuations ranging from DKK 15,000 to DKK 85 million.
 This research paper intends to analyse real estate price valuations and which geo- and sociodemographic criteria affect valuations, using machine learning models.
@@
 \href{https://www.dst.dk/da/Statistik/emner/befolkning-og-valg}{Danmarks Statistik} respectively.
-The factors include income, reported crime, level of highest completed education etc.
-These are transformed into ratios, by taking the total population in a given municipality into account.
+The factors include income, reported crime, level of highest completed education, etc.
+These were transformed into ratios, by taking the total population in a given municipality into account.
  \vspace*{5px} \newline
@@
 Three datasets were obtained through web scraping from Boliga.dk, Hvorlangterder.dk and DAWA.dk.
-This section will analyse the logs created in the scraping process, with the intention of providing evidence of the data quality.
-The analysis the scraping logs was done according to Snorres demand on analyzing logs.
+This section will analyse the logs created in the scraping process, with the intention of ensuring the data quality.
 \paragraph{Response Code\newline}
@@
 \textcolor{red}{Fig XA} displays response codes for the duration of the web scrapings.
-Every single request received a response code 200.
-Further evaluation of the response codes was not necessary.
+Every request received a response code 200, making further evaluation of the response codes redundant.
 \begin{figure}[H]
@@
 \paragraph{Error Codes\newline}
-\textcolor{red}{Figure XB} plots errors codes received throughout the duration of the scrapings.
+\textcolor{red}{Figure XB} plots error codes received throughout the duration of the scrapings.
 Boliga and DAWA received no errors, while hvorlangterder received a total of 80 errors.
-The error code returns the same response in all 80 cases: \small{\textbf{('Connection aborted.', RemoteDisconnected('Remote end closed connection without response'))}}
+The error code returned the same response in all 80 cases: \small{\textbf{('Connection aborted.', RemoteDisconnected('Remote end closed connection without response'))}}
+\normalsize
 \begin{figure}[H]
@@
 To understand the errors, a closer manual analysis of the log was performed on requests receiving errors.
-The errors occur in random intervals and are subsequently followed by another request to an identical URL.
+The errors occurred in random intervals and were subsequently followed by another request to an identical URL.
 Therefore, we assessed that these errors were due to connection problems or server traffic.
-Since the errors were corrected by a following request, we assessed it would not affect the research.
+Since the errors were corrected by a following request, it should not affect the research.
 
 \paragraph{Server Response Times\newline}
-An indicator of poor data quality is varying the response times from the server being scraped.
+An indicator of poor data quality is varying response times from the server being scraped.
 \textcolor{red}{Figure XC} plots changes in response times for the duration of the web scrapings.
-The 3 data sources all resulted in few variations of response times.
-Responses times differing from usual within the logs, have been assessed to be caused by two either a slow server time or connection, or due to larger quantities of data being requested.
-To validate the quality of data, manual control of the returned result and the webpage result was performed, without the notice of significant corruptions in the data to be utilised in the research.
+The three data sources all resulted in few variations of response time.
+Unusual response times has been assessed within the logs, to be caused by either a slow server connection, or due to larger quantities of data being requested.
+To validate the quality of data, manual control of the returned results and the webpage results was performed, without notice of significant corruptions in the data utilised in the research.
 \begin{figure}[H]
@@
 \textcolor{red}{Figure XD} plots response sizes throughout the duration of the web scrapings.
-Boliga contains a single noticeable large response size within short time, while hvorlangterder response sizes vary throughout the scrape.
-The DAWA scrape resulted in indifferent response sizes, and therefore needed no further investigation.
+Boliga contains a single noticeably large response size within short time, while hvorlangterder response sizes vary throughout the scrape.
+The DAWA scrape resulted in consistent response sizes, and therefore needed no further investigation.
 \begin{figure}[H]
@@
 \end{figure}
-With a further analysis the distribution of sample sizes in figure XE, the Boliga and DAWA response sizes seem to be close to normally distributed, except for two single cases of large sample sizes in the Boliga log.
+Examining the distribution of sample sizes in figure XE, the Boliga and DAWA response sizes seem to be close to normally distributed, except for two single cases of large sample sizes in the Boliga log.
 By manually assessing the returned output of the Boliga scrape, these two requests were found to return a larger amount of data than usual.
-The two requests were made to two pages, where few properties contain nested dictionary attributes approximately 59 times larger than the average size of dictionaries within the ‘image’ data column.
-These dictionaries are image descriptions, and are not utilised within this research.
+The requests were made to two pages, where a few properties contained nested dictionary attributes approximately 59 times larger than the average size of dictionaries within the ‘image’ data column.
+These dictionaries were image descriptions, and were not utilised within this research.
 These larger responses were deemed as not polluting the results of the research.
@@
 \end{figure}
-\textcolor{red}{Figure XE depicts that the hvorlangerder response sizes are a bit left scewed, while Figure XD} shows that the distribution of large sizes happens during the middle of the scrape.
+\textcolor{red}{Figure XE depicts that the hvorlangerder response sizes were a bit left skewed, while Figure XD} shows that the distribution of large sizes happens during the middle of the scrape.
 With a further glimpse into the log, we observed two things.
-First, all response sizes of 0 are related to the errors, displayed in figure XB.
+Firstly, all response sizes of 0 are related to the errors, displayed in figure XB.
 The variance of responses could be explained by the type of data retrieved from the scrape.
@@
 When extracting the value from every single key of the dictionary output, no errors or missing values were found.
-Further control of samples of large and small sizes were performed without discovering flaws.
-The response sizes from hvorlangterder are found to vary by nature, which may explain the difference.
+Further control of samples of large and small sizes was performed without discovering flaws.
+The response sizes from hvorlangterder are found to vary in nature, which may explain the difference.
 
-\paragraph{Assesment of the Scraping Logs\newline}
-The individual analyses of the scraping logs showed minor suspicious traits which were assessed manually through the output or logs.
-The most concerning analysis being difference in response sizes and response times from the hvorlangterder scrape.
+\paragraph{Assessment of the Scraping Logs\newline}
+The individual analysis of the scraping logs showed minor suspicious traits which were assessed manually through the output or logs.
+The most noticeable analysis being differences in response sizes and response times from the hvorlangterder scrape.
 This scrape consumed large amounts of time and computing power, as every single observation from the Boliga data, had to be input for requesting a response.
-In an extensive research, these problems could be handled by gaining direct access to the website instead of scraping and would benefit by running on a server with greater computing power.
+In an extensive research, these problems could be handled by gaining direct access to the website instead of scraping and would benefit from running on a server with greater computing power.
 The results of the data collection were evaluated to be satisfying, and not corrupting the results of our research, as fairly reasonable explanations for noticeable dissimilarities within the logs were found.
@@
 \paragraph{Critique of Logs Using Scraping Class\newline}
-In the process of analyzing the scraping logs, minor flaws from the scraping library named ‘scraping\_class’ were detected.
+In the process of analysing the scraping logs, minor flaws from the scraping library named ‘scraping\_class’ were detected.
 The returned columns ‘t’ and ‘delta\_t’ contained non-generic formats of epoch time.
@@
 \subsection{Merging Data}
-Pandas objects can be combined in different ways according to the nature of features in the dataset.
+Pandas objects can be combined in different ways according to the nature of the features in the dataset.
 Relational database style operations are based on linking keys together, thereby maintaining the relationship between the combined datasets\footnote{McKinney, W.
@@
 p.
-231 }
+231 }.
 
@@
 
-The Boliga dataset acts as a master dataset and was joined or merged upon throughout the process, and acts as the “left” of all operations.
-The Longitude and Latitude features serve as specific coordinates for valued properties but are in few cases repetitive regarding different apartments from the same complex.
-The municipality code was used for translation purposes between the master dataset and other datasets.
+The Boliga dataset acted as a master dataset and was joined or merged upon throughout the process, and acted as the \textit{left} of all operations.
+The Longitude and Latitude features served as specific coordinates for valued properties but were in few cases repetitive regarding different apartments from the same complex.
+The municipality code was used for translational purposes between the master dataset and other datasets.
 
@@
 The DAWA dataset was scraped with an input of a distinct municipality code from the master dataset, returning a dataframe of municipality names for each code.
-This dataframe was merged onto the Boliga dataframe as a many-to-one merge with municipality code as the merge keys.
+This dataframe was merged onto the Boliga dataframe using a many-to-one merge with municipality codes as the merge keys.
 The scraped municipality names from DAWA was used as the merge key for all further merges of municipal data.
@@
 The police statistics webpage does not specify whether different types of reported crimes can relate to a single case, but we assessed that the number of crimes reported provides a meaningful feature either way.
-The dataset containing total reported crimes per municipality, was merged with the master dataset in the same fashion as previous municipality-based features.
+The dataset containing total reported crimes per municipality was merged with the master dataset in the same fashion as previous municipality-based features.
 
@@
 The scraping function, which was created for returning location-based features, created a column for the row specific values.
-Therefore, a merge operation was not necessary, but could alternatively have been managed with a one-to-one inner-merge id.
+Therefore, a merge operation was not necessary, but could alternatively have been managed with a one-to-one inner-merge on id.
 As few coordinates regarding apartment properties are repetitive, these are not suitable for merging upon.
@@
 \subsubsection{Initial clean-up}
-The initial clean-up sorted out rows that contained an illogical value.
-Here we focused our efforts on the removing any and all observations that contained a municipality code of 0.
-Additionally, we chose to exclude any real estate valued below DKK.
-100, while these listings existed on Boliga's website, they were all listings, where the seller wanted  to sell to the highest bidder.
+The initial clean-up filter out rows that contained illogical values.
+Here we focused our efforts on removing any and all observations that contained a municipality code of zero.
+Additionally, we chose to exclude any real estate valued below DKK 100, these listings existed on Boliga's website, but were all auction listings.
 We excluded these listings on the basis that they were unrealistically priced compared to the property's real market value.\newline
@@
 We chose to exclude the typification "other", as there were only 17 houses listed in the category - too few for training our machine learning model.
-Furthermore, we also removed any listing without coordinates as these were vital for the scraping process on hvorlangerder.dk.\newline
+Furthermore, we also removed any listing without coordinates as these were vital for the scraping process of hvorlangterder.dk.\newline
 We dropped all observations with an unreasonably high days-for-sale, as we saw these instances to not  represent reasonable pricing or demand.
@@
 This results in the omission of approximately 5\% of our dataset.
-The highest mean "days-for-sale" on a municipal level was roughly 600 days, so as not to discriminate against the observations from the municipalities with a longer average 'sales time' we set the cut-off somewhat higher than the highest mean.
-Another option was to set the limit according to each municipality's mean, a solution that was a bit more time consuming, and would have yielded approximately the same result, hence we opted not to do it.
+The highest mean "days-for-sale" on a municipal level was roughly 600 days, so to avoid discrimination against the observations from the municipalities with a longer average days-for-sale we set the cut-off somewhat higher than the highest mean.
+Another option was to set the limit according to each municipality's mean, a solution that was a bit more time consuming.
 In figure XX the number of rows dropped at each step of the cleaning can be perused.
+\begin{table}
 \begin{center}
+\caption{Filtered Rows\label{time}}
 \begin{tabular}{|l|c|}
 \hline 
-Feature & \emph{n} \\
+\textbf{Feature} & \textbf{\emph{n}} \\
 \hline 
@@
 \hline 
-Total\footnote{"The total is the count of how many rows were dropped. Some rows were missing multiple features.} & 4,332\\
+Total\tablefootnote{The total is the count of how many rows were dropped. Some rows were missing multiple features} & 4,332\\
 \hline
 \end{tabular}
+
 \end{center}
-
+\end{table}
 \subsubsection{Ejerlejlighed's lot size}
@@
 \subsubsection{Elastic-net}
-The Elastic net combines the penalizing terms of Lasso and Ridge, with $\alpha$ defining the relative weights between Lasso and Ridge. Elastic net minimises the function: 
+The Elastic net combines the penalising terms of Lasso and Ridge, with $\alpha$ defining the relative weights between Lasso and Ridge. Elastic net minimises the function: 
 $$L_{elasticnet}(\hat{\beta}) = \frac{\sum_{i=1}^{n}\left(y_i-\hat{y_i}(\beta)\right)^2}{2n} + \lambda\left(\frac{1-\alpha}{2}\sum_{j=1}^{p}\hat{\beta_j}^2+\alpha\sum_{j=1}^{p}|\hat{\beta_j}|\right)$$
@@
 
-\subsection{Optimizing the Hyperparameter}
+\subsection{Optimising the Hyperparameter}
 To minimise the mean squared errors of our Lasso and Ridge regression we performed k-fold cross validation to optimise the hyperparameter $\lambda$. 
@@
 Matthew Salganik offer four principles deduced from the Belmont and Menlo Report that should guide the ethical deliberations of the researcher: 1) the respect for persons, that is individuals should be treated as autonomous and if circumstances require it individuals should be entitled to additional protections.
-2) Beneficence stresses the importance of doing no harm and to maximise the possible benefits and minimizing any potential harms.
+2) Beneficence stresses the importance of doing no harm and to maximise the possible benefits and minimising any potential harms.
 3) The principle of justice touches upon the importance of the distribution of burdens and benefits of the social scientist's research.

### 2019-08-29 Opsætningexam/DraftExam.tex

@@
 Within social data science there exist widely differing definitions of big data and machine learning. This section seeks to clarify the use of these terms within the scope of this paper.
-\paragraph{On Big Data \& Machine Learning\newline}
+\subsection{On Big Data \& Machine Learning}
 Historically, big data has been a term reserved for data that was unable to be processed by extant software.
@@
 
+\subsection{An Ethical Overview}
+The ethical principles of social research are anchored in the fundamental human rights, which are broadly formulated in the UN Declaration of Human Rights.
+Additional policies and declarations that codify principles of research ethics and the ethical treatment of research participants include the Nuremberg Code, the Helsinki Declaration, the Belmont Report, and the Menlo Report\footnote{Salganik, Matthew J.
+(2018) \textit{Bit by Bit Bit - Social research in the digital age.}}\, \footnote{European Commission (2018).
+\textit{Ethics in Social Sciences and the Humanities}}.
+These codes and addendums originate mostly in the biomedical field, though they encompass the central principles applied to all human research, which have led some academics to call for a Hippocratic oath for data scientists to safeguard against powerful new technologies under development in laboratories and tech firms\footnote{Rotblat, Joseph (1999) \textit{A Hippocratic Oath for Scientists}}\, \footnote{Sample, Ian (2019, Fri 16 Aug 2019) \textit{and tech specialists need Hippocratic oath, says academic.}}.
+This discussion is nothing new however, as a tentative reformulation of the Hippocratic oath was introduced by Karl Popper\footnote{Popper, Karl (1969) \textit{The Moral Responsibility of the Scientist}}, wherein he stressed the importance of professional responsibility, a critical mind, and an overriding loyalty towards the betterment of mankind.\newline
+Matthew Salganik offer four principles deduced from the Belmont and Menlo Report that should guide the ethical deliberations of the researcher: 1) the respect for persons, that is individuals should be treated as autonomous and if circumstances require it individuals should be entitled to additional protections.
+2) Beneficence stresses the importance of doing no harm and to maximise the possible benefits and minimising any potential harms.
+3) The principle of justice touches upon the importance of the distribution of burdens and benefits of the social scientist's research.
+This principle stress that is should not be a single stratum of society that bears the costs of the research while another stratum benefits.
+4) The fourth and final principle is the respect for law and public interest, according to Salganik, the principle consists of two distinct elements, that is compliance to relevant laws and legal contracts and transparency-based accountability.
+It is worth noting that Popper’s tentative Hippocratic oath mirrors the first three principles put forth by Salganik, stressing the importance of the ethical conduct of the researcher.\newline
+The need for rigid ethical standards within computational social science was made apparent by the Cambridge Analytica Scandal that broke on the 17th of March 2018.
+Where Steve Bannon could reveal that between 2013 and 2015 Cambridge Analytica had exploited a loophole in Facebook’s API which allowed the company to harvest profile data from 87 million Facebook users, without the user’s permission and use the harvested data to construct a massive targeted marketing database based on the user’s likes and interests\footnote{Vox.com (2018) \textit{The Cambridge Analytica Facebook scandal} [Online]}.
+Other examples of misuse of data acquired from Facebook include the Harvard-run experiment, where students' data was used to create new knowledge about how social networks form and how these networks and their actors' behavior co-evolve, and the emotional contagion experiment from 2012, where approximately 700,000 users were involved in a research experiment to examine the extent to which a person's emotions are affected by the emotions of the people they interact with (Salganik.
+2018).\newline
+From this it should be evident that clear ethical guidelines are required in order to protect the user's privacy from tech-savvy companies.
+To this end, the European Parliament introduced the General Data Protection Regulation (GDPR).
+With its seven overarching principles the GDPR seeks to formalise the procedures involved in the data processing and storing of sensitive and private information (CDRC\footnote{Consumer Data Research Center, UK  [CDRC] (2018) \textit{The General Data Protection Regulation \& Social Science Research} [Online]:}).
+These principles include and expand upon the principles found in the Belmont and Menlo Report.
+The most important consideration, however, must be that even a dataset comprising tens of thousands of observations involve human beings who must be protected from adverse side-effects of the social research.
+There is considerable evidence that point to the fact that even in anonymised data sets it can be possible to backtrack an individual's identity.
+A researcher must therefore be mindful of the mosaic effect if the dataset combines large amount of data from various sources (European Commission 2018).
+
 \section{Data Description \& Ethics}
@@
 Drawing upon the European Comissions\footnote{European Commission (2018).
-\textit{Ethics in Social Sciences and the Humanities}} guidelines and principles for ethical conduct in social data science, the potential harm to users of Boliga's web-page were carefully considered.
+\textit{Ethics in Social Sciences and the Humanities}} guidelines and principles for ethical conduct in social data science, the potential harm to users of Boliga's website were carefully considered.
 As a step to prevent the mosaic effect and in an effort to anonymise the scraped data only aggregated data will be presented in this paper, so that no single observation can be identified from the analysed data.\newline
@@
 When parsing data from websites, the goal is to receive a response code ‘200’, expressing a successful request.
-\textcolor{red}{Fig XA} displays response codes for the duration of the web scrapings.
+Figure 2 displays response codes for the duration of the web scrapings.
 Every request received a response code 200, making further evaluation of the response codes redundant.
@@
 \paragraph{Error Codes\newline}
-\textcolor{red}{Figure XB} plots error codes received throughout the duration of the scrapings.
+Figure plots error codes received throughout the duration of the scrapings.
 Boliga and DAWA received no errors, while hvorlangterder received a total of 80 errors.
@@
 Unusual response times has been assessed within the logs, to be caused by either a slow server connection, or due to larger quantities of data being requested.
-To validate the quality of data, manual control of the returned results and the webpage results was performed, without notice of significant corruptions in the data utilised in the research.
+To validate the quality of data, manual control of the returned results and the website results was performed, without notice of significant corruptions in the data utilised in the research.
 \begin{figure}[H]
@@
 Afterwards, the values were added to each other, providing a total of reported crimes within each municipality.
-The police statistics webpage does not specify whether different types of reported crimes can relate to a single case, but we assessed that the number of crimes reported provides a meaningful feature either way.
+The police statistics website does not specify whether different types of reported crimes can relate to a single case, but we assessed that the number of crimes reported provides a meaningful feature either way.
 The dataset containing total reported crimes per municipality was merged with the master dataset in the same fashion as previous municipality-based features.
@@
 However, big data is often dirty and requires tidying before it can be used in any meaningful statistical context (Salganik 2018).
+The data cleaning process consists of removing duplicate values, handling missing data and manipulating strings\footnote{McKinney, W.
+(2018).
+'Data Wrangling: Join, Combine and Reshape'.
+In W.
+McKinney, \textit{Python for Data Analysis} p.
+191}.
+The pandas library contains functions to handle these data cleaning methods and was used throughout the process.
 In the following sections we describe our data cleaning efforts.
 \subsubsection{Initial clean-up}
-The initial clean-up filter out rows that contained illogical values.
+The initial clean-up filtered out rows that contained illogical values.
 Here we focused our efforts on removing any and all observations that contained a municipality code of zero.
@@
 \subsubsection{Ejerlejlighed's lot size}
-Inspecting our data we found that from 8,028 apartments 1,176 of these had a lot size.
+Inspecting our data we found that out of 8,028 apartments, 1,176 had a lot size.
 These listings included the apartment complex' common area, whereas the rest did not.
@@
 
-\subsubsection{Final touch-ups}
+\subsubsection{Final touches}
 After merging the housing info with the demographic data and the distances from hvorlangterder.dk, we removed a single duplicate and deleted all columns not relevant for our analysis.
-After the clean-up of the data we were left with a dataset consisting of 61,618  observations and 37 features and 1 target variable.
+After the clean-up of the data we were left with a dataset consisting of 61,618  observations, 37 features and 1 target variable.
+The features are of both categorical and continuous measures
 
 \subsection{Descriptive Statistics}
-In this section, we will examine the more apparent patterns of our collected data. This is done to familiarise ourselves with the data, before we commence on the analysis.
+In this section, we will examine the more apparent patterns of our collected data. This is done to familiarise ourselves with the data, before we commence the analysis.
 \subsubsection{Key Statistics}
-Some key statistical characteristic is presented in table 1:
+Some key statistical characteristics are presented in table 1:
 \begin{table}[H]
@@
    & Price & \, Rooms \ & \ $m^2$ \ & Average Municipal Income \\ \hline
-   Mean & 2,312,798.00 & \ 4.21 \  & \ 127.82 \ & 312,957.03 \\ \hline
-   Std & 2,351,127.00 & 2.12 & 75.67 & 46,095.34 \\ \hline
-   Min & 15,000.00 & 0 & 0 & 257,776 \\ \hline
-   25\% & 985,000.00 & 3 & 82 & 290,973 \\ \hline
-   50\% & 1,695,000.00 & 4 & 123 & 302,153 \\ \hline
-   75\% & 2,895,000.00 & 5 & 167 & 318,745 \\ \hline
-   Max & 85,000,000.00 & 50 & 2,390 & 583,331 \\ \hline
+   Mean & 2,312,798 & \ 4.21 \  & \ 127.82 \ & 312,957.03 \\ \hline
+   Std & 2,351,127 & 2.12 & 75.67 & 46,095.34 \\ \hline
+   Min & 15,000 & 0 & 0 & 257,776 \\ \hline
+   25\% & 985,000 & 3 & 82 & 290,973 \\ \hline
+   50\% & 1,695,000 & 4 & 123 & 302,153 \\ \hline
+   75\% & 2,895,000 & 5 & 167 & 318,745 \\ \hline
+   Max & 85,000,000 & 50 & 2,390 & 583,331 \\ \hline
 \end{tabular}
@@
 Initially, it should be addressed that some of the properties has 0 rooms and consists of 0 $m^2$.
-This is due to the fact that we have also included land on which housing has not yet been build.
+This is due to the fact that we have also included land on which housing has not yet been built.
 Examining the 25\%-quintile and the 75\%-quintile of the valuation prices, it becomes apparent that there are some substantial outliers both to the cheaper and to expensive side.
-This is also the case with rooms and $m^2$, where the highest values are sizably higher than the 75\%-quintile.
+
 It is worth noting, that there is quite a big difference between the lowest average municipal income of DKK 257,776.
@@
 \end{figure}
-The boxplot illustrates that the distribution is heavily left-skewed, where some municipalities has a sizably higher average income than the rest of the Danish municipalities.
+The boxplot illustrates that the distribution is heavily left-skewed, where some municipalities has a sizebly higher average income than the rest of the Danish municipalities.
 
@@
 \end{figure}
-It becomes apparent that the distribution is quite left-skewed and that there are a few municipalities who’s price per square meter is much higher than the rest of the municipalities.
+It becomes apparent that the distribution is quite right-skewed and that there are a few municipalities who’s price per square meter is much higher than the rest of the municipalities.
 Recalling the geoplot in figure 1, these expensive outliers are heavily concentrated around- and north of Copenhagen.
@@
 This is not especially surprising though, as it is a well-established trend that real estate prices in major cities are skyrocketing.
-Refraining from delving deeper into to a discussion of global urbanization, we retain the fact that property type does have an apparently significant effect on valuation pricings on average.
+Refraining from delving deeper into a discussion of global urbanization, we retain the fact that property type does have an apparently significant effect on average valuation.
 We will include the ‘type’ feature in our impending model training to control for this effect.
 
-\subsubsection{The Dataset}
-The merged dataset contains 61.618 observations and 37 features.   The features are of both categorical and continuous measures. Skal dette ikke bare op i Merging data?\newline
-
 \section{Methods}
-\subsection{Supervised Machine Learning}
-The objective by applying Machine Learning is to train a model that are able to make predictions in near future or never seen data.
-By feeding a model with labeled data as well as data samples, ML will define the algorithms that predicts the best\footnote{Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow}.
+The objective of applying Machine Learning(ML) is to train a model that is able to make predictions on never seen data.
+By feeding a model labelled data as well as data samples, ML will define the algorithms that performs best predictions\footnote{Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow}.
 p.
 3}.
-This project, implements a ML regression prediction model to predict pricing of housing listed in near future.
+This project implements a ML regression prediction model.
 \subsection{Fitting the model}
-The potential problems of underfitting and overfitting should be assessed when fitting a model.
+The potential problems of underfitting and overfitting should be assessed when fitting a model to data.
 A model is underfitted if it hardly captures the variation of the sample data.
@@
 This is done through \textit{regularization}.
-In this project three different types of regularization are applied; Lasso, Ridge and Elastic net.
+In this project two different types of regularization are applied; LASSO and RIDGE.
 
-\subsubsection{Lasso}
-Regularization by Lasso, will penalise complexity of the model by the sum of the absolute value of the coefficients.
+\subsubsection{LASSO}
+Regularization by LASSO, will penalise complexity of the model by the sum of the absolute value of the coefficients.
 This penalty will make the model less complex and more appropriate for prediction.
@@
 332}
-\newline Lasso minimises: $$L_{Lasso}(\hat{\beta}) = \left(\sum_{i=1}^{n} (y_i-\hat{y_i}(\beta))^2+\lambda\sum_{j=1}^{p}|\hat{\beta_j}|\right) \qquad s.t \quad \lambda \geq 0 $$
-Another convenient attribute of the Lasso penalty is that some estimates are set equal to zero and thereby produce sparse models\footnote{Hal R.
+\newline LASSO minimises: $$L_{LASSO}(\hat{\beta}) = \left(\sum_{i=1}^{n} (y_i-\hat{y_i}(\beta))^2+\lambda\sum_{j=1}^{p}|\hat{\beta_j}|\right) \qquad s.t \quad \lambda \geq 0 $$
+Another convenient attribute of the LASSO penalty is that some estimates are set equal to zero and thereby produce sparse models\footnote{Hal R.
 Varian.
@@
 p.19}.
-Lasso thereby performs the feature selection automatic.
-\subsubsection{Ridge}
-The ridge model penalises with the sum of squared coefficients. Opposed to Lasso, Ridge do not force features to be omitted. Instead Ridge penalises the magnitude of the coefficients. Ridge minimises:
-$$L_{Ridge}(\hat{\beta}) = \left(\sum_{i=1}^{n} (y_i-\hat{y_i}(\beta))^2+\lambda\sum_{j=1}^{p}\hat{\beta_j}^2\right) \qquad s.t \quad \lambda \geq 0 $$
-
-\subsubsection{Elastic-net}
-The Elastic net combines the penalising terms of Lasso and Ridge, with $\alpha$ defining the relative weights between Lasso and Ridge. Elastic net minimises the function: 
-$$L_{elasticnet}(\hat{\beta}) = \frac{\sum_{i=1}^{n}\left(y_i-\hat{y_i}(\beta)\right)^2}{2n} + \lambda\left(\frac{1-\alpha}{2}\sum_{j=1}^{p}\hat{\beta_j}^2+\alpha\sum_{j=1}^{p}|\hat{\beta_j}|\right)$$
-$$0 \leq \alpha \leq 1 \quad \wedge \quad \lambda \geq 0$$
+LASSO thereby performs feature selection automaticly.
+\subsubsection{RIDGE}
+Opposed to LASSO, RIDGE does not force features to be omitted. Instead RIDGE penalises the magnitude of the coefficients. RIDGE minimises:
+$$L_{RIDGE}(\hat{\beta}) = \left(\sum_{i=1}^{n} (y_i-\hat{y_i}(\beta))^2+\lambda\sum_{j=1}^{p}\hat{\beta_j}^2\right) \qquad s.t \quad \lambda \geq 0 $$
 
 \subsection{Selecting Features}
-In case regularization is not sufficient to cope with the overfitting of the model.
-Exclusion of features are a viable approach.
-With the number of scraped features in this project, taking into consideration.
-A recurring overfitting of the model would be likely.
-As a consequence a deliberate exclusion of features of interest will need to be carried out.
+In case regularization is not sufficient to cope with the overfitting of the model, exclusion of features is a viable approach.
+With the number of scraped features in this project taking into consideration, A recurring overfitting of the model would be likely.
+As a consequence a deliberate exclusion of features of interest are necessary.
 
 \subsection{Optimising the Hyperparameter}
-To minimise the mean squared errors of our Lasso and Ridge regression we performed k-fold cross validation to optimise the hyperparameter $\lambda$. 
+To minimise the mean squared errors of our LASSO and RIDGE regression we performed k-fold cross validation to optimise the hyperparameter $\lambda$. 
 We split the data into a test set and a development set, consisting of respectively 20\% and 80\% of the total observations.
@@
 Since we are working with a relatively large dataset we chose to split our data into 5 folds, and computed the average MSE for the 5 iterations.
-By using the k-fold cross-validation method we relieve ourselves of the concern that the estimation of our model’s performance is simply due to a lucky or unlucky split of the data.
+By using the k-fold cross-validation method we minimise the concern that the estimation of our model’s performance is simply due to a lucky or unlucky split of the data.
 \newline
-We performed this procedure for 12 different values of $\lambda$ spanning between \textcolor{red}{$10^(-4) and 10^4$}.
-We chose the value of $\lambda$ which yields the smallest average MSE over the 5 folds.
-We both calculated the optimal hyperparameters for a Ridge regression model, a Lasso regression model and an Elastic Net regression model.
-\textcolor{red}{The following table} shows the performance of the different models, when trained with their optimal hyperparameter and predicting the test data.
+We performed this procedure for different values of $\lambda$. We chose the value of $\lambda$ which yielded the smallest average MSE over the 5 folds. 
+We both calculated the optimal hyperparameters for a RIDGE regression model and a LASSO regression model.
 
@@
 With the hyperparameters optimised, final model performance can be evaluated.
-Once more a cross-validation is carried out, which return the average performance-error of each model.
+Once more a cross-validation is carried out, which returns the average performance error of each model.
 By retraining the models on the complete training set and testing on the independent test set, performance measures are obtained\footnote{Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow}.
 p.192}.
-\newline The performances of the models are simply measured by MSE, RMSE and MAE.
+\newline The performances of the models are simply measured by MSE and MAE.
 \newline
 $$ MSE = \frac{1}{n}\sum_{i=1}^{n}(y_i-\hat{y_i})^2$$
-
-$$ RMSE = \sqrt{\frac{1}{n}\sum_{i=1}^{n}(y_i-\hat{y_i})^2}$$
 $$ MAE = \frac{1}{n}\sum_{i=1}^{n}|y_i-\hat{y_i}|$$
@@
 A number of features are excluded before training the model.
-The exclusion was determined, quite simply, by investigation of the correlation between the complete set of features and the target variable.
-A list of the excluded features are found in appendix 11.0.1.
-The model used for ML are found in appendix 11.0.2.
+The exclusion is determined, quite simply, by investigation of the correlation between the complete set of features and the target variable.
+A list of the excluded features is found in appendix 11.0.1.
+The model used for ML is found in appendix 11.0.2.
 
@@
 \begin{tabular}{ c | c  c  c } 
-  & $\lambda_{Lasso}$ & $\lambda_{Ridge}$ &  $\lambda_{Elastic Net}$ \\ \hline
-2 degrees  & 372.76 & 26.83 & 1 \\ \hline
-3 degrees  & 2310.13 & 432.88 & 1
+  & $\lambda_{LASSO}$ & $\lambda_{RIDGE}$ \\ \hline
+2 degrees  & 372.76 & 26.83 \\ \hline
+3 degrees  & 2310.13 & 432.88
 \end{tabular}
@@
    & \ MSE \ & \, RMSE \ & \ MAE \ \\ \hline
-   Lasso 2-deg & 59,081,597,331.11 & \ 243,067.06 \  & \ 47,660.52 \ \\ 
-  Ridge 2-deg & 62,416,553,466.45 & 249,833.05 & 51,306.19  \\ 
-  Elastic net 2-deg & 1 & 1 & 1  \\ 
+   LASSO 2-deg & 59,081,597,331.11 & \ 243,067.06 \  & \ 47,660.52 \ \\ 
+  RIDGE 2-deg & 62,416,553,466.45 & 249,833.05 & 51,306.19  \\ 
   OLS 2-deg & 64,297,245,726.80 & 253,569.02 & 52,035.52  \\ \hline 
-  Lasso 3-deg & 60,103,955,188.37 & 245,161.08 & 47,126.43  \\ 
-  Ridge 3-deg & 55,667,264,851.14 & 235,939.11 & 43,630.55  \\ 
-  Elastic Net 3-deg & 1 & 1 & 1  \\
-  OLS 3-deg & 2.848e+28 & 168,763,945,674,352.3 & 2,637,476,978,906.39  \\ \hline
+  LASSO 3-deg & 60,103,955,188.37 & 245,161.08 & 47,126.43  \\ 
+  RIDGE 3-deg & 55,667,264,851.14 & 235,939.11 & 43,630.55  \\ 
+  OLS 3-deg & 2.848e+28 & 1.68,7e+14 & 2.637e+12  \\ \hline
 \end{tabular}
@@
 \end{table}
-Since our efforts are aimed at predicting the valuation of a given real estate, we want to penalise the size of the error the MSE-score is a better indicator for our model's performance as opposed to the mean absolute error (MAE).
+Since our efforts are aimed at predicting the valuation of a given real estate, we want to penalise the size of the error.
+Hence, the MSE-score is a better indicator for our model's performance as opposed to the mean absolute error (MAE).
 Since MSE squares the error terms, it gives a relatively high weight to large errors, which is desirable for our current aim.
 
-From table XX it is evident that the machine learning model with two degrees of polynomial features performs best with a regularization by LASSO as it has the lowest measures of difference between the predicted price and the true price, with a MSE of 5.91E+10, whilst the model with 3 degrees of polynomial features regularised by ridge regression performs even better with a MSE 5.57E+10.
+From table 4 it is evident that the model with 3 degrees of polynomial features regularised by RIDGE regression performs best.
+We are somewhat satisfied with the average performance of the model.
+With an MSE of approximately $55\cdot10^{10}$ and a MAE of DKK 43,630.55, we find that the model performs quite well on unseen data.
 Therefore, we chose this model as the final model from which we will conduct the rest of the analysis with.
+Assessment of the preferred model is conducted below.
 \newline
 
-We examine the validation curve, figure \textcolor{red}{XX}, of the model to examine whether we have found a good bias-variance-balance with our optimised hyperparameter.
-We plot the average train and cross-validation performance for different values of $\lambda$:
-
-\paragraph{Learning Curve}
-We examine the learning curve of the model to examine whether the model suffers from immediate over- or underfitting problems and whether these would be remedied by collecting more data\footnote{Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow} p.
+\paragraph{Learning Curve\newline}
+We examine the learning curve of the model to assert whether the model suffers from immediate over- or underfitting problems and whether these would be remedied by collecting more data\footnote{Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow} p.
 196}
@@
 \end{figure}
-The plotted curved represent the average performance of the sets, while the width of the plotted curves expresses the 95\%-confidence interval of the performance.  
-Interpreting the graph could appear quite daunting, as the performances on the validation set are very inconsistent and varies a lot.
-Though inconsistent, it seems as if the gap is decreasing between the performances of the training- and validation sets as the sample size increases.
+The plotted curves represent the average performance of the validation- and training sets, while the width of the plotted curves expresses the 95\%-confidence interval of the performance.  
+The performances on the validation set are very inconsistent and varies a lot.
+None the less, it seems as if the gap is decreasing between the performances of the training- and validation sets as the sample size increases.
 At around 33,000 observations the validation curve drastically decreases and both curves flatten out.
-Though the confidence interval of the validation performance is still noteworthy it also improves dramatically when the sample gets sufficiently high.
+Though the confidence interval of the validation performance is still noteworthy, it also improves dramatically when the sample gets sufficiently high.
 Just before 40,000 observations, the confidence interval of the validation curve actually drops below the train curve, which should not be possible.
@@
 
-\paragraph{Validation Curve}
-We examine the validation curve of the model to see whether we have found a good bias-variance-trade-off with our optimised hyperparameter.
+\paragraph{Validation Curve\newline}
+We examine the validation curve of the model to see whether we have found a good bias-variance trade-off with our optimised hyperparameter.
 We plot the average train and cross-validation performance for different values of $\lambda$:
@@
 
-\textcolor{red}{Firstly, we are somewhat satisfied with the average performance of the model.
-With an MSE of approximately $55\cdot10^{10}$ and a MAE of DKK 43,630.55, we find that the model performs quite well on unseen data.}
-The curve suggest that we have found the optimal degree of regularization with our hyperparameter.
+The curves suggest that we have found the optimal degree of regularization with our hyperparameter.
 Had we chosen a smaller value of $\lambda$, the model would have had too high variance and thus been overfit.
-This is deduced by how poorly the validation predictions performs at smaller lambdas, as opposed to the training performance.
+This is deduced by how poorly the validation predictions performs at smaller $\lambda$, as opposed to the training performance.
 On the contrary, had we chosen a greater value of $\lambda$, the model would have been too biased.
 This is illustrated by how poorly the training data, as well as the validation data, performs at higher values of $\lambda$ .
-In that case, we would have underfit our model.
+In that case, we would have underfitted our model.
 Nonetheless, it is apparent that our model performs better on the training data, which indicates that it retains a degree of overfitting.
 For the abovementioned reasons, it would not be meaningful to minimise this performance gab by adjusting the hyperparameter.
-Other options for decreasing the variance of the model, could be to include more training data, but as illustrated by the learning curve, this would not seem effect the variance.
+Other options for decreasing the variance of the model, could be to include more training data, but as illustrated by the learning curve, this would not seem to effect the variance.
 Lastly, as overfitting is often caused by a sizeable number of features, omission would be a reasonable mean.
-As we have already conducted feature selection on the basis of correlations, we did not find a feasible way to conduct further selection.
+As we have already conducted feature selection on the basis of correlations, we did not find a feasible way to conduct further selection without omitting theoretically warranted features.
 This could be a subject for further studies, to investigate whether this could improve the performance and evaluation of the model.
 \newline
-In conclusion, it would seem that we have found the hyperparameter which yields the optimal bias-variance-trade-off.
-We can thus conclude that we have optimised our model under the given circumstances.
-
-\section{Results}
-\begin{figure}[H]
-\centering
-\caption{Predicted Valuation vs. Actual Valuation}
-%\includegraphics[scale=0.4]{}
-%\source{Own creation, with data from \href{https://www.boliga.dk}{Boliga.dk}}
-\end{figure}
+To sum up it would seem that we have found the hyperparameter which yields the optimal bias-variance trade-off. We can thus conclude that we have optimised our model under the given resources.
 
 \section{Discussion}
-\subsection{No grit search}
+\subsection{No Grid Search or One-to-many}
+$$L_{elasticnet}(\hat{\beta}) = \frac{\sum_{i=1}^{n}\left(y_i-\hat{y_i}(\beta)\right)^2}{2n} + \lambda\left(\frac{1-\alpha}{2}\sum_{j=1}^{p}\hat{\beta_j}^2+\alpha\sum_{j=1}^{p}|\hat{\beta_j}|\right)$$
+$$0 \leq \alpha \leq 1 \quad \wedge \quad \lambda \geq 0$$
 
+\subsection{Best Subset Feature Selection}
 \subsection{Data critique}
-Another interesting prediction which could have been done using the same methods, would have been to predict selling prices.
-This could have been done simply by scraping data on sold housing instead.
-This could be of more value for private agents, whose main interest should be the selling price of their housing.
-%This approach would undoubtedly get a greater data basis.
-needs to add time series trends
+An interesting prediction which could have been done using the same methods, would have been to predict selling prices.
+This could have been done simply by scraping data on sold housing.
+This could be of more value for private agents, whose main interest would be the actual selling price instead of the valuation.
 \newline
 In a prediction-model like this it is near impossible to evade some form of omitted variable bias.
-A significant amount of potential important factors can not be acquired.
-For an example the view from the listed housing will for sure be of great impact of the valuation price.
-Another factor of interest could have been a evaluation of the condition of the housing, unfortunately the statement of property\footnote{red.
+A significant amount of potentially important factors can not be acquired.
+For example the view from the listed housing will for sure be of great impact of the valuation price.
+Another factor of interest could have been an evaluation of the condition of the housing.
+Unfortunately the statement of property\footnote{red.
 Tilstandsrapport} are not publicly accessible.
@@
 The prediction of the cooperative housing valuation %\footnote{http://housingpeople.dk/en/housing-guide/housing-types/cooperative-andelsbolig/},
-are subject to significant bias, since the cooperative housing that enters the marked through a realtor often would be those with critical amount of undesirable characteristics.
+are subject to significant bias, since the cooperative housing that enters the market through a realtor often would be those with critical amount of undesirable characteristics.
+Future studies could exclude cooperative housing in an effort to increase the prediction capabilities.
 
 \subsection{Model Limitations}
-The necessity to exclude municipality dummies as regressors in the prediction models.
-Leaves the model to only separate municipalities by the socio-economic factors, which are subject to low variance.
-This makes distinction between municipality a lot more difficult as well as uncertain.
+The exclusion of municipality dummies as regressors in the prediction models, leaves the model to only separate municipalities by the socio-economic factors, which are subject to low variance.
+This makes distinction between municipalities a lot more difficult as well as uncertain.
 Without the municipality dummies, the interpretation of the prediction results are more insecure.
@@
 Geographical boundaries could have been limited way more, resulting in easier interpretation of predictions. Potentially by predicting only for a specific city or municipality. \\
-If one intended to predict valuations country-wide more realistic, a model for each municipality could have been more satisfactory.
-Resulting in 98 separate models.
-The evident downside of this approach being the prospect of limitations in available data (some municipalities has very few listings).
-Another approach could have been to group cities which share characteristics. Ex. The three biggest cities, the provinces, the islands, the country-side towns.
+If one intended to predict valuations country-wide more realisticly, a model for each municipality could have been more satisfactory, resulting in 98 separate models.
+The evident downside of this approach being the prospect of limitations in available data since some municipalities has very few listings.
+Another approach could have been to group cities which share characteristics. Ex. The three biggest cities, the islands, the country-side towns.
 
 \subsection{Model Selection}
-Instead of only assessing the different models by MAE and RMSE.
-The Information criteria of the respective models could have been introduced.
-Which could have altered the selection of preferred model.
-Both AIC and BIC, would likely have suggested Lasso, with 2-degrees of polynomial features, as preferred model.
-As both measurement are increasing in numbers of estimated parameters\footnote{Peckov, Aleksandar.
+Instead of only assessing the different models by MSE,
+the information criteria of the respective models could have been introduced, which could have altered the selection of preferred model.
+Both AIC and BIC would likely have suggested LASSO with 2-degrees of polynomial features as preferred model, as both criteria are increasing with the numbers of estimated parameters\footnote{Peckov, Aleksandar.
 (2012)  \textit{A Machine Learning Approach To Polynomial Regression}}.
@@
 In this assignment, we have used machine learning to train a model to predict valuation prices of real estate in Denmark.
-We did this by scraping Boliga.dk for all of their active houses for sale and combining this with municipal data on income, education, schools and urbanization.
+We did this by scraping Boliga.dk for all of their listed housing and combining this with municipal data on income, education, schools and urbanization.
 Additionally, we also scraped data from hvorlangterder.dk which calculates the distance from an address, to different every-day commodities such as hospitals, schools and shopping.
-We have explained how we carried out our gathering of data, how we have structured the data and how we cleaned it.
-
-We performed descriptive statistics on the data to gain a better acquaintance with the data. 
+We have explained how we carried out our gathering of data, how we have structured the data and how we cleaned it. \newline
+We performed descriptive statistics to gain a better acquaintance with the data. 
 We conducted feature selection by assessing the correlation between the different features and the target variable, which in our assignment has been the valuation price. 
-We trained both a Lasso- and a Ridge regression model and compared their performances with the performance of a standard linear regression.
-Though k-fold cross-validation, we estimated the optimised hyperparameters for both regularization models.
-We found that the Ridge regression performed best on average, with the performance measure being the smallest mean square error of the model.
-We have assessed to which degree we have managed to find a good bias-variance-balance for our model and concluded that our model suffers from a degree of overfitting.
-This was done by examining the validation curve of our final model.
-
+We trained both a LASSO- and a RIDGE regression model and compared their performances with the performance of a standard linear regression.
+Through k-fold cross-validation, we estimated the optimised hyperparameters for both regularization models.
+We found that the RIDGE regression with three polynomial features performed best, at predicting out of sample data with the performance measure being the smallest mean square error.
+When predicting the test data the model had a MSE of 5.566e+10 with a optimised hyperparameter $\lambda$=432.88 which we found to be a decent performance.
+We have assessed the final model and examined to which degree we have managed to find a good bias-variance-balance for our model and concluded that our model suffers from a degree of overfitting.
+This was done by examining the validation- and learning curve of our final model.
+Additionally we addressed possibilities of further optimising the model.
+\newline
 Finally, we have discussed the results of our analysis. We have critically assessed the boundaries of our research and drawn up potential possibilities for improvement.
-
-\section{An Ethical Overview}
-The ethical principles of social research are anchored in the fundamental human rights, which are broadly formulated in the UN Declaration of Human Rights.
-Additional policies and declarations that codify principles of research ethics and the ethical treatment of research participants include the Nuremberg Code, the Helsinki Declaration, the Belmont Report, and the Menlo Report\footnote{Salganik, Matthew J.
-(2018) \textit{Bit by Bit Bit - Social research in the digital age.}}\, \footnote{European Commission (2018).
-\textit{Ethics in Social Sciences and the Humanities}}.
-These codes and addendums originate mostly in the biomedical field, though they encompass the central principles applied to all human research, which have led some academics to call for a Hippocratic oath for data scientists to safeguard against powerful new technologies under development in laboratories and tech firms\footnote{Rotblat, Joseph (1999) \textit{A Hippocratic Oath for Scientists}}\, \footnote{Sample, Ian (2019, Fri 16 Aug 2019) \textit{and tech specialists need Hippocratic oath, says academic.}}.
-This discussion is nothing new however, as a tentative reformulation of the Hippocratic oath was introduced by Karl Popper\footnote{Popper, Karl (1969) \textit{The Moral Responsibility of the Scientist}}, wherein he stressed the importance of professional responsibility, a critical mind, and an overriding loyalty towards the betterment of mankind.\newline
-Matthew Salganik offer four principles deduced from the Belmont and Menlo Report that should guide the ethical deliberations of the researcher: 1) the respect for persons, that is individuals should be treated as autonomous and if circumstances require it individuals should be entitled to additional protections.
-2) Beneficence stresses the importance of doing no harm and to maximise the possible benefits and minimising any potential harms.
-3) The principle of justice touches upon the importance of the distribution of burdens and benefits of the social scientist's research.
-This principle stress that is should not be a single stratum of society that bears the costs of the research while another stratum benefits.
-4) The fourth and final principle is the respect for law and public interest, according to Salganik, the principle consists of two distinct elements, that is compliance to relevant laws and legal contracts and transparency-based accountability.
-It is worth noting that Popper’s tentative Hippocratic oath mirrors the first three principles put forth by Salganik, stressing the importance of the ethical conduct of the researcher.\newline
-The need for rigid ethical standards within computational social science was made apparent by the Cambridge Analytica Scandal that broke on the 17th of March 2018.
-Where Steve Bannon could reveal that between 2013 and 2015 Cambridge Analytica had exploited a loophole in Facebook’s API which allowed the company to harvest profile data from 87 million Facebook users, without the user’s permission and use the harvested data to construct a massive targeted marketing database based on the user’s likes and interests\footnote{Vox.com (2018) \textit{The Cambridge Analytica Facebook scandal} [Online]}.
-Other examples of misuse of data acquired from Facebook include the Harvard-run experiment, where students' data was used to create new knowledge about how social networks form and how these networks and their actors' behavior co-evolve, and the emotional contagion experiment from 2012, where approximately 700,000 users were involved in a research experiment to examine the extent to which a person's emotions are affected by the emotions of the people they interact with (Salganik.
-2018).\newline
-From this it should be evident that clear ethical guidelines are required in order to protect the user's privacy from tech-savvy companies.
-To this end, the European Parliament introduced the General Data Protection Regulation (GDPR).
-With its seven overarching principles the GDPR seeks to formalise the procedures involved in the data processing and storing of sensitive and private information (CDRC\footnote{Consumer Data Research Center, UK  [CDRC] (2018) \textit{The General Data Protection Regulation \& Social Science Research} [Online]:}).
-These principles include and expand upon the principles found in the Belmont and Menlo Report.
-The most important consideration, however, must be that even a dataset comprising tens of thousands of observations involve human beings who must be protected from adverse side-effects of the social research.
-There is considerable evidence that point to the fact that even in anonymised data sets it can be possible to backtrack an individual's identity.
-A researcher must therefore be mindful of the mosaic effect if the dataset combines large amount of data from various sources (European Commission 2018).
 
@@
 
-(https://jakevdp.github.io/PythonDataScienceHandbook/05.03-hyperparameters-and-model-validation.html). [Accessed on 29/08/2019]
-%Varian, Hal R. (2014) Big Data: New Tricks for Econometrics. Journal of Economic Perspectives. Vol. 28, April: 3-27 \newline
+(https://jakevdp.github.io/PythonDataScienceHandbook/05.03-hyperparameters-and-model-validation.html). [Accessed on 29/08/2019]\newline
 
+https://www.dst.dk/da/Statistik/nyt/NytHtml?cid=27979 [Accessed 27/08/2019]\newline
+
+https://www.dst.dk/da/Statistik/nyt/NytHtml?cid=28741 [Accessed 27/08/2019]\newline
 \newpage

### 2019-08-29 Opsætningexam/DraftExam.tex
r

@@
 \rhead{}
-\chead{Social Data Science, Summer 2019.}
+\chead{Social Data Science, Summer 2019}
 
@@
 \section{Introduction}
-This report depicts a research performed regarding active Danish real estate property valuations.
+This research paper regards listed Danish real estate property valuations.
 Since 2011, the annual number of real estate properties sold has slightly increased, with 2017 being the year with most sold properties in 10 years \href{https://www.dst.dk/da/Statistik/nyt/NytHtml?cid=27979}{(Danmarks Statistik, 2018)}.
@@
 The Boliga data contains approximately 66,000 active offerings with valuations ranging from DKK 15,000 to DKK 85 million.
-This research paper intends to analyse real estate price valuations and which geo- and sociodemographic criteria affect valuations, using machine learning models.
+This research paper intends to use machine learning to analyse real estate price valuations and which geographical and sociodemographic criteria affect valuations.
 Our research question is as follows:
 \begin{center}
- \textit{Which features are most relevant for predicting valuations of real estate properties in Denmark?}
+ \textit{How can geographic and sociodemographic features be utilised to predict real estate property valuations in Denmark?}
 \end{center}
 This research paper contains a section describing the construction of research data and assesses the choices made in gathering meaningful features for the dataset.
-Also, a section regarding the choice and optimization of machine learning models is included, where the intention is to provide insights on our progress of finding the optimal model.
+Also, a section regarding the choice and optimisation of machine learning models is included, where the intention is to provide insights on our progress of finding the optimal model.
 As a result, the best performing model is chosen with a discussion of its usability.
@@
 \section{Literature Review}
-Within social data science there exist widely differing definitions of big data and machine learning. This section seeks to clarify the use of these terms within the scope of this paper.
+Within social data science there exist different definitions of big data and machine learning. This section seeks to clarify the use of these terms within the scope of this paper.
 \subsection{On Big Data \& Machine Learning}
 Historically, big data has been a term reserved for data that was unable to be processed by extant software.
-However, recent increases in computational power has enabled data processing of hitherto unheard of quantities of data\footnote{Lazer, David and Jason Radford (2017) \textit{Data ex Machina.
+However, recent increases in computational power has enabled data processing of hitherto unheard data quantities\footnote{Lazer, David and Jason Radford (2017) \textit{Data ex Machina.
 Introduction to Big Data}.
@@
 Since the data is always-on it is also drifting, meaning that the structure and population it represents is ever-changing.
-It is therefore important to understand that big data is not a naturally occurring system, but driven by the engineered purpose of the system.
+It is therefore important for scientist to understand that big data is not a naturally occurring system, but driven by the engineered purpose of the system.
 This algorithmic confounding force the scientist to be careful regarding any observed human behaviour that is extracted from a single digital system.\newline
-In the analysis of big data it is often useful to employ machine learning as it can identify and predict various non-linear relationships in big data sets, that otherwise would remain hidden.
+In the analysis of big data it is often useful to employ machine learning as it can identify and predict non-linear relationships in big data sets, that otherwise would remain hidden.
 Data scientists' have for the most part optimised the predictive capabilities of the algorithm applied, and as a consequence they have often ignored or trivialised machine learning's potential in causal modelling\footnote{Varian.
@@
 These new approaches could help define what variables to manipulate and how to properly use machine learning within the framework of theoretical assumptions.
-Ultimately, big data and machine learning could increase the scope of the social scientist's field, not only by delivering new data and methods, but by helping the social scientist to focus on new questions\footnote{Mullainathan, Sendhil, and Jann Spiess (2017) \textit{Machine Learning: An Applied Econometric Approach}}.
+Ultimately, big data and machine learning could increase the scope of the social scientist's field, not only by delivering new data and methods, but by helping the social scientist to focus on new questions and avenues of research\footnote{Mullainathan, Sendhil, and Jann Spiess (2017) \textit{Machine Learning: An Applied Econometric Approach}}.
 
-\subsection{An Ethical Overview}
+\subsection{Ethical Concerns in a Petabyte Age}
 The ethical principles of social research are anchored in the fundamental human rights, which are broadly formulated in the UN Declaration of Human Rights.
@@
 \textit{Ethics in Social Sciences and the Humanities}}.
-These codes and addendums originate mostly in the biomedical field, though they encompass the central principles applied to all human research, which have led some academics to call for a Hippocratic oath for data scientists to safeguard against powerful new technologies under development in laboratories and tech firms\footnote{Rotblat, Joseph (1999) \textit{A Hippocratic Oath for Scientists}}\, \footnote{Sample, Ian (2019, Fri 16 Aug 2019) \textit{and tech specialists need Hippocratic oath, says academic.}}.
-This discussion is nothing new however, as a tentative reformulation of the Hippocratic oath was introduced by Karl Popper\footnote{Popper, Karl (1969) \textit{The Moral Responsibility of the Scientist}}, wherein he stressed the importance of professional responsibility, a critical mind, and an overriding loyalty towards the betterment of mankind.\newline
-Matthew Salganik offer four principles deduced from the Belmont and Menlo Report that should guide the ethical deliberations of the researcher: 1) the respect for persons, that is individuals should be treated as autonomous and if circumstances require it individuals should be entitled to additional protections.
+These codes and addendums originate mostly in the biomedical field, though they encompass the central principles applied to all human research, which have led some academics to call for a Hippocratic Oath for data scientists to safeguard against powerful new technologies under development in laboratories and tech firms\footnote{Rotblat, Joseph (1999) \textit{A Hippocratic Oath for Scientists}}\, \footnote{Sample, Ian (2019, Fri 16 Aug 2019) \textit{and tech specialists need Hippocratic Oath, says academic.}}.
+This discussion is nothing new however, as a tentative reformulation of the Hippocratic Oath was introduced by Karl Popper\footnote{Popper, Karl (1969) \textit{The Moral Responsibility of the Scientist}}, wherein he stressed the importance of professional responsibility, a critical mind, and an overriding loyalty towards the betterment of mankind.\newline
+Matthew Salganik offers four principles deduced from the Belmont and Menlo Report that should guide the ethical deliberations of the researcher: 1) the respect for persons, that is individuals should be treated as autonomous and if circumstances require it individuals should be entitled to additional protections.
 2) Beneficence stresses the importance of doing no harm and to maximise the possible benefits and minimising any potential harms.
 3) The principle of justice touches upon the importance of the distribution of burdens and benefits of the social scientist's research.
-This principle stress that is should not be a single stratum of society that bears the costs of the research while another stratum benefits.
+This principle stresses that is should not be a single stratum of society that bears the costs of the research while another stratum benefits.
 4) The fourth and final principle is the respect for law and public interest, according to Salganik, the principle consists of two distinct elements, that is compliance to relevant laws and legal contracts and transparency-based accountability.
-It is worth noting that Popper’s tentative Hippocratic oath mirrors the first three principles put forth by Salganik, stressing the importance of the ethical conduct of the researcher.\newline
-The need for rigid ethical standards within computational social science was made apparent by the Cambridge Analytica Scandal that broke on the 17th of March 2018.
-Where Steve Bannon could reveal that between 2013 and 2015 Cambridge Analytica had exploited a loophole in Facebook’s API which allowed the company to harvest profile data from 87 million Facebook users, without the user’s permission and use the harvested data to construct a massive targeted marketing database based on the user’s likes and interests\footnote{Vox.com (2018) \textit{The Cambridge Analytica Facebook scandal} [Online]}.
-Other examples of misuse of data acquired from Facebook include the Harvard-run experiment, where students' data was used to create new knowledge about how social networks form and how these networks and their actors' behavior co-evolve, and the emotional contagion experiment from 2012, where approximately 700,000 users were involved in a research experiment to examine the extent to which a person's emotions are affected by the emotions of the people they interact with (Salganik.
+It is worth noting that Popper’s tentative Hippocratic Oath mirrors the first three principles put forth by Salganik, stressing the importance of the ethical conduct of the researcher.\newline
+The need for rigid ethical standards within computational social science was made apparent by the Cambridge Analytica Scandal that broke on the $17^{th}$ of March 2018.
+Where Steve Bannon could reveal that between 2013 and 2015 Cambridge Analytica had exploited a loophole in Facebook’s API.
+This allowed the company to harvest profile data from 87 million Facebook users, without the user’s permission and used the harvested data to construct a massive targeted marketing database based on the user’s likes and interests\footnote{Vox.com (2018) \textit{The Cambridge Analytica Facebook scandal} [Online]}.
+Other examples of misuse of data acquired from Facebook include the Harvard-run experiment, where students' data was used to create new knowledge about how social networks form.
+The gathered information was used to examine how these networks and their actors' behavior co-evolve.
+Another example of misuge of data is the emotional contagion experiment from 2012, where approximately 700,000 Facebook users were involved in a research experiment to examine the extent to which a person's emotions are affected by the emotions of the people they interact with (Salganik.
 2018).\newline
@@
 These principles include and expand upon the principles found in the Belmont and Menlo Report.
-The most important consideration, however, must be that even a dataset comprising tens of thousands of observations involve human beings who must be protected from adverse side-effects of the social research.
-There is considerable evidence that point to the fact that even in anonymised data sets it can be possible to backtrack an individual's identity.
+The most important consideration, however, must be that even a dataset comprising tens of thousands observations involve human beings who must be protected from adverse side-effects of the social research.
+There is considerable evidence that points to the fact that even in anonymised data sets it can be possible to backtrack an individual's identity.
 A researcher must therefore be mindful of the mosaic effect if the dataset combines large amount of data from various sources (European Commission 2018).
@@
 \section{Data Description \& Ethics}
+In the following sections we will consider the ethical ramifications of our inquiry.
+We will focus our efforts on the contractual obligations laid down by Boliga's Terms \& Conditions and the more general ethical considerations a social scientist should consider before conducting research.
+Following this, will be a brief description of our data, how it was collected, cleaned and examined.
 
@@
 In the current paper the appropriate care and consideration has been given to the ethical concerns regarding the scraping, processing, and the presentation of the data.
-Drawing upon the European Comissions\footnote{European Commission (2018).
+Drawing upon the European Comission's\footnote{European Commission (2018).
 \textit{Ethics in Social Sciences and the Humanities}} guidelines and principles for ethical conduct in social data science, the potential harm to users of Boliga's website were carefully considered.
-As a step to prevent the mosaic effect and in an effort to anonymise the scraped data only aggregated data will be presented in this paper, so that no single observation can be identified from the analysed data.\newline
-No informed consent has been obtained from the users of the site, prompting us to consider the consequences of the lack thereof, as informed consent is paramount to the proper, ethical conduct in social science.
+As a step to prevent the mosaic effect and in an effort to anonymise the scraped data, only aggregated data will be presented in this paper, so that no single observation can be identified from the analysed data.\newline
+Informed consent has not been obtained from the users of the site, prompting us to consider the consequences of the lack thereof, as informed consent is paramount to the proper, ethical conduct in social science.
 However, as in this instance, informed consent can be logistically impossible to collect from all participants in the study.
 Salganik mentions that informed consent for everything is an ideal, but in practice impossible to obtain and researchers should instead strive to follow an alternative rule, that he describes as: "some form of consent for most things." \footnote{Salganik, Matthew J.
-(2018) \textit{Bit by Bit - Social research in the digital age.} p.303} Adhering to this, more complex understanding of the practicality of informed consent, we chose to contact Boliga to inform them of our intent to scrape their website and use the data in an educational context\footnote{Shiab, Nael (2015) \textit{On the Ethics of Web Scraping and Data Journalism}}.
+(2018) \textit{Bit by Bit - Social research in the digital age.} p.303} Adhering to this more complex understanding of the practicality of informed consent, we chose to contact Boliga to inform them of our intent to scrape their website and use the data in an educational context\footnote{Shiab, Nael (2015) \textit{On the Ethics of Web Scraping and Data Journalism}}.
 Boliga responded positively to our inquiry, which we took as informed consent from a third party on behalf of the participating users in our study.\newline
@@
 In order to comply with these terms we refrained from burdening their website's performance by implementing a time.sleep function.
-This causes each scraping iteration to pause for 0.5 seconds before commencing on scraping the next page \textcolor{red}{(see Jupyter XX)}.
+This causes each scraping iteration to pause for 0.5 seconds before commencing on scraping the next page (see Jupyter).
 \subsection{Data Scraping Process}
-In the following paragraphs our scraping efforts will be described. The scrapers can be examined in the attached Jupyter Notebooks labelled \textcolor{red}{XX and XX.} 
+In the following paragraphs our scraping efforts will be described. The scrapers can be examined in the attached Jupyter Notebooks. 
 \paragraph{\href{https://www.boliga.dk}{Boliga}\newline}
 Our data comes from \href{https://www.boliga.dk}{Boliga.dk}, the largest independent online web-portal for real estate sales in Denmark and has access to unique features such as days-for-sale, price-development and access to BBR - the Danish Building and Housing Register \footnote{\href{https://www.boligagruppen.dk}{www.boligagruppen.dk}}.
-Giving us unique insights into the pricing of real estate in all 98 municipalities of Denmark.
+This gives unique insight into the pricing of real estate in all 98 municipalities of Denmark.
 65,950 properties were for sale at the time of scraping.\newline
 The scraping process was conducted on Friday the $23^{rd}$ of August 2019.
-Global Investigative Journalism Network.
-In order to scrape the data of interest we familiarised ourselves with the HTML-structure of Boliga.
-On the basis of these insights we constructed a code, which was able to scrape every page, containing information pertaining the currently listed real estates on Boliga.
+In order to scrape the data of interest we familiarised ourselves with the network-structure of Boliga.
+On the basis of these insights we constructed a code which was able to scrape every page, containing information on the currently listed real estates on Boliga.
 The scraper requested all information available from each individual page, which surmounted to 1,319 URL requests.
@@
 For each listed property, 34 features and the target variable (price) was collected.
-Table \textcolor{red}{XX} provides an overview of the features with a short description, and whether the feature has been dropped or saved for later usage.
+Appendix \textcolor{red}{XX} provides an overview of the features with a short description, and whether the feature has been dropped or saved for later usage.
 There are three reasons for a feature to be dropped:\newline
@@
 2. The feature contains insufficient data,\newline
-3. The feature is poorly formatted and cannot efficiently be recreated. 
-11 features are considered to be of interest.
+3. The feature is poorly formatted and cannot efficiently be recreated. \newline
+10 features are considered to be of interest.
 \vspace*{10px} \newline
@@
 \begin{tabular}{c c}
-Categorical: & ForClosure, Type, Municipality, lotSize	 \\	
+Categorical: & ForClosure, Type, Municipality	 \\	
 \end{tabular}
-\paragraph{\href{https://www.hvorlangterder.dk}{Hvorlangterder.dk}\newline}
+\paragraph{\href{https://www.hvorlangterder.dk}{hvorlangterder.dk}\newline}
 \href{https://www.hvorlangterder.dk}{hvorlangterder.dk} returns distances from a given address, to everyday commodities such as supermarkets, hospitals and schools.   
@@
 The function returned 65,950 URL responses, from which relevant information was extracted.\newline
-As Jupyter performs poorly when running long asynchronous tasks and estimated a running time of 18 hours this procedure was run in Visual Studio.
+As Jupyter performs poorly when running long asynchronous tasks and the estimated running time was 18 hours, this procedure was run in Visual Studio Code.
  \vspace*{10px} \newline
@@
 \begin{tabular}{c c}
-\qquad \qquad \qquad \qquad &  pharmacy, library, coast, junction \\	
+\qquad \qquad \qquad \qquad & metro, pharmacy, library, coast, junction \\	
 \end{tabular}
@@
 \paragraph{DAWA\newline}
+\href{https://dawa.aws.dk/}{Denmark's Addresses Web API}\footnote{red.
+Danmarks Adressers Web API} (DAWA) is an API containing data regarding Danish addresses.
+DAWA will be used to collect information about the municipality that each address is located in.
+This data will be used to merge the socio-demographic data collected from various sources (see below) with the data scraped from Boliga.
 
-\paragraph{Socioeconomic Factors\newline}
-Socioeconomic factors on municipality level was collected from \href{https://statistik.politi.dk/QvAJAXZfc/opendoc.htm?document=QlikApplication%2F2999_Public\%2FPublic_IndsatsResultater.qvw}{statistik.politi.dk} and
-\href{https://www.dst.dk/da/Statistik/emner/befolkning-og-valg}{Danmarks Statistik} respectively.
+\paragraph{Sociodemographic Factors\newline}
+Sociodemographic factors on municipality level was collected from \href{https://statistik.politi.dk/QvAJAXZfc/opendoc.htm?document=QlikApplication%2F2999_Public\%2FPublic_IndsatsResultater.qvw}{statistik.politi.dk} and
+\href{https://www.dst.dk/da/Statistik/emner/befolkning-og-valg}{Danmarks Statistik}.
 The factors include income, reported crime, level of highest completed education, etc.
@@
 \begin{tabular}{c c}
-\textit{Features obtained:}: & unemployment\_relative, primary\_school\_educ, high\_school\_educ \\	
+\textit{Features obtained}: & unemployment\_relative, primary\_school\_educ, high\_school\_educ \\	
 \end{tabular}\newline 
@@
 \subsection{Analysis of Scraping Logs}
-Three datasets were obtained through web scraping from Boliga.dk, Hvorlangterder.dk and DAWA.dk.
+Three datasets were obtained through web scraping from Boliga.dk, hvorlangterder.dk and DAWA.dk.
 This section will analyse the logs created in the scraping process, with the intention of ensuring the data quality.
@@
 \paragraph{Error Codes\newline}
-Figure plots error codes received throughout the duration of the scrapings.
+Figure 3 plots error codes received throughout the duration of the scrapings.
 Boliga and DAWA received no errors, while hvorlangterder received a total of 80 errors.
@@
 An indicator of poor data quality is varying response times from the server being scraped.
-\textcolor{red}{Figure XC} plots changes in response times for the duration of the web scrapings.
+Figure 4 plots changes in response times for the duration of the web scrapings.
 The three data sources all resulted in few variations of response time.
-Unusual response times has been assessed within the logs, to be caused by either a slow server connection, or due to larger quantities of data being requested.
-To validate the quality of data, manual control of the returned results and the website results was performed, without notice of significant corruptions in the data utilised in the research.
+Unusual response times have been assessed, to be caused by a slow server connection, or due to larger quantities of data being requested.
+To validate the quality of data, manual control of the returned results and the website results was performed, without notice of significant corruptions in the data.
 \begin{figure}[H]
@@
 To validate the response quality, an assessment of the response size was performed.
-\textcolor{red}{Figure XD} plots response sizes throughout the duration of the web scrapings.
+Figure 5 plots response sizes throughout the duration of the web scrapings.
 Boliga contains a single noticeably large response size within short time, while hvorlangterder response sizes vary throughout the scrape.
@@
 \end{figure}
-Examining the distribution of sample sizes in figure XE, the Boliga and DAWA response sizes seem to be close to normally distributed, except for two single cases of large sample sizes in the Boliga log.
+Examining the distribution of sample sizes in figure 6, the Boliga and DAWA response sizes seem to be close to normally distributed, except for two single cases of large sample sizes in the Boliga log.
 By manually assessing the returned output of the Boliga scrape, these two requests were found to return a larger amount of data than usual.
@@
 \end{figure}
-\textcolor{red}{Figure XE depicts that the hvorlangerder response sizes were a bit left skewed, while Figure XD} shows that the distribution of large sizes happens during the middle of the scrape.
+Figure 6 depicts that the hvorlangterder response sizes were a bit left skewed, while Figure 5 shows that the distribution of large sizes happens during the middle of the scrape.
 With a further glimpse into the log, we observed two things.
-Firstly, all response sizes of 0 are related to the errors, displayed in figure XB.
+Firstly, all response sizes of 0 are related to the errors, displayed in figure 2.
 The variance of responses could be explained by the type of data retrieved from the scrape.
@@
 
-The data collection and scraping process provided a total of 15 Datasets from Boliga, Hvorlangterder, DAWA, the Danish Police, Social- \& Indenrigsministeriet and Danmarks Statistik.
+The data collection and scraping process provided a total of 15 Datasets from Boliga, hvorlangterder, DAWA, the Danish Police, Social- \& Indenrigsministeriet and Danmarks Statistik.
 This section will describe how each dataset was merged, using pandas relational database styled merge and join operations.
@@
 \paragraph{Boliga.dk\newline}
-An evaluation of the Boliga datasets features and their ability to support further data collection led to the utilization of the following features:
+An evaluation of the Boliga datasets features and their ability to support further data collection led to the utilisation of the following features:
 
@@
 This dataframe was merged onto the Boliga dataframe using a many-to-one merge with municipality codes as the merge keys.
-The scraped municipality names from DAWA was used as the merge key for all further merges of municipal data.
+The scraped municipality names from DAWA were used as the merge keys for all further merges of municipal data.
 
-\paragraph{Danmarks Statistik, Danish Police \& Social og Indenrigsministeriet\newline}
+\paragraph{Danmarks Statistik, Danish Police and Social \& Indenrigsministeriet\newline}
 Of the municipality-based data collected, the merging of these to our master dataframe was subsequently performed identically.
@@
 Therefore, a merge operation was not necessary, but could alternatively have been managed with a one-to-one inner-merge on id.
-As few coordinates regarding apartment properties are repetitive, these are not suitable for merging upon.
 
@@
 In the following sections we describe our data cleaning efforts.
-\subsubsection{Initial clean-up}
+\subsubsection{Initial Clean-Up}
 The initial clean-up filtered out rows that contained illogical values.
-Here we focused our efforts on removing any and all observations that contained a municipality code of zero.
+Here we focused our efforts on removing all observations that contained a municipality code of zero.
 Additionally, we chose to exclude any real estate valued below DKK 100, these listings existed on Boliga's website, but were all auction listings.
@@
 Another option was to set the limit according to each municipality's mean, a solution that was a bit more time consuming.
-In figure XX the number of rows dropped at each step of the cleaning can be perused.
-\begin{table}
+In table 1 the number of rows filtered at each step of the cleaning can be perused.
+\begin{table}[H]
 \begin{center}
@@
 \hline 
-days-for-sale & 3,940\\
+Days-for-Sale & 3,940\\
 \hline 
@@
 \end{table}
-\subsubsection{Ejerlejlighed's lot size}
+\subsubsection{Apartment Lot Size}
 Inspecting our data we found that out of 8,028 apartments, 1,176 had a lot size.
 These listings included the apartment complex' common area, whereas the rest did not.
-To overcome this discrepancy we chose to set all non-zero values to zero, as not to confuse our model with an inconsistent feature (Raschka \& Mirjalili 2017).
+To overcome this discrepancy we chose to set all non-zero values to zero, as not to confuse our model with an inconsistent feature\footnote{Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow}}.
 
-\subsubsection{Final touches}
-After merging the housing info with the demographic data and the distances from hvorlangterder.dk, we removed a single duplicate and deleted all columns not relevant for our analysis.
+\subsubsection{Final Touches}
+After merging the housing info with the sociodemographic data and the distances from hvorlangterder.dk, we removed a single duplicate and deleted all columns not relevant for our analysis.
 After the clean-up of the data we were left with a dataset consisting of 61,618  observations, 37 features and 1 target variable.
-The features are of both categorical and continuous measures
+The features are of both categorical and continuous measures.
 
@@
 \subsubsection{Key Statistics}
-Some key statistical characteristics are presented in table 1:
+Some key statistical characteristics are presented in table 2:
 \begin{table}[H]
@@
 Initially, it should be addressed that some of the properties has 0 rooms and consists of 0 $m^2$.
-This is due to the fact that we have also included land on which housing has not yet been built.
-Examining the 25\%-quintile and the 75\%-quintile of the valuation prices, it becomes apparent that there are some substantial outliers both to the cheaper and to expensive side.
+This is due to the fact that we have also included property on which housing has not yet been built.
+Examining the 25\%-quintile and the 75\%-quintile of the valuation prices, it becomes apparent that there are some substantial outliers both to the cheaper and expensive side.
 
@@
    \caption{}
-   \includegraphics[width=\linewidth]{Box1.png} 
+   \includegraphics[scale=0.5]{Box1.png} 
   \label{fig:}
 \end{figure}
-The boxplot illustrates that the distribution is heavily left-skewed, where some municipalities has a sizebly higher average income than the rest of the Danish municipalities.
+The boxplot illustrates that the distribution is right-skewed, where some municipalities has a sizeably higher average income than the rest of the Danish municipalities.
 
@@
    \caption{}
-   \includegraphics[width=\linewidth]{Box2.png} 
+   \includegraphics[scale=0.5]{Box2.png} 
   \label{fig:}
 \end{figure}
-It becomes apparent that the distribution is quite right-skewed and that there are a few municipalities who’s price per square meter is much higher than the rest of the municipalities.
+It becomes apparent that the distribution is quite right-skewed and that there are a few municipalities whose price per square meter is much higher than the rest of the municipalities.
 Recalling the geoplot in figure 1, these expensive outliers are heavily concentrated around- and north of Copenhagen.
-The distribution looks similar to that of figure 2 (The previous boxplot), though we cannot declare any correlation between average municipal income and average municipal price per square meter.
+The distribution looks similar to that of figure 7, though we cannot declare any correlation between average municipal income and average municipal price per square meter.
 Nonetheless, it becomes apparent that the valuation price of property is highly discriminated by municipal factors.
-The scope of this assignment is exactly to examine these factors and attempt to use these to evaluate an unseen, out-of-sample property.
+The scope of this research paper is exactly to examine these factors and attempt to use these to valuate an unseen, out-of-sample property.
 
@@
    \caption{}
-   \includegraphics[width=\linewidth]{bar1.png} 
+   \includegraphics[scale=0.5]{bar1.png} 
   \label{fig:}
@@
 This is not especially surprising though, as it is a well-established trend that real estate prices in major cities are skyrocketing.
-Refraining from delving deeper into a discussion of global urbanization, we retain the fact that property type does have an apparently significant effect on average valuation.
+Refraining from delving deeper into a discussion of global urbanisation, we retain the fact that property type does have an effect on average valuation.
 We will include the ‘type’ feature in our impending model training to control for this effect.
@@
 \section{Methods}
-The objective of applying Machine Learning(ML) is to train a model that is able to make predictions on never seen data.
-By feeding a model labelled data as well as data samples, ML will define the algorithms that performs best predictions\footnote{Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow}.
+The objective of applying Machine Learning (ML) is to train a model that is able to make predictions on new data.
+By feeding a model labelled data as well as data samples, ML will define the algorithm that perform best predictions\footnote{Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow}.
 p.
 3}.
-This project implements a ML regression prediction model.
+This research paper implements a ML regression prediction model.
+The following section will establish the methods utilised for optimising the prediction model.
 \subsection{Fitting the model}
@@
 In both cases, the model will generalise poorly.
-A key step in defining a decent model in machine learning is to find an optimal bias-variance-balance, by tuning the complexity of one’s model.
-This is done through \textit{regularization}.
-In this project two different types of regularization are applied; LASSO and RIDGE.
+A key step in defining a decent model in machine learning is to find an optimal bias-variance balance, by tuning the complexity of one's model.
+This is done through \textit{regularisation}.
+In this research two different types of regularisation are applied; LASSO and RIDGE.
 
 \subsubsection{LASSO}
-Regularization by LASSO, will penalise complexity of the model by the sum of the absolute value of the coefficients.
-This penalty will make the model less complex and more appropriate for prediction.
-\footnote{Foster, Ian; Rayid Ghani Ron S.
+Regularisation by LASSO, will penalise complexity of the model by the sum of the absolute value of the coefficients.
+This penalty will make the model less complex and more appropriate for prediction\footnote{Foster, Ian; Rayid Ghani Ron S.
 Jarmin, Frauke Kreuter, Julia Lane; \textit{Big Data in Social Sciences, A Practical Guide to Methods and Tools} p.
 173}\, \footnote{Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow} p.
-332}
+332}.
 \newline LASSO minimises: $$L_{LASSO}(\hat{\beta}) = \left(\sum_{i=1}^{n} (y_i-\hat{y_i}(\beta))^2+\lambda\sum_{j=1}^{p}|\hat{\beta_j}|\right) \qquad s.t \quad \lambda \geq 0 $$
@@
 p.19}.
-LASSO thereby performs feature selection automaticly.
+LASSO thereby performs feature selection.
 \subsubsection{RIDGE}
@@
 
+\subsubsection{Polynomial Features}
+Regression models assume linear relationships as standard.
+One way to account for violations of this assumption, is by utilising polynomial terms within the regression.
+These polynomial terms create extensive polynomial combinations between the features, fitting the model more precisely to the given data\footnote{Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow} p.
+334}.
+Polynomial expansion may cause overfitting of the model, generating poor predictions on new data.
+
 \subsection{Selecting Features}
-In case regularization is not sufficient to cope with the overfitting of the model, exclusion of features is a viable approach.
-With the number of scraped features in this project taking into consideration, A recurring overfitting of the model would be likely.
-As a consequence a deliberate exclusion of features of interest are necessary.
+In case regularisation is not sufficient to cope with the overfitting of the model, exclusion of features is a viable approach.
+With the number of scraped features in this research taking into consideration, a recurring overfitting of the model would be likely.
+As consequence a deliberate exclusion of features of interest is necessary.
 
@@
 Subsequently, we use k-fold cross-validation to randomly split the development set into k folds, where k-1 folds are used to train the model.
-The remaining fold is used to validate the model’s generalizability by calculating the mean squared errors of the trained model’s prediction of the left-out fold\footnote{Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow}.
+The remaining fold is used to validate the model’s generalisability by calculating the mean squared errors of the trained model’s prediction of the left-out fold\footnote{Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow}.
 p.191}.
@@
 Since we are working with a relatively large dataset we chose to split our data into 5 folds, and computed the average MSE for the 5 iterations.
-By using the k-fold cross-validation method we minimise the concern that the estimation of our model’s performance is simply due to a lucky or unlucky split of the data.
+By using the k-fold cross-validation method we minimise the concern that the estimation of our model’s performance is due to a lucky or unlucky split of the data.
 \newline
-We performed this procedure for different values of $\lambda$. We chose the value of $\lambda$ which yielded the smallest average MSE over the 5 folds. 
+We performed this procedure for different values of $\lambda$.
+Initially we tested greatly different values of $\lambda$ to prevent convergence issues.
+On subsequent iterations the value-span was narrowed down.
+We eventually chose the value of $\lambda$ which yielded the smallest average MSE over the 5 folds.
 We both calculated the optimal hyperparameters for a RIDGE regression model and a LASSO regression model.
@@
 p.192}.
-\newline The performances of the models are simply measured by MSE and MAE.
+\newline The performances of the models are simply measured by MSE.
 \newline
 $$ MSE = \frac{1}{n}\sum_{i=1}^{n}(y_i-\hat{y_i})^2$$
-$$ MAE = \frac{1}{n}\sum_{i=1}^{n}|y_i-\hat{y_i}|$$
 
@@
 A number of features are excluded before training the model.
-The exclusion is determined, quite simply, by investigation of the correlation between the complete set of features and the target variable.
-A list of the excluded features is found in appendix 11.0.1.
-The model used for ML is found in appendix 11.0.2.
+The exclusion is determined by investigation of the single correlation between the  individual features and the target variable, shown in figure 10.
+\begin{figure}[H]
+\centering
+\caption{}
+\includegraphics[scale=0.6]{Corrplot.png}
+%\source{}
+\end{figure}
 
-The initial 5-fold cross-validation to obtain the optimal values of the hyperparameters in each regularization yields. 
-\begin{table}[h!]
+A list of the excluded features is found in appendix 11.0.1. The model used for ML is found in appendix 11.0.2.  
+The initial 5-fold cross-validation to obtain the optimal values of the hyperparameters in each regularisation yields: 
+\begin{table}[H]
 \begin{center}
@@
   & $\lambda_{LASSO}$ & $\lambda_{RIDGE}$ \\ \hline
-2 degrees  & 372.76 & 26.83 \\ \hline
+2 degrees  & 372.76 & 22.76 \\ \hline
 3 degrees  & 2310.13 & 432.88
@@
   RIDGE 3-deg & 55,667,264,851.14 & 235,939.11 & 43,630.55  \\ 
-  OLS 3-deg & 2.848e+28 & 1.68,7e+14 & 2.637e+12  \\ \hline
+  OLS 3-deg & 2.848e+28 & 1.687e+14 & 2.637e+12  \\ \hline
 \end{tabular}
@@
 \end{table}
-Since our efforts are aimed at predicting the valuation of a given real estate, we want to penalise the size of the error.
+Since our efforts are aimed at predicting the valuation of a out-of-sample real estate property, we want to penalise the size of the error.
 Hence, the MSE-score is a better indicator for our model's performance as opposed to the mean absolute error (MAE).
@@
 From table 4 it is evident that the model with 3 degrees of polynomial features regularised by RIDGE regression performs best.
+Figure 11 shows a plot of the predicted values of our model against the actual values of the test data.
+
+\begin{figure}[H]
+\centering
+\caption{}
+\includegraphics[scale=0.4]{predictactual.png}
+%\source{}
+\end{figure}
 We are somewhat satisfied with the average performance of the model.
@@
 Therefore, we chose this model as the final model from which we will conduct the rest of the analysis with.
-Assessment of the preferred model is conducted below.
-\newline
+In the following section further assessment of the model will be conducted  \newline
 
@@
 The plotted curves represent the average performance of the validation- and training sets, while the width of the plotted curves expresses the 95\%-confidence interval of the performance.  
-The performances on the validation set are very inconsistent and varies a lot.
-None the less, it seems as if the gap is decreasing between the performances of the training- and validation sets as the sample size increases.
+The performance on the validation set is very inconsistent and varies a lot.
+Nonetheless, it seems as if the gap is decreasing between the performances of the training- and validation sets as the sample size increases.
 At around 33,000 observations the validation curve drastically decreases and both curves flatten out.
@@
 \end{figure}
-The dotted line approximately represents the optimised value of lambda from our previously conducted k-fold cross-validation.
-
-The curves suggest that we have found the optimal degree of regularization with our hyperparameter.
+The dotted line approximately represents the optimised value of $\lambda$ from our previously conducted k-fold cross-validation. 
+The curves suggest that we have found the optimal degree of regularisation with our hyperparameter.
 Had we chosen a smaller value of $\lambda$, the model would have had too high variance and thus been overfit.
@@
 \section{Discussion}
-\subsection{No Grid Search or One-to-many}
+\subsection{Alternative Regularisation}
+As an alternative method of regularisation, we could also have used a regularisation regression called Elastic Net.
+It is a mix of both LASSO and RIDGE regressions, and minimises\footnote{Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow} p.
+332}:
 $$L_{elasticnet}(\hat{\beta}) = \frac{\sum_{i=1}^{n}\left(y_i-\hat{y_i}(\beta)\right)^2}{2n} + \lambda\left(\frac{1-\alpha}{2}\sum_{j=1}^{p}\hat{\beta_j}^2+\alpha\sum_{j=1}^{p}|\hat{\beta_j}|\right)$$
@@
 
+Note that an Elastic Net regression contains 2 hyperparameters, which also makes it additionally difficult to compute and optimise for big datasets like ours.
+Optimising the hyperparameters can be done through Grid Search which is a computationally demanding method.
+We did attempt this method on a subsample of our data, which caused our kernel to crash.
+With a smaller dataset or with a stronger computer, the performance of an optimised Elastic Net regression should have been taking into account when deciding on a model.
+As we did not find a lucrative way to optimise the model, we have not included it.
+
 \subsection{Best Subset Feature Selection}
-\subsection{Data critique}
+The current feature selection consisted of selecting features based on their individual correlation to the target.
+Although providing a satisfying performance, the feature selection could be executed better.
+The optimal approach to our feature selection, would be applying a Best Subset Selection approach.
+The Best Subset Selection takes all variable combinations into consideration of the given model and selects the best performing model.
+Although this approach would provide the best feature combination, the process is highly time consuming \footnote{Gareth, J., Witten, D., Tibshirani, R., \& Hastie, T.
+(2017).
+Linear Model Selection and Regularisation.
+In J.
+Gareth, D.
+Witten, R.
+Tibshirani, \& T.
+Hastie, \textit{An Introduction to Statistical Learning}, p.
+207}.
+LASSO-models eliminate features irrelevant to the prediction, in contrary best subset feature selection provide a more precise dataset for testing more models.
+\subsection{Data Critique}
 An interesting prediction which could have been done using the same methods, would have been to predict selling prices.
@@
 \newline
-The prediction of the cooperative housing valuation %\footnote{http://housingpeople.dk/en/housing-guide/housing-types/cooperative-andelsbolig/},
+The prediction of the cooperative housing valuation\footnote{http://housingpeople.dk/en/housing-guide/housing-types/cooperative-andelsbolig/},
 are subject to significant bias, since the cooperative housing that enters the market through a realtor often would be those with critical amount of undesirable characteristics.
@@
 \subsection{Model Limitations}
-The exclusion of municipality dummies as regressors in the prediction models, leaves the model to only separate municipalities by the socio-economic factors, which are subject to low variance.
+The exclusion of municipality dummies as regressors in the prediction models, leaves the model to only separate municipalities by the sociodemografic factors, which are subject to low variance.
 This makes distinction between municipalities a lot more difficult as well as uncertain.
@@
 Geographical boundaries could have been limited way more, resulting in easier interpretation of predictions. Potentially by predicting only for a specific city or municipality. \\
-If one intended to predict valuations country-wide more realisticly, a model for each municipality could have been more satisfactory, resulting in 98 separate models.
+If one intended to predict valuations country-wide more realisticly, a model for each municipality could have been another interesting approach, resulting in 98 separate models.
 The evident downside of this approach being the prospect of limitations in available data since some municipalities has very few listings.
@@
 \section{Conclusion}
-In this assignment, we have used machine learning to train a model to predict valuation prices of real estate in Denmark.
-We did this by scraping Boliga.dk for all of their listed housing and combining this with municipal data on income, education, schools and urbanization.
+In this research paper we have used machine learning to train a model to predict valuation prices of real estate in Denmark.
+The model train on sociodemographic and geographical data.
+\newline We did this by scraping Boliga.dk for all of their listed housing and combining this with municipal data on income, education, schools and urbanisation.
 Additionally, we also scraped data from hvorlangterder.dk which calculates the distance from an address, to different every-day commodities such as hospitals, schools and shopping.
@@
 We performed descriptive statistics to gain a better acquaintance with the data. 
-We conducted feature selection by assessing the correlation between the different features and the target variable, which in our assignment has been the valuation price. 
+We conducted feature selection by assessing the correlation between the different features and the target variable, which in our research has been the valuation price. 
 We trained both a LASSO- and a RIDGE regression model and compared their performances with the performance of a standard linear regression.
-Through k-fold cross-validation, we estimated the optimised hyperparameters for both regularization models.
-We found that the RIDGE regression with three polynomial features performed best, at predicting out of sample data with the performance measure being the smallest mean square error.
+Through k-fold cross-validation, we estimated the optimised hyperparameters for both regularisation models.
+We found that the RIDGE regression with three polynomial features performed best, at predicting out-of-sample data with the performance measure being the smallest mean square error.
 When predicting the test data the model had a MSE of 5.566e+10 with a optimised hyperparameter $\lambda$=432.88 which we found to be a decent performance.
-We have assessed the final model and examined to which degree we have managed to find a good bias-variance-balance for our model and concluded that our model suffers from a degree of overfitting.
+We have assessed the final model and examined to which degree we have managed to find a good bias-variance trade-off for our model and concluded that our model suffers from a degree of overfitting.
 This was done by examining the validation- and learning curve of our final model.
@@
 
-Sample, Ian (2019, Fri 16 Aug 2019) \textit{and tech specialists need Hippocratic oath, says academic.} The Guardian [Online]: \href{https://www.theguardian.com/science/2019/aug/16/mathematicians-need-doctor-style-hippocratic-oath-says-academic-hannah-fry} [Accessed on 25/08/2019]\newline
+Sample, Ian (2019, Fri 16 Aug 2019) \textit{and tech specialists need Hippocratic Oath, says academic.} The Guardian [Online]: \href{https://www.theguardian.com/science/2019/aug/16/mathematicians-need-doctor-style-hippocratic-oath-says-academic-hannah-fry} [Accessed on 25/08/2019]\newline
 
@@
 
+Gareth, J., Witten, D., Tibshirani, R., \& Hastie, T.
+(2017).
+Linear Model Selection and Regularization.
+In J.
+Gareth, D.
+Witten, R.
+Tibshirani, \& T.
+Hastie, \textit{An Introduction to Statistical Learning} (pp.
+205-262).
+New York City: Springer.
+
 https://www.dst.dk/da/Statistik/nyt/NytHtml?cid=27979 [Accessed 27/08/2019]\newline
@@
          \end{bmatrix}$$
+\newpage
+\subsubsection{t}
+
 \end{document}

### 2019-08-29 Opsætningexam/DraftExam.tex
b

@@
 For each listed property, 34 features and the target variable (price) was collected.
-Appendix \textcolor{red}{XX} provides an overview of the features with a short description, and whether the feature has been dropped or saved for later usage.
+Appendix 9.0.3 provides an overview of the features with a short description, and whether the feature has been dropped or saved for later usage.
 There are three reasons for a feature to be dropped:\newline
@@
 \begin{tabular}{c c}
-Distances to: & lake, forest, doctor, supermarket,	school, daycare, hospital, train \\	
+Distances to: & lake, forest, doctor, supermarket,	school, daycare, hospital, train, bus\_stop \\	
 \end{tabular}\newline 
 \begin{tabular}{c c}
-\qquad \qquad \qquad \qquad & metro, pharmacy, library, coast, junction \\	
+\qquad \qquad \qquad \qquad & metro, pharmacy, library, coast, junction, s-train, airport \\	
 \end{tabular}
@@
 DAWA will be used to collect information about the municipality that each address is located in.
-This data will be used to merge the socio-demographic data collected from various sources (see below) with the data scraped from Boliga.
+This data will be used to merge the sociodemographic data collected from various sources (see below) with the data scraped from Boliga.
 
@@
 It would be reasonable to assume that there is an average difference in valuation pricing depending on the type of property.
-Figure 4 displays the median valuation price for each type:
+Figure 9 displays the median valuation price for each type:
 \begin{figure}[H]
@@
 
-A list of the excluded features is found in appendix 11.0.1. The model used for ML is found in appendix 11.0.2.  
+A list of the excluded features is found in appendix 9.0.1. The model used for ML is found in appendix 9.0.2.  
 The initial 5-fold cross-validation to obtain the optimal values of the hyperparameters in each regularisation yields: 
@@
 Since MSE squares the error terms, it gives a relatively high weight to large errors, which is desirable for our current aim.
-
+\newline
 From table 4 it is evident that the model with 3 degrees of polynomial features regularised by RIDGE regression performs best.
@@
 \newline
-Finally, we have discussed the results of our analysis. We have critically assessed the boundaries of our research and drawn up potential possibilities for improvement.
+Finally, we have discussed the results of our analysis.
+We have critically assessed the boundaries of our research and drawn up potential possibilities for improvement.
+In conclusion, we found that sociodemographical and geographical features can be utilised to a satisfactory degree in predicting real estate valuations in Denmark
 
@@
 
-Consumer Data Research Center, UK  [CDRC] (2018) \textit{The General Data Protection Regulation \& Social Science Research} [Online]: \href{https://ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020_ethics-soc-science-humanities_en.pdf}{ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020\_ethics-soc-science-humanities\_en.pdf} [Accessed on 25/08/2019]\newline
+Consumer Data Research Center, UK  [CDRC] (2018) \textit{The General Data Protection Regulation \& Social Science Research} [Online]: \newline\href{https://ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020ethics-soc-science-humanities_en.pdf}{ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020} [Accessed on 25/08/2019]\newline
 
 European Commission (2018).
-\textit{Ethics in Social Sciences and the Humanities} [Online]: \href{https://ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020_ethics-soc-science-humanities_en.pdf}{https://ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020\_ethics-soc-science-humanities\_en.pdf} [Accessed on 25/08/2019] \newline
+\textit{Ethics in Social Sciences and the Humanities} [Online]: \href{https://ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020_ethics-soc-science-humanities_en.pdf}{ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020\_ethics-soc-science-humanities} [Accessed on 25/08/2019] \newline
 
@@
 
-Salganik, Matthew J. (2018) \textit{Bit by Bit Bit - Social research in the digital age.} Princeton, NJ: Princeton University Press.\newline
+Salganik, Matthew J. (2018) \textit{Bit by Bit - Social research in the digital age.} Princeton, NJ: Princeton University Press.\newline
 
@@
 \newpage
-\subsubsection{t}
+\subsubsection{}  
+\begin{tabular}{|c|c|c|}
+\hline 
+\textbf{Feature} & \textbf{Description} & \textbf{Dropped} \\ 
+\hline 
+agentDisplayName & Real estate Agent Name & True \\ 
+\hline 
+agentRegId & Real-estate Agent ID & True \\ 
+\hline 
+area & Area of country (11 areas) & True \\ 
+\hline 
+basementSize & Square meters of basement & False \\ 
+\hline 
+buildYear & Year of house built & False \\ 
+\hline 
+city & City Name & False \\ 
+\hline 
+createdDate & Day of offer creation & True \\ 
+\hline 
+daysForSale & Scraping date - createdDate & False \\ 
+\hline 
+domainId & Description unknown & True \\ 
+\hline 
+energyClass & Energy scale - not sufficiently formated & True \\ 
+\hline 
+exp & Property expenses & False \\ 
+\hline 
+floor & Entrance floor & False \\ 
+\hline 
+groupKey & Key for same buildings & True \\ 
+\hline 
+guid & Link & True \\ 
+\hline 
+id & Unique identifier & True \\ 
+\hline 
+images & Image format dictionary & True \\ 
+\hline 
+inWatchlist & In profile's watchlist & True \\ 
+\hline 
+isActive & If the offer is active on webpage (all are active)
+ & True \\ 
+\hline 
+isForeclosure & The house is being foreclosed & True \\ 
+\hline 
+isPremiumAgent & An agent ranking & True \\ 
+\hline 
+latitude & Latitude of address & False \\ 
+\hline 
+longitude & Longitude of adress & False \\ 
+\hline 
+lotSize & Size of total property & False \\ 
+\hline 
+municipality & Municipality code & False \\ 
+\hline 
+net & Description unknown & True \\ 
+\hline 
+openHouse & Boolean. True if future open house date exists & True \\ 
+\hline 
+price & Total price (Target) & False \\ 
+\hline 
+priceChangePercentTotal & Price change since first valuation & True \\ 
+\hline 
+propertyType & Property type category & False \\ 
+\hline 
+rooms & No. of rooms & False \\ 
+\hline 
+selfsale & Bool if property sold without agen & True \\ 
+\hline 
+size & Size of residential property & False \\ 
+\hline 
+squaremeterPrice & Price/size & True \\ 
+\hline 
+street & Street name & True \\ 
+\hline 
+views & No. of views on website & True \\ 
+\hline 
+zipCode & Zipcode (Post nr.) & True \\ 
+\hline 
+\end{tabular}
 

### 2019-08-29 Opsætningexam/DraftExam.tex
de

@@
 \newline
-
 The valuations included in the research are collected from one of Denmarks largest online real estate websites named Boliga.dk.
@@
 In order to comply with these terms we refrained from burdening their website's performance by implementing a time.sleep function.
-This causes each scraping iteration to pause for 0.5 seconds before commencing on scraping the next page (see Jupyter).
+This causes each scraping iteration to pause for 0.5 seconds before commencing on scraping the next page.
+See attached Jupyter notebooks.
 \subsection{Data Scraping Process}
@@
 \end{tabular}
-\paragraph{\href{https://www.hvorlangterder.dk}{hvorlangterder.dk}\newline}
-\href{https://www.hvorlangterder.dk}{hvorlangterder.dk} returns distances from a given address, to everyday commodities such as supermarkets, hospitals and schools.   
+\paragraph{\href{https://www.hvorlangterder.dk}{Hvorlangterder.dk}\newline}
+\href{https://www.hvorlangterder.dk}{Hvorlangterder.dk} returns distances from a given address, to everyday commodities such as supermarkets, hospitals and schools.   
 The scraping of \href{https://www.hvorlangterder.dk}{hvorlangterder.dk} was achieved by writing a function that took in the GPS-coordinates gathered from Boliga.
@@
 p.
-231 }.
-
+231 }.\newline
 The data collection and scraping process provided a total of 15 Datasets from Boliga, hvorlangterder, DAWA, the Danish Police, Social- \& Indenrigsministeriet and Danmarks Statistik.
@@
 Therefore, we chose this model as the final model from which we will conduct the rest of the analysis with.
-In the following section further assessment of the model will be conducted  \newline
+In the following section further assessment of the model will be conducted.
 
-\paragraph{Learning Curve\newline}
+\subsection{Learning Curve}
 We examine the learning curve of the model to assert whether the model suffers from immediate over- or underfitting problems and whether these would be remedied by collecting more data\footnote{Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow} p.
@@
 Just before 40,000 observations, the confidence interval of the validation curve actually drops below the train curve, which should not be possible.
-We have not found a meaningful explanation aside from noise or chance \footnote{\href{https://jakevdp.github.io/PythonDataScienceHandbook/05.03-hyperparameters-and-model-validation.html}{jakevdp.github.io/PythonDataScienceHandbook/05.03-hyperparameters-and-model-validation.html}}
+We have not found a meaningful explanation aside from noise or chance \footnote{\href{https://jakevdp.github.io/PythonDataScienceHandbook/05.03-hyperparameters-and-model-validation.html?fbclid=IwAR22jhu2nrTY3eJME4VTuTSLXNKqNMmPzlwU4-IJ8VvEMIsLy05-IqgQdsI}{Van der Plas, Jake.
+(2016)}}
 All in all, the learning curve would indicate that the performance of the model will not benefit from additional training data.
 
-\paragraph{Validation Curve\newline}
+\subsection{Validation Curve}
 We examine the validation curve of the model to see whether we have found a good bias-variance trade-off with our optimised hyperparameter.
@@
 We have critically assessed the boundaries of our research and drawn up potential possibilities for improvement.
-In conclusion, we found that sociodemographical and geographical features can be utilised to a satisfactory degree in predicting real estate valuations in Denmark
+\newline In conclusion, we found that sociodemographical and geographical features can be utilised to a satisfactory degree in predicting real estate valuations in Denmark
 
@@
 \section{Litterature}
-\ Foster, Ian; Rayid Ghani Ron S. Jarmin, Frauke Kreuter, Julia Lane; \textit{Big Data in Social Sciences, A Practical Guide to Methods and Tools}, CRS Press 2017 \newline
+Anderson, Chris (2008) \textit{The end of theory: The data deluge makes the scientific method obsolete.} Wired, 16-07 [Online] \url{www.wired.com/2008/06/pb-theory/} [Accessed on 27/08/2019]
 
-Rashka, Sebastian; Mirjalli, Vahid; \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow}, $2^{nd}$editon, Packt Publishing 2017. \newline
+Athey, Susan (2018) 'The Impact of Machine Learning on Economics' in Ajay Agrawal et al. (eds) \textit{The Economics of Artificial Intelligence: An Agenda} (2019) Chicago: University of Chicago Press.
 
-Varian. Hal R. \textit{Big data: New tricks for econometrics}. Journal of Economic Perspectives, 28(2):3–28, 2014. \newline
+Consumer Data Research Center, UK [CDRC] (2018) \textit{The General Data Protection Regulation \& Social Science Research} [Online]: \href{https://www.cdrc.ac.uk/wp-content/uploads/2018/05/6-GDPR-and-social-science-research-full-document-1.pdf}{https://www.cdrc.ac.uk} [Accessed on 27/08/2019]
 
-Consumer Data Research Center, UK  [CDRC] (2018) \textit{The General Data Protection Regulation \& Social Science Research} [Online]: \newline\href{https://ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020ethics-soc-science-humanities_en.pdf}{ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020} [Accessed on 25/08/2019]\newline
+Boligagruppen.dk (2019) \textit{Om boliga gruppen} [Online]: \url{www.boligagruppen.dk}: [Accessed on 27/08/2019]
 
-European Commission (2018).
-\textit{Ethics in Social Sciences and the Humanities} [Online]: \href{https://ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020_ethics-soc-science-humanities_en.pdf}{ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020\_ethics-soc-science-humanities} [Accessed on 25/08/2019] \newline
+DST (2019) \url{https://www.dst.dk/da/Statistik/nyt/NytHtml?cid=27979} [Accessed 27/08/2019]
+
+DST (2019) \url{https://www.dst.dk/da/Statistik/nyt/NytHtml?cid=28741} [Accessed 27/08/2019]
+
+Einav, Liran and Jonathan Levin (2014) \textit{Economics in the age of big data.} Science, vol. 346, November.
+
+European Commission (2018) \textit{Ethics in Social Sciences and the Humanities}[Online]: \href{https://ec.europa.eu/research/participants/data/ref/h2020/other/hi/h2020_ethics-soc-sciencehumanities_en.pdf}{https://ec.europa.eu/}[Accessed on 25/08/2019]
+
+Foster, Ian; Rayid Ghani Ron S. Jarmin, Frauke Kreuter, Julia Lane; (2017) \textit{Big Data in Social Sciences, A Practical Guide to Methods and Tools}, CRS Press
+
+Gareth, J., Witten, D., Tibshirani, R., \& Hastie, T.
+(2017) \textit{Linear Model Selection and Regularization.} In J.
+Gareth, D.Witten, R.
+Tibshirani, \& T.
+Hastie, \textit{An Introduction to Statistical Learning}(pp.
+205-262).
+New York City: Springer.
+
+Grimmer, Justin (2015) \textit{We are all social scientists now: how big data, machine learning, and causal inference work together.} PS: Political Science \& Politics, vol. 48, January: 80-83.
+
+Lazer, David and Jason Radford (2017) D\textit{ata ex Machina. Introduction to Big Data}. Annual Review of Sociology, vol. 43, August.
+
+McKinney, W. (2018) ’Data Wrangling: Join, Combine and Reshape’. In W. McKinney, \textit{Python for Data Analysis}. Sebastopol: O’Reilly Media Inc.
+
+Mullainathan, Sendhil, and Jann Spiess (2017)\textit{ Machine Learning: An Applied Econometric Approach.} Journal of Economic Perspectives, vol. 31 (2): 87-106.
+
+Peckov, Aleksandar.
+(2012) \textit{A Machine Learning Approach To Polynomial Regression.} Available at \url{kt.ijs.si/theses/phd_aleksandar_peckov.pdf} Doctoral Dissertation.
+Jozef Stefan International Postgraduate School.
+Ljubljana, Slovenia, October 2012.
+[Accessed on 29/08/2019]
 
@@
 Encounter, March 1969, pp.
-52-56 [Online]: \href{http://www.unz.com/print/Encounter-1969mar-00052}{http://www.unz.com/print/Encounter-1969mar-00052} [Accessed on 25/08/2019]\newline
+52-56 [Online]: \href{http://www.unz.com/print/Encounter-1969mar-00052}{unz.com} [Accessed on 25/08/2019]
+
+Rashka, Sebastian; Mirjalli, Vahid; (2017) \textit{Python Machine Learning, Machine Learning and Deep Learning with Python, scikit-learn, and Tensorflow} 2ndediton, Packt Publishing
 
@@
 286, Issue 5444, pp.
-1475 [Online]: \href{https://science.sciencemag.org/content/286/5444/1475.full}{https://science.sciencemag.org/content/286/5444/1475.full} [Accessed on 25/08/2019] DOI: 10.1126/science.286.5444.1475 \newline
+1475 [Online]: \url{https://science.sciencemag.org/content/286/5444/1475.full} [Accessed on 25/08/2019] DOI: 10.1126/science.286.5444.1475
 
-Salganik, Matthew J. (2018) \textit{Bit by Bit - Social research in the digital age.} Princeton, NJ: Princeton University Press.\newline
+Salganik, Matthew J. (2018) \textit{Bit by Bit - Social research in the digital age}. Princeton, NJ: Princeton University Press.
 
-Sample, Ian (2019, Fri 16 Aug 2019) \textit{and tech specialists need Hippocratic Oath, says academic.} The Guardian [Online]: \href{https://www.theguardian.com/science/2019/aug/16/mathematicians-need-doctor-style-hippocratic-oath-says-academic-hannah-fry} [Accessed on 25/08/2019]\newline
+Sample, Ian (2019, Fri 16 Aug 2019) \textit{Maths and tech specialists need Hippocratic oath, says academic.} The Guardian [Online]: \href{https://www.theguardian.com/science/2019/aug/16/mathematicians-need-doctor-style-hippocratic-oath-says-academic-hannah-fry}{www.theguardian.com} [Accessed on 25/08/2019]
 
-Vox.com (2018) \textit{The Cambridge Analytica Facebook scandal} [Online]: \href{https://www.vox.com/2018/4/10/17207394/cambridge-analytica-facebook-zuckerberg-trump-privacy-scandal} [Accessed on 26/08/2019] \newline
+Shiab, Nael (2015) O\textit{n the Ethics of Web Scraping and Data Journalism}.
+Global Investigative Journalism Network.
+[Online]: \href{gijn.org/2015/08/12/on-the-ethics-of-web-scraping-and-data-journalism/}{gijn.org}: [Accessed on 27/08/2019]
+Varian. Hal R. \textit{Big data: New tricks for econometrics}. Journal of Economic Perspectives, 28(2):3–28, 2014.
 
-Boligagruppen.dk (2019) \textit{Om boliga gruppen} [Online]: \href{https://www.boligagruppen.dk}{www.boligagruppen.dk}: [Accessed on 27/08/2019] \newline
+Van der Plas, Jake.
+(2016)\textit{Python Data Science Handbook} available at: \href{https://jakevdp.github.io/PythonDataScienceHandbook/05.03-hyperparameters-and-model-validation.html?fbclid=IwAR22jhu2nrTY3eJME4VTuTSLXNKqNMmPzlwU4-IJ8VvEMIsLy05-IqgQdsI}{GitHub} [Accessed on 29/08/2019]
 
-Shiab, Nael (2015) \textit{On the Ethics of Web Scraping and Data Journalism.
-Global Investigative Journalism Network.} [Online]: \href{https://gijn.org/2015/08/12/on-the-ethics-of-web-scraping-and-data-journalism/}{gijn.org/2015/08/12/on-the-ethics-of-web-scraping-and-data-journalism/}: [Accessed on 27/08/2019] \newline
+Vox.com (2018) \textit{The Cambridge Analytica Facebook scandal} [Online]: \href{https://www.vox.com/2018/4/10/17207394/cambridge-analytica-facebook-zuckerberg-trump-privacy-scandal}{vox.com} [Accessed on 26/08/2019]
 
-McKinney, W. (2018). 'Data Wrangling: Join, Combine and Reshape'. In W. McKinney, \textit{Python for Data Analysis}. Sebastopol: O'Reilly Media Inc. \newline
-
-Athey, Susan (2018) 'The Impact of Machine Learning on Economics' in Ajay Agrawal et al.
-(eds) \textit{The Economics of Artificial Intelligence: An Agenda} (2019).
-Chicago: University of Chicago Press.
-\newline
-
-Einav, Liran and Jonathan Levin (2014) \textit{Economics in the age of big data}. Science, vol. 346, November. \newline
-
-Grimmer, Justin (2015) \textit{We are all social scientists now: how big data, machine learning, and causal inference work together}.
-PS: Political Science \& Politics, vol.
-48, January: 80-83.
-\newline
-
-Lazer, David and Jason Radford (2017) \textit{Data ex Machina. Introduction to Big Data. Annual Review of Sociology}, vol. 43, August. \newline
-
-Mullainathan, Sendhil, and Jann Spiess (2017) \textit{Machine Learning: An Applied Econometric Approach}. Journal of Economic Perspectives, vol. 31 (2): 87-106. \newline
-
-Anderson, Chris (2008) \textit{The end of theory: The data deluge makes the scientific method obsolete}.
-Wired, 16-07 [Online] \href{https://www.wired.com/2008/06/pb-theory/}{www.wired.com/2008/06/pb-theory/} [Accessed on 27/08/2019]\newline
-
-Peckov, Aleksandar.
-(2012)  \textit{A Machine Learning Approach To Polynomial Regression}.
-Available at \href{http://kt.ijs.si/theses/phd_aleksandar_peckov.pdf}{kt.ijs.si/theses/phd\_aleksandar\_peckov.pdf}.
-Doctoral Dissertation.
-Jozef Stefan International Postgraduate School.
-Ljubljana, Slovenia, October 2012.
-[Accessed on 29/08/2019]
-
-(https://jakevdp.github.io/PythonDataScienceHandbook/05.03-hyperparameters-and-model-validation.html). [Accessed on 29/08/2019]\newline
-
-Gareth, J., Witten, D., Tibshirani, R., \& Hastie, T.
-(2017).
-Linear Model Selection and Regularization.
-In J.
-Gareth, D.
-Witten, R.
-Tibshirani, \& T.
-Hastie, \textit{An Introduction to Statistical Learning} (pp.
-205-262).
-New York City: Springer.
-
-https://www.dst.dk/da/Statistik/nyt/NytHtml?cid=27979 [Accessed 27/08/2019]\newline
-
-https://www.dst.dk/da/Statistik/nyt/NytHtml?cid=28741 [Accessed 27/08/2019]\newline
 \newpage
